### 2024-05-16 paper/header.tex
Initial commit

% **************GENERATED FILE, DO NOT EDIT**************

\title{My JuliaCon proceeding}

\author[1]{1st author}
\author[1, 2]{2nd author}
\author[2]{3rd author}
\affil[1]{University}
\affil[2]{National Lab}

\keywords{Julia, Optimization, Game theory, Compiler}

\hypersetup{
pdftitle = {My JuliaCon proceeding},
pdfsubject = {JuliaCon 2022 Proceedings},
pdfauthor = {1st author, 2nd author, 3rd author},
pdfkeywords = {Julia, Optimization, Game theory, Compiler},
}

### 2024-05-16 paper/paper.tex
Initial commit

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}

\begin{document}

\input{header}

\maketitle

\begin{abstract}

This is a guide for authors who are preparing papers for JuliaCon using the \LaTeX{} document
preparation system and the \verb|juliacon|  class file.

\end{abstract}

\section{Introduction}

The \LaTeX{} document preparation system is a special version of the
\TeX; typesetting program where-in a collection of \TeX; commands
are added to \LaTeX{} to simplify typesetting. Importantly, it allows
the author to concentrate on the logical structure of the document
rather than its visual layout.\vskip 6pt
Moreover, \LaTeX{} provides a consistent and comprehensive document
preparation interface. There are simple-to-use commands for
generating a table of contents, lists of figures and/or tables, and indexes.
\LaTeX{} can automatically number list entries, equations, figures,
tables, and footnotes, as well as articles, sections, and subsections.
Using this numbering system, bibliographic citations, page
references, and cross references to any other numbered entity (e.g.
article, section, equation, figure, list entry, etc.) become quite simple
and straightforward. The use of \LaTeX{} document classes allows
a simple change of class to transform the appearance of your document.\vskip 6pt
\LaTeX{} is a powerful tool for managing long and complex documents.
In particular, partial processing enables long documents to
be produced article by article without losing sequential information.
The use of document classes allows a simple change of style
(or style option) to transform the appearance of your document.

\section{The JuliaCon Article Class}
\label{sec:documentclass}
%
The juliacon class file preserves the standard LATEX{} interface such
that any document that can be produced using the standard LATEX{}
article class can also be produced with the class file.\vskip 6pt
It is likely that the make up will change after file submission. For
this reason, we ask you to ignore details such as slightly long lines,
page stretching, or figures falling out of synchronization, as these
details can be dealt with at a later stage.\vskip 6pt
Use should be made of symbolic references (\verb|\ref| ) in order to
protect against late changes of order, etc.

\section{USING THE JuliaCon Article CLASS FILE}

If the file \verb|juliacon.cls|  is not already in the appropriate system directory
for \LaTeX{} files, either arrange for it to be put there or copy
it to your working directory. The \verb|juliacon|  document class is implemented
as a complete class, not a document style option. In order to
use the \verb|juliacon  document class, replace \verb|article|  by \verb|juliacon|  in the
\verb|\documentclass|  command at the beginning of your document:
\vskip 6pt
\begin{centering}
    \verb|\documentclass{article}|  \end{centering}
\vskip 6pt
replace by
\vskip 6pt
 \verb|\documentclass{juliacon}|  \vskip 6pt
In general, the following standard document \verb|style|  options should
{ \itshape not} be used with the {\footnotesize \itshape article} class file:
\begin{enumerate}
\item[(1)] \verb|10pt|,  \verb|11pt|,  \verb|12pt|   ? unavailable;
\item[(2)] \verb|twoside|  (no associated style file) ? \verb|twoside|  is the default;
\item[(3)] \verb|fleqn|, \verb|leqno|, \verb|titlepage| ? should not be used;
\end{enumerate}

\section{Additional Document Style Options}
\label{sec:additional_doc}
%
The following additional style option is available with the \verb|juliacon|  class file:
\vskip 6pt
Please place any additional command definitions at the very start of
the \LaTeX{} file, before the \verb|\begin{document}|. For example, user-defined
\verb|\def|  and \verb|\newcommand|   commands that define macros for
technical expressions should be placed here. Other author-defined
macros should be kept to a minimum.
\vskip 6pt
Commands that differ from the standard \LaTeX{} interface, or that
are provided in addition to the standard interface, are explained in
this guide. This guide is not a substitute for the \LaTeX{} manual itself.
Authors planning to submit their papers in \LaTeX{} are advised to use
\verb|juliacon.cls|  as early as possible in the creation of their files.

%
%
%
%
\begin{table*}[t]
\tabcolsep22pt
\tbl{If necessary, the tables can be extended both columns.}{
\begin{tabular}{|l|l|c|c|}\hline
Label & \multicolumn{1}{c|}{Description}
& Number of Users &
Number of Queries\\\hline
Test 1 & Training Data &
\smash{\raise-7pt\hbox{70}} & 104\\
\cline{1-2}\cline{4-4}
Test 2 & Testing Data I & & 105\\\hline
Test 3 & Testing Data II & 30 & 119\\\hline
& Total & 100 & 328\\\hline
\end{tabular}}
\label{tab:symbols}
\begin{tabnote}
This is an example of table footnote.
\end{tabnote}
\end{table*}
% \begin{figure*}[t]
% \centerline{\includegraphics[width=11cm]{juliagraphs.png}}
% \caption{If necessary, the images can be extended both columns.}
%   \label{fig:sample_image}
% \end{figure*}

\section{Additional features}
\label{sec:additional_faci}
In addition to all the standard \LaTeX{} design elements, the \verb|juliacon|  class file includes the following features:
In general, once you have used the additional \verb|juliacon.cls| facilities
in your document, do not process it with a standard \LaTeX{} class
file.

\subsection{Titles, Author's Name, and Affiliation}
\label{subsub:title_auth}
The title of the article, author's name, and affiliation are used at the
beginning of the article (for the main title). These can be produced
using the following code:

\begin{verbatim}
\title{ This is an example of article title} }
\author{
   \large 1st Author \\[-3pt]
   \normalsize 1st author's affiliation  \\[-3pt]
    \normalsize 1st line of address \\[-3pt]
    \normalsize 2nd line of address \\[-3pt]
    \normalsize	1st author's email address \\[-3pt]
  \and
   \large 2nd Author \\[-3pt]
   \normalsize 2nd author's affiliation  \\[-3pt]
    \normalsize 1st line of address \\[-3pt]
    \normalsize 2nd line of address \\[-3pt]
    \normalsize	2nd author's email address \\[-3pt]
\and
   \large 3rd Author \\[-3pt]
   \normalsize 3rd author's affiliation  \\[-3pt]
    \normalsize 1st line of address \\[-3pt]
    \normalsize 2nd line of address \\[-3pt]
    \normalsize	3rd author's email address \\[-3pt]
}
\maketitle
\end{verbatim}

\subsection{Writing Julia code}

A special environment is already defined for Julia code,
built on top of \textit{listings} and \textit{jlcode}.

\begin{verbatim}
\begin{lstlisting}[
    language = Julia, 
    numbers=left, 
    label={lst:exmplg}, 
    caption={Example Code Block.}
]
using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{lstlisting}
\end{verbatim}
\begin{lstlisting}[
    language = Julia, 
    numbers=left, 
    label={lst:exmplg}, 
    caption={Example Code Block.}
]
using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{lstlisting}

\subsection{Abstracts, Key words, term etc...}
\label{subsub:abs_key_etc}

At the beginning of your article, the title should be generated
in the usual way using the \verb|\maketitle|  command. For genaral tem and keywords use
\verb|\terms|,
\verb|\keywords|  commands respectively. The abstract should be enclosed
within an abstract environment, All these environment
can be produced using the following code:
\begin{verbatim}
\terms{Experimentation, Human Factors}

\keywords{Face animation, image-based modelling...}

\begin{abstract}
In this paper, we propose a new method for the
systematic determination of the model's base of
time varying delay system. This method based on
the construction of the classification data related
to the considered system. The number, the orders,
the time delay and the parameters of the local
models are generated automatically without any
knowledge about the full operating range of the
process. The parametric identification of the local
models is realized by a new recursive algorithm for
on line identification of systems with unknown time
delay. The proposed algorithm allows simultaneous
estimation of time delay and parameters of
discrete-time systems. The effectiveness of
the new method has been illustrated through
simulation.
\end{abstract}

\end{verbatim}

\section{Some guidelines}
\label{sec:some_guide}
The following notes may help you achieve the best effects with the
\verb|juliacon|  class file.

\subsection{Sections}
\label{subsub:sections}
\LaTeXe{}  provides four levels of section headings and they are all
defined in the \verb|juliacon|  class file:
\begin{itemize}
\item \verb|\section|
\item \verb|\subsection|
\item \verb|\subsubsection|
\item \verb|\paragraph|
\end{itemize}
Section headings are automatically converted to allcaps style.
\subsection{Lists}
\label{sec:lists}
%
The \verb|juliacon|   class file provides unnumbered lists using the
\verb|unnumlist|  environment for example,

\begin{unnumlist}
\item First unnumbered item which has no label and is indented from the
left margin.
\item Second unnumbered item.
\item Third unnumbered item.
\end{unnumlist}
The unnumbered list which has no label and is indented from the
left margin. was produced by:
\begin{verbatim}
\begin{unnumlist}
\item First unnumbered item...
\item Second unnumbered item...
\item Third unnumbered item...
\end{unnumlist}
\end{verbatim}

The \verb|juliacon|  class file also provides hyphen list using the
\verb|itemize|  environment for example,
\begin{itemize}
\item First unnumbered bulleted item which has no label and is indented
from the left margin.
\item Second unnumbered bulleted item.
\item Third unnumbered bulleted item which has no label and is indented
from the left margin.
\end{itemize}
was produced by:
\begin{verbatim}
\begin{itemize}
\item First item...
\item Second item...
\item Third item...
\end{itemize}
\end{verbatim}

Numbered list is also provided in acmtog class file using the
enumerate environment for example,
\begin{enumerate}
\item The attenuated and diluted stellar radiation.
\item Scattered radiation, and
\item Reradiation from other grains.
\end{enumerate}

was produced by:
\begin{verbatim}
\begin{enumerate}
\item The attenuated...
\item Scattered radiation, and...
\item Reradiation from other grains...
\end{enumerate}
\end{verbatim}
\subsection{Illustrations (or figures)}
\label{subsub:sec_Illus}
The \verb|juliacon|  class file will cope with most of the positioning of
your illustrations and you should not normally use the optional positional
qualifiers on the \verb|figure|  environment that would override
these decisions.
\vskip 6pt

%
\begin{figure}[t]
\centerline{\includegraphics[width=4cm]{juliagraphs.png}}
\caption{This is example of the image in a column.}
	\label{fig:sample_figure}
\end{figure}

The figure \ref{fig:sample_figure} is taken from the JuliaGraphs
organization \footnote{https://github.com/JuliaGraphs}.

Figure captions should be \emph{below} the figure itself, therefore the
\verb|\caption|  command should appear after the figure or space left for
an illustration. For example, Figure 1 is produced using the following
commands:

\begin{verbatim}
\begin{figure}
\centerline{\includegraphics[width=20pc]{Graphics.eps}}
\caption{An example of the testing process for a
binary tree. The globa null hypothesis is tested
first at level $\alpha$ (a), and the level of
individual variables is reached last (d). Note
that individual hypotheses can be tested at
level $\alpha/4$ and not $\alpha/8$ as one might
expect at first.}
\label{sample-figure_2}
\end{figure}
\end{verbatim}
Figures can be resized using first and second argument of
\verb|\includegraphics|   command. First argument is used for modifying
figure height and the second argument is used for modifying
figure width respectively.
\vskip 6pt
Cross-referencing of figures, tables, and numbered, displayed
equations using the \verb|\label|  and \verb|\ref|   commands is encouraged.
For example, in referencing Figure 1 above, we used
\verb|Figure~\ref{sample-figure}|

 \subsection{Tables}
\label{subsub:sec_Tab}
The \verb|juliacon|   class file will cope with most of the positioning of
your tables and you should not normally use the optional positional qualifiers on the table environment which would override these
decisions. Table captions should be at the top.
\begin{verbatim}
\begin{table}
\tbl{Tuning Set and Testing Set}{
\begin{tabular}{|l|l|c|c|}\hline
Label & \multicolumn{1}{c|}{Description}
& Number of Users &
Number of Queries\\\hline
Train70 & Training Data &
\smash{\raise-7pt\hbox{70}} & 104\\
\cline{1-2}\cline{4-4}
Test70 & Testing Data I & & 105\\\hline
Test30 & Testing Data II & 30 & 119\\\hline
& Total & 100 & 328\\\hline
\end{tabular}}
\end{table}
\end{verbatim}

\begin{table}
\tbl{Tuning Set and Testing Set}{
\begin{tabular}{|l|l|c|c|}\hline
Label & \multicolumn{1}{c|}{Description}
& Number of Users &
Number of Queries\\\hline
Test 1 & Training Data &
\smash{\raise-7pt\hbox{70}} & 104\\
\cline{1-2}\cline{4-4}
Test 2 & Testing Data I & & 105\\\hline
Test 3 & Testing Data II & 30 & 119\\\hline
& Total & 100 & 328\\\hline
\end{tabular}}
\end{table}
\subsection{Landscaping Pages}
\label{subsub:landscaping_pages}
If a table is too wide to fit the standard measure, it may be turned,
with its caption, to 90 degrees. Landscape tables cannot be produced
directly using the \verb|juliacon|   class file because \TeX{} itself cannot
turn the page, and not all device drivers provide such a facility.
The following procedure can be used to produce such pages.
\vskip 6pt
Use the package \verb|rotating|   in your document and change the coding
from
\begin{verbatim}
\begin{table}...\end{table}
to
\begin{sidewaystable}...\end{sidewaystable}
and for figures
\begin{figure}...\end{figure}
to
\begin{sidewaysfigure}...\end{sidewaysfigure}
\end{verbatim}

environments in your document to turn your table on the appropriate
page of your document. For instance, the following code prints
a page with the running head, a message half way down and the
table number towards the bottom.
\begin{verbatim}
\begin{sidewaystable}
\tbl{Landscape table caption to go here.}{...}
\label{landtab}
\end{sidewaystable}
\end{verbatim}

\subsection{Double Column Figure and Tables}
\label{subsub:double_fig_tab}
For generating the output of figures and tables in double column
we can use the following coding:

\begin{enumerate}
\item For Figures:
\begin{verbatim}
\begin{figure*}...\end{figure*}
\end{verbatim}
\item For landscape figures:
\begin{verbatim}
\begin{sidewaysfigure*}...\end{sidewaysfigure*}
\end{verbatim}
\item For Tables:
\begin{verbatim}
\begin{table*}...\end{table*}
\end{verbatim}
\item For landscape tables:
\begin{verbatim}
\begin{sidewaystable*}...\end{sidewaystable*}
\end{verbatim}
\end{enumerate}

\subsection{Typesetting Mathematics}
\label{subsub:type_math}
The \verb|juliacon| class file will set displayed mathematics with center to
the column width, provided that you use the \LaTeXe{} standard of
open and closed square brackets as delimiters.
The equation
\[
\sum_{i=1}^p \lambda_i = (S)
\]

was typeset using the acmtog class file with the commands

\begin{verbatim}
\[
\sum_{i=1}^p \lambda_i = (S)
\]
\end{verbatim}

For display equations, cross-referencing is encouraged. For example,
\begin{verbatim}
\begin{equation}
(n-1)^{-1} \sum^n_{i=1} (X_i - \overline{X})^2.
\label{eq:samplevar}
\end{equation}
Equation~(\ref{eq:samplevar}) gives the formula for
sample variance.
\end{verbatim}
The following output is generated with the above coding:
\begin{equation}
(n-1)^{-1} \sum^n_{i=1} (X_i - \overline{X})^2.
\label{eq:samplevar}
\end{equation}
Equation~(\ref{eq:samplevar}) gives the formula for
sample variance.

\subsection{Enunciations}
\label{subsub:enunciation}
The \verb|juliacon|   class file generates the enunciations with the help of
the following commands:
\begin{verbatim}
\begin{theorem}...\end{theorem}
\begin{strategy}...\end{strategy}
\begin{property}...\end{property}
\begin{proposition}...\end{proposition}
\begin{lemma}...\end{lemma}
\begin{example}...\end{example}
\begin{proof}...\end{proof}
\begin{definition}...\end{definition}
\begin{algorithm}...\end{algorithm}
\begin{remark}...\end{remark}
\end{verbatim}
The above-mentioned coding can also include optional arguments
such as
\begin{verbatim}
\begin{theorem}[...]. Example for theorem:
\begin{theorem}[Generalized Poincare Conjecture]
Four score and seven ... created equal.
\end{theorem}
\end{verbatim}

\begin{theorem}[Generalized Poincare Conjecture]
Four score and seven years ago our fathers brought forth,
upon this continent, a new nation, conceived in Liberty,
 and dedicated to the proposition that all men are
created equal.
\end{theorem}

\subsection{Extract}
\label{subsub:extract}
Extract environment should be coded within
\begin{verbatim}
\begin{extract}..\end{extract}
\end{verbatim}

\subsection{Balancing column at last page}
\label{subsub:Balance}
For balancing the both column length at last page use :
\begin{verbatim}
\vadjust{\vfill\pagebreak}
\end{verbatim}

%\vadjust{\vfill\pagebreak}

at appropriate place in your \TeX{} file or in bibliography file.

\section{Handling references}
\label{subsub:references}
References are most easily (and correctly) generated using the
BIBTEX, which is easily invoked via
\begin{verbatim}
\bibliographystyle{juliacon}
\bibliography{ref}
\end{verbatim}
When submitting the document source (.tex) file to external
parties, the ref.bib file should be sent with it.
\cite{bezanson2017julia}

\input{bib.tex}

\end{document}

% Inspired by the International Journal of Computer Applications template

### 2024-05-16 docs/make.jl

@@ -1,98 +1,0 @@
-const IS_CI = haskey(ENV, "GITHUB_ACTIONS")
-const LIVE_MODE = "LIVE_MODE" in ARGS
-if LIVE_MODE
-    using Revise
-    Revise.revise()
-end
-
-using Peridynamics
-using Documenter
-using Literate
-using DocumenterCitations
-
-bib = CitationBibliography(joinpath(@__DIR__, "src", "refs.bib"))
-
-LIT_MD_OUT = joinpath(@__DIR__, "src", "generated")
-# LIT_NB_OUT = joinpath(@__DIR__, "..", "notebooks") #TODO
-rm(LIT_MD_OUT; recursive = true, force = true)
-# rm(LIT_NB_OUT; recursive = true, force = true) #TODO
-
-# LIT_MANUAL_IN = [
-    # "howto_single_body_analysis.jl",
-    # "howto_contact_analysis.jl",
-    # "howto_pointclouds.jl",
-    # "howto_precracks.jl",
-    # "howto_matformulations.jl",
-# ]
-# LIT_MANUAL_IN .= joinpath.(@__DIR__, "src", "literate", LIT_MANUAL_IN)
-# Literate.markdown.(LIT_MANUAL_IN, LIT_MD_OUT; credit=false)
-
-LIT_TUTORIALS_IN = [
-    "tutorial_tension_static.jl",
-    "tutorial_tension_dynfrac.jl",
-    "tutorial_tension_precrack.jl",
-    "tutorial_wave_in_bar.jl",
-]
-LIT_TUTORIALS_IN .= joinpath.(@__DIR__, "src", "literate", LIT_TUTORIALS_IN)
-Literate.markdown.(LIT_TUTORIALS_IN, LIT_MD_OUT; credit=false)
-# Literate.notebook.(LIT_TUTORIALS_IN, LIT_NB_OUT; execute = IS_CI) #TODO
-
-DocMeta.setdocmeta!(Peridynamics, :DocTestSetup, :(using Peridynamics); recursive=true)
-
-makedocs(;
-    plugins = [bib],
-    modules = [Peridynamics],
-    authors = "Kai Partmann",
-    repo = "https://github.com/kaipartmann/Peridynamics.jl/blob/{commit}{path}#{line}",
-    sitename = "Peridynamics.jl",
-    format = Documenter.HTML(;
-        prettyurls = get(ENV, "CI", "false") == "true",
[…]

### 2024-05-16 docs/servedocs.jl

@@ -1,26 +1,0 @@
-#-------------------------------------------------------------------------------------------
-# RUN THIS SCRIPT ONLY FOR LOCAL DEVELOPMENT OF THE DOCUMENTATION!
-#-------------------------------------------------------------------------------------------
-
-# Root of the repository
-const REPO_ROOT = dirname(@__DIR__)
-
-# Make sure the docs environment is active and instantiated
-import Pkg
-Pkg.activate(@__DIR__)
-Pkg.instantiate()
-
-# Communicate with make.jl that docs are build in live mode
-push!(ARGS, "LIVE_MODE")
-
-using LiveServer
-servedocs(;
-    # Documentation root where make.jl and src/ are located
-    foldername = joinpath(REPO_ROOT, "docs"),
-    # Watch the src folder so docstrings can be Revise'd
-    include_dirs = [joinpath(REPO_ROOT, "src")],
-    # Skip the folder where Literate.jl output is written. This is needed
-    # to avoid infinite loops where running make.jl updates watched files,
-    # which then triggers a new run of make.jl etc...
-    skip_dirs = [joinpath(REPO_ROOT, "docs", "src", "generated")],
-)

### 2024-05-16 docs/src/literate/TODO_tutorial_multi_material.jl

@@ -1,53 +1,0 @@
-# TODO
-
-using Peridynamics
-using GLMakie
-
-lxy = 1
-lz = 0.1lxy
-nz = 5
-dx = lz/nz
-pc = PointCloud(lxy, lxy, lz, dx)
-
-E_variation = 60e3:250e3
-rho_variation = 2e-6:8e-6
-epsilon_c_variation = 0.002:0.00001:0.01
-
-pore_radius_variation = 0.05lxy:0.0001lxy:0.1lxy
-
-n_pores = 200
-
-mats = Tuple(BBMaterial(horizon=3dx, rho=rand(rho_variation), E=rand(E_variation), epsilon_c=rand(epsilon_c_variation)) for _ in 1:n_pores)
-
-matofpoint = ones(Int, pc.n_points)
-radius_of_pores = zeros(n_pores)
-
-for i in 1:n_pores
-    # get random pore position inside model
-	pos = [rand(-lxy/2:0.1dx:lxy/2), rand(-lxy/2:0.1dx:lxy/2), rand(-lz/2:0.1dx:lz/2)]
-    # get random pore radius
-	rad = rand(pore_radius_variation)
-	# add pore radius to radius vector
-    radius_of_pores[i] = rad
-	# get points inside of pore
-    for (point_id, point) in enumerate(eachcol(pc.position))
-        dist = sqrt((point[1]-pos[1])^2 + (point[2]-pos[2])^2 + (point[3]-pos[3])^2)
-        if dist ≤ rad
-            # assign material of pore to these points
-            matofpoint[point_id] = i
-        end
-    end
-end
-
-# mat = MultiMaterial(mats, matofpoint)
-
-pore_size = radius_of_pores[matofpoint]
-
-#-
-fig = Figure(resolution = (1000,1000), figure_padding=0) #src
-ax = Axis3(fig[1,1]; aspect = :data, elevation=0.37π, azimuth=0.45π) #src
-hidespines!(ax) #src
-hidedecorations!(ax) #src
-meshscatter!(ax, pc.position; markersize=0.5dx, color=pore_size, colormap=:lightrainbow) #src
-save(joinpath(@__DIR__, "..", "assets", "multi_material_test.png"), fig; px_per_unit=3)
-fig

### 2024-05-16 docs/src/literate/howto_contact_analysis.jl

@@ -1,22 +1,0 @@
-# # [Contact analysis](@id howto_contact_analysis)
-# Short guide on how to run a peridynamic analysis with contact of multiple bodies.
-
-# ## Steps
-# ### 1. Define the bodies
-# To define the bodies, create [`BodySetup`](@ref) instances. Each `BodySetup` is created
-# with [step 1-4 from single body analysis guide](@ref howto_single_body_analysis).
-# Optionally choose if a body should contribute to the automatic calculation of the stable
-# time step with the `calc_timestep` keyword. Be careful if you use this option!
-# ### 2. Define contact
-# Define the contact of two bodies by creating a [`Contact`](@ref) instance.
-# ### 3. Choose temporal discretization settings
-# Create a [`VelocityVerlet`](@ref) instance.
-# ### 4. Choose export settings
-# Create a [`ExportSettings`](@ref) instance.
-# ### 5. Create the simulation job
-# Create a [`PDContactAnalysis`](@ref) instance and choose a simulation name.
-# ### 6. Run the simulation job
-# Run the simulation with the [`submit`](@ref) function.
-
-# ## Examples
-# Please refer to the [Peridynamics.jl logo tutorial](@ref tutorial_logo).

### 2024-05-16 docs/src/literate/howto_precracks.jl

@@ -1,47 +1,0 @@
-# # [Predefined cracks](@id howto_precracks)
-# Short guide on how to define initial cracks.
-
-# ## Definition with two point sets
-# All interactions of points in set $a$ with points in set $b$ will be set as failed.
-
-# ## Example
-
-#-
-using Peridynamics #hide
-l = 1.0
-a = 0.1l # crack length
-Δx = l / 50
-pc = PointCloud(l, l, 0.1l, Δx)
-# ![](../assets/tutorial_tension_1.png) #md
-
-#-
-# We define a crack length `a` and specify the point sets of points that should not
-# interact with each other.
-# ##### Conditions for the coordinates of the point sets
-# ###### First set:
-# ```math
-# x_p \leq -\frac{l}{2}+a \; ,
-# ```
-# ```math
-# 0 \leq y_p \leq 6\Delta x \; .
-# ```
-set_a = findall(p -> p[1] ≤ -l/2+a && 0 ≤ p[2] ≤ 6Δx, eachcol(pc.position))
-
-# ###### Second set:
-# ```math
-# x_p \leq -\frac{l}{2}+a \; ,
-# ```
-# ```math
-# -6\Delta x \leq y_p < 0 \; ,
-# ```
-
-
-#-
-set_b = findall(p -> p[1] ≤ -l/2+a && -6Δx ≤ p[2] < 0, eachcol(pc.position))
-
-#-
-# ![](../assets/tutorial_tension_2.png) #md
-
-#-
-# The initial crack is specified as a [`PreCrack`](@ref) instance:
-precrack = PreCrack(set_a, set_b)

### 2024-05-16 docs/src/literate/tutorial_tension_dynfrac.jl

@@ -1,54 +1,0 @@
-# # [Mode I tension dynamic with fracture](@id tutorial_tension_dynfrac)
-
-#-
-# Import the package:
-using Peridynamics
-using Peridynamics.AbaqusMeshConverter
-
-#-
-# Read and convert the [Abaqus FEM mesh of a tensile test](https://github.com/kaipartmann/Peridynamics.jl/blob/main/docs/src/assets/TensileTestMesh.inp)
-# into a point cloud for the peridynamic model:
-## insert your correct path to the downloaded mesh file!
-pos, vol, pointsets = read_inp(joinpath(@__DIR__, "..", "assets", "TensileTestMesh.inp"))
-# ![](../assets/TensileTestMesh.png)
-
-#-
-# Create a body with the points from the mesh: (The bond-based material model is used here.)
-b = Body(BBMaterial(), pos, vol)
-
-# Convert the element sets defined in Abaqus into point sets of the Body:
-point_set!(b, :top, pointsets["top"])
-point_set!(b, :bottom, pointsets["bottom"])
-
-# Specify the material parameters as:
-
-# | material parameter | value |
-# |:--------|:-------------|
-# | Horizon $ δ $ | $0.01 \, \mathrm{m}$ |
-# | Density $ρ$ | $ 2700 \,\mathrm{kg}\,\mathrm{m}^{-3}$ |
-# | Young's modulus $E$ | $ 70 \cdot 10^{9} \, \mathrm{Pa}$ |
-# | Griffith's parameter $G_c$ | $100 \, \mathrm{N} \, \mathrm{m}^{-1}$ |
-
-material!(b; horizon=0.01, rho=2700, E=70e9, Gc=100)
-
-# As loading condition for the specimen, a constant velocity of $0.6 \, \mathrm{m}\,\mathrm{s}^{-1}$ in $x$-direction is set for the bottom and top.
-velocity_bc!(t -> -0.6, b, :bottom, 1)
-velocity_bc!(t -> 0.6, b, :top, 1)
-
-# Set the number of time steps for the Velocity Verlet algorithm to 500 time steps:
-vv = VelocityVerlet(steps=500)
-
-# Define the storage path:
-root = joinpath(@__DIR__, "results", "tension_dynamic_fracture")
-
-# Create the job:
-job = Job(b, vv; path=root)
-
-#-
-# Submit the job to start simulations:
-#md # ```julia
-#md # submit(job)
-#md # ```
-
[…]

### 2024-05-16 docs/src/literate/tutorial_tension_precrack.jl

@@ -1,126 +1,0 @@
-# # [Mode I tension with predefined crack](@id tutorial_tension_precrack)
-
-# Import the package:
-using Peridynamics
-using GLMakie #src
-using LaTeXStrings #src
-
-# First some geometrical parameters are defined.
-# These are edge length `l`, point spacing `Δx` and crack length `a`.
-l, Δx, a = 100.0, 100/50, 50.0
-
-# Now a cuboid body with the specified edge lengths and a thickness of one tenth thereof is
-# created using the bond-based material model.
-pos, vol = uniform_box(l, l, 0.1l, Δx)
-b = Body(BBMaterial(), pos, vol)
-
-#-
-fig = Figure(resolution = (1000,500), figure_padding=0) #src
-ax = Axis3(fig[1,1]; aspect = :data) #src
-hidespines!(ax) #src
-hidedecorations!(ax) #src
-meshscatter!(ax, pc.position; markersize=0.5Δx, color=:grey80) #src
-arrows!(ax, Point3[(0,-l/2,-0.08l),(-l/2,0,-0.08l),(-l/2*1.03,l/2*1.03,0)], #src
-        Vec3[(0.1,0,0),(0,0.1,0),(0,0,0.05)], arrowsize=(0.03,0.03,0.05), #src
-        linewidth=0.01, color=:black) #src
-linesegments!(ax, Point3[(0,-l/2,-0.1l), (0,-l/2,-0.06l), (-l/2,0,-0.1l), #src
-              (-l/2,0,-0.06l), (-l/2*1.03-0.02,l/2*1.03,0), #src
-              (-l/2*1.03+0.02,l/2*1.03,0)]; linewidth=4, color=:black) #src
-text!(ax, L"\mathbf{x}", position=Point3(0.18,-l/2,-0.08l), fontsize=30, #src
-      align=(:center,:center), color=:black) #src
-text!(ax, L"\mathbf{y}", position=Point3(-l/2,0.18,-0.08l), fontsize=30, #src
-      align=(:center,:center), color=:black) #src
-text!(ax, L"\mathbf{z}", position=Point3(-l/2*1.03,l/2*1.03,0.13), fontsize=30, #src
-      align=(:center,:center), color=:black) #src
-# save(joinpath(@__DIR__, "..", "assets", "tutorial_tension_1.png"), fig; px_per_unit=3) #src
-fig #src
-
-#-
[…]

### 2024-05-16 docs/src/literate/tutorial_tension_static.jl

@@ -1,55 +1,0 @@
-# # [Mode I tension quasi-static](@id tutorial_tension_static)
-
-#-
-# Import the package:
-using Peridynamics
-
-#-
-# Read and convert the [Abaqus FEM mesh of a tensile test](https://github.com/kaipartmann/Peridynamics.jl/blob/main/docs/src/assets/TensileTestMesh.inp):
-## insert your correct path to the downloaded mesh file!
-pc = read_inp(joinpath(@__DIR__, "..", "assets", "TensileTestMesh.inp"))
-# ![](../assets/TensileTestMesh.png)
-
-#-
-# Do not allow failure in the entire point cloud:
-pc.failure_flag .= false
-
-#-
-# Define a bond-based material with
-# - Horizon $\delta = 0.01\,\mathrm{m}$
-# - Density $\rho = 2700\,\mathrm{kg}\,\mathrm{m}^{-3}$
-# - Youngs modulus $E = 70 \times 10^9 \, \mathrm{Pa}$
-# - Griffith's parameter $G_c = 100 \, \mathrm{N} \, \mathrm{m}^{-1}$
-mat = BBMaterial(; horizon=0.01, rho=2700, E=70e9, Gc=100)
-
-#-
-# As loading condition for the specimen, a constant force density of $1 \times 10^9 \, \mathrm{N}\,\mathrm{m}^{-3}$ in $x$-direction is set for the bottom and top.
-# Note, that element sets defined in Abaqus are converted to `point_sets` of the `PointCloud`.
-bcs = [
-    ForceDensityBC(t -> -1e9, pc.point_sets["bottom"], 1),
-    ForceDensityBC(t -> 1e9, pc.point_sets["top"], 1),
-]
-
-#-
-# We set the number of time steps for the dynamic relaxation algorithm to 500 time steps.
-dr = DynamicRelaxation(500)
-
-#-
-# The results of our analysis should be saved in the directory `"results/TensileTestStatic"` every 10'th time step.
-name = "TensileTestStatic"
-path = joinpath("results", name)
-!ispath(path) && mkpath(path) # create the path if it does not exist
-es = ExportSettings(path, 10)
-
-#-
-# Run a single body analysis:
-#-
-job = PDSingleBodyAnalysis(name=name, pc=pc, mat=mat, bcs=bcs, td=dr, es=es)
-
-#-
-#md # ```julia
-#md # submit(job)
-#md # ```
-
-# ![](../assets/tension_static.gif)
[…]

### 2024-05-16 docs/src/literate/tutorial_wave_in_bar.jl

@@ -1,63 +1,0 @@
-# # Pressure wave in bar
-
-# In this tutorial, a cuboid bar is created.
-# A velocity pulse in the form of one period of a sine wave is applied to create
-# a pressure wave that propagates through the bar.
-#
-# First import the Peridynamics.jl package:
-using Peridynamics
-
-# To get started, some parameters used to for this simulation are defined.
-# These are the length of the bar `lx`, the width and height `lyz` and the number of
-# points in the width `npyz`.
-
-lx = 0.2
-lyz = 0.002
-npyz = 4
-
-# With these parameters the point spacing can be calculated:
-Δx = lyz / npyz
-# A cuboid body according to the ordinary state-based model with the specified dimensions
-# and point spacing is then created:
-pos, vol = uniform_box(lx, lyz, lyz, Δx)
-body = Body(OSBMaterial(), pos, vol)
-# Failure is prohibited throughout the body:
-failure_permit!(body, false)
-# Following material parameters are specified:
-
-# | material parameter | value |
-# |:--------|:-------------|
-# | Horizon $ δ $ | $3.015 \cdot Δx$ |
-# | Density $ρ$ | $ 7850\,\mathrm{kg}\,\mathrm{m}^{-3}$ |
-# | Young's modulus $E$ | $ 210 \, \mathrm{GPa}$ |
-# | Poisson's ratio $ν$ | $0.25$ |
-# | critical strain $ε_c$ | $0.01$ |
-material!(body, horizon=3.015Δx, rho=7850.0, E=210e9, nu=0.25, epsilon_c=0.01)
-# Point set `:left` including the first row of points in x-direction is created:
-point_set!(x -> x < -lx / 2 + 1.2Δx, body, :left)
-# The velocity boundary condition of the form
-# ```math
-#     {v}_x (t) =
-#     \begin{cases}
-#         v_\mathrm{max} \cdot \sin(2\pi \cdot \frac{t}{T}) \qquad
-#         & \forall \; 0 \leq t \leq T \\
-#         0 &\text{else}
-#     \end{cases}
-# ```
-# is applied to point set `:left`. The parameters used for this excitation are period
-# length `T` and amplitude `vmax`.
-T, vmax = 1.0e-5, 2.0
-velocity_bc!(t -> t < T ? vmax * sin(2π / T * t) : 0.0, body, :left, :x)
-# ![](../assets/impact_velocity.png)
-# The Velocity Verlet algorithm is used as time integration method and 2000 time steps
[…]

### 2024-05-16 src/AbaqusMeshConverter/AbaqusMeshConverter.jl

@@ -1,112 +1,0 @@
-module AbaqusMeshConverter
-
-using StaticArrays
-using LinearAlgebra
-using AbaqusReader: abaqus_read_mesh
-
-const SUPPORTED_ELEMENT_TYPES = [:Tet4, :Hex8]
-
-export read_inp
-
-function get_points(nodes::Dict{Int, Vector{Float64}}, elements::Dict{Int, Vector{Int}},
-                    element_types::Dict{Int, Symbol})
-    nel = length(elements)
-    midpoints = zeros(3, nel)
-    volumes = zeros(nel)
-    for i in 1:nel
-        T = element_types[i]
-        if T in SUPPORTED_ELEMENT_TYPES
-            if T == :Tet4
-                nodeids = elements[i]
-                if length(nodeids) == 4
-                    a = nodes[nodeids[1]]
-                    b = nodes[nodeids[2]]
-                    c = nodes[nodeids[3]]
-                    d = nodes[nodeids[4]]
-                    @views midpoints[:, i] = midpoint(a, b, c, d)
-                    volumes[i] = tetvol(a, b, c, d)
-                else
-                    throw(DimensionMismatch("4 nodes needed for element of type Tet4!"))
-                end
-            end
-            if T == :Hex8
-                nodeids = elements[i]
-                if length(nodeids) == 8
-                    n1 = nodes[nodeids[1]]
-                    n2 = nodes[nodeids[2]]
-                    n3 = nodes[nodeids[3]]
-                    n4 = nodes[nodeids[4]]
-                    n5 = nodes[nodeids[5]]
-                    n6 = nodes[nodeids[6]]
-                    n7 = nodes[nodeids[7]]
-                    n8 = nodes[nodeids[8]]
-                    @views midpoints[:, i] = midpoint(n1, n2, n3, n4, n5, n6, n7, n8)
-                    volume1 = tetvol(n1, n2, n4, n5)
-                    volume2 = tetvol(n2, n3, n4, n7)
-                    volume3 = tetvol(n2, n5, n6, n7)
-                    volume4 = tetvol(n4, n5, n7, n8)
-                    volume5 = tetvol(n2, n4, n5, n7)
-                    volumes[i] = volume1 + volume2 + volume3 + volume4 + volume5
-                else
-                    throw(DimensionMismatch("8 nodes needed for element of type Hex8"))
-                end
-            end
-        else
[…]

### 2024-05-16 src/Peridynamics.jl

@@ -1,122 +1,0 @@
-module Peridynamics
-
-using Base.Threads, Printf, LinearAlgebra, StaticArrays, NearestNeighbors, ProgressMeter,
-      WriteVTK, TimerOutputs, MPI, PrecompileTools
-@static if Sys.islinux()
-    using ThreadPinning
-end
-
-import LibGit2, Dates
-
-# Abstract types
-export AbstractMaterial, AbstractBondSystemMaterial, AbstractSpatialSetup, AbstractBody,
-       AbstractMultibodySetup, AbstractParameterSetup, AbstractPointParameters,
-       AbstractTimeSolver, AbstractJob, AbstractSystem, AbstractPredefinedCrack,
-       AbstractCorrection, AbstractStorage, AbstractCondition
-
-# Material models
-export BBMaterial, CKIMaterial, NOSBMaterial, OSBMaterial
-
-# Systems related types
-export BondSystem, NoCorrection, EnergySurfaceCorrection
-
-# Discretization
-export Body, point_set!, failure_permit!, material!, velocity_bc!, velocity_ic!,
-       forcedensity_bc!, precrack!, MultibodySetup, contact!, uniform_box
-
-# Running simulations
-export VelocityVerlet, Job, submit
-
-# Post processing and helpers
-export read_vtk, process_each_export, mpi_isroot, force_mpi_run!, force_threads_run!,
-       enable_mpi_timers!, disable_mpi_timers!, @mpitime, @rootdo
-
-function __init__()
-    init_mpi()
-    @static if Sys.islinux()
-        mpi_run() || pinthreads(:cores; force=false)
-    end
-    BLAS.set_num_threads(1)
-    return nothing
-end
-
-abstract type AbstractMaterial end
-abstract type AbstractSpatialSetup end
-abstract type AbstractBody{T<:AbstractMaterial} <: AbstractSpatialSetup end
-abstract type AbstractMultibodySetup{T<:AbstractMaterial} <: AbstractSpatialSetup end
-abstract type AbstractParameterSetup end
-abstract type AbstractPointParameters <: AbstractParameterSetup end
-abstract type AbstractParamSpec end
-abstract type AbstractTimeSolver end
-abstract type AbstractJob end
-abstract type AbstractOptions end
-abstract type AbstractSystem end
-abstract type AbstractPredefinedCrack end
-abstract type AbstractBodyChunk{S<:AbstractSystem,T<:AbstractMaterial} end
-abstract type AbstractParameterHandler <: AbstractParameterSetup end
[…]

### 2024-05-16 src/VtkReader/VtkReader.jl

@@ -1,314 +1,0 @@
-module VtkReader
-
-using Base64: base64decode
-using CodecZlib: ZlibDecompressor
-using LightXML: LightXML, XMLDocument, XMLElement, parse_string, attribute, child_elements,
-                free, find_element, get_elements_by_tagname
-
-export read_vtk
-
-const HEADER_TYPE = UInt64
-const DATATYPE_MAPPING = Dict("Float64" => Float64, "Int64" => Int64)
-
-abstract type AbstractDataArray end
-
-struct DataArray{T,N} <: AbstractDataArray
-    name::Symbol
-    offset::Int
-    function DataArray(xml::XMLElement)
-        if LightXML.name(xml) != "DataArray"
-            throw(ArgumentError("xml element has to be a DataArray!"))
-        end
-        type_str = attribute(xml, "type"; required=true)
-        name_str = attribute(xml, "Name"; required=true)
-        noc_str = attribute(xml, "NumberOfComponents"; required=true)
-        offset_str = attribute(xml, "offset"; required=true)
-        format_str = attribute(xml, "format"; required=true)
-        if format_str != "appended"
-            throw(ArgumentError("only DataArrays with format appended are valid!\n"))
-        end
-        if !haskey(DATATYPE_MAPPING, type_str)
-            msg = "data of type $type_str for data $name_str not supported!\n"
-            throw(ArgumentError(msg))
-        end
-        type = DATATYPE_MAPPING[type_str]
-        name = Symbol(name_str)
-        noc = parse(Int, noc_str)
-        offset = parse(Int, offset_str)
-        return new{type,noc}(name, offset)
-    end
-end
-
-struct PDataArray{T,N} <: AbstractDataArray
-    name::Symbol
-    das::Vector{DataArray{T,N}}
-    function PDataArray(das::Vector{DataArray{T,N}}) where {T,N}
-        name = first(das).name
-        return new{T,N}(name, das)
-    end
-end
-
-element_type(::DataArray{T,N}) where {T,N} = T
-element_type(::PDataArray{T,N}) where {T,N} = T
-
-function get_raw_xml_and_data(file::String)
-    raw_file = read(file, String)
-
-    # find appended data
-    marker = findfirst("<AppendedData encoding=\"raw\">", raw_file)
-    if isnothing(marker)
[…]

### 2024-05-16 src/auxiliary/function_arguments.jl

@@ -1,25 +1,0 @@
-function get_method_of_function(f::F) where {F<:Function}
-    func_method = collect(methods(f))
-    if length(func_method) > 1
-        msg =  "multiple methods defined for specified function $(nameof(f))!\n\n"
-        msg *= "Better use anonymous functions as an argument!\n"
-        throw(ArgumentError(msg))
-    end
-    return first(func_method)
-end
-
-function get_argument_names_of_function(func_method::Method)
-    argnames = Base.method_argnames(func_method)
-    isempty(argnames) && return argnames
-    first(argnames) === Symbol("#self#") && popfirst!(argnames)
-    return argnames
-end
-
-function check_kwargs(p::Dict{Symbol,Any}, allowed_kwargs::NTuple{N,Symbol}) where {N}
-    for key in keys(p)
-        if !in(key, allowed_kwargs)
-            throw(ArgumentError("keyword $key not allowed!\n"))
-        end
-    end
-    return nothing
-end

### 2024-05-16 src/auxiliary/io.jl

@@ -1,46 +1,0 @@
-
-function get_export_fields(::Type{S}, o::Dict{Symbol,Any}) where {S}
-    local _fields::NTuple{N,Symbol} where {N}
-    if haskey(o, :fields)
-        _fields = o[:fields]
-    else
-        _fields = DEFAULT_EXPORT_FIELDS
-    end
-
-    fields = [field for field in _fields]
-    check_export_fields(S, fields)
-
-    return fields
-end
-
-function check_export_fields(::Type{S}, fields::Vector{Symbol}) where {S}
-    allowed_fields = point_data_fields(S)
-    for f in fields
-        if !in(f, allowed_fields)
-            msg = "unknown point data field `:$(f)` specified for export!\n"
-            msg *= "All point data fields of $S:\n"
-            for allowed_name in allowed_fields
-                msg *= "  - $allowed_name\n"
-            end
-            throw(ArgumentError(msg))
-        end
-    end
-    return nothing
-end
-
-function _export_results(b::AbstractBodyChunk, chunk_id::Int, n_chunks::Int,
-                         options::AbstractOptions, n::Int, t::Float64)
-    filename = joinpath(options.vtk, @sprintf("timestep_%06d", n))
-    position = get_loc_position(b)
-    pvtk_grid(filename, position, b.cells; part=chunk_id, nparts=n_chunks) do vtk
-        for field in options.fields
-            vtk[string(field), VTKPointData()] = get_loc_point_data(b.storage, b.ch, field)
-        end
-        vtk["time", VTKFieldData()] = t
-    end
-    return nothing
-end
-
-@inline function get_loc_position(b::AbstractBodyChunk)
-    return @views b.storage.position[:, 1:b.ch.n_loc_points]
-end

### 2024-05-16 src/auxiliary/logs.jl

@@ -1,97 +1,0 @@
-const QUIET = Ref(false)
-
-@inline quiet() = QUIET[]
-@inline set_quiet!(b::Bool) = (QUIET[] = b; return nothing)
-
-is_logging(io) = isa(io, Base.TTY) == false || (get(ENV, "CI", nothing) == "true")
-
-@inline progress_enabled() = !is_logging(stderr) && !quiet()
-
-function init_logs(options::AbstractOptions)
-    options.exportflag || return nothing
-    mpi_isroot() || return nothing
-    mkpath(options.vtk)
-    init_logfile(options)
-    return nothing
-end
-
-function init_logfile(options::AbstractOptions)
-    open(options.logfile, "w+") do io
-        write(io, get_logfile_head())
-        write(io, peridynamics_banner())
-        write(io, get_run_info())
-    end
-    return nothing
-end
-
-function add_to_logfile(options::AbstractOptions, msg::AbstractString)
-    open(options.logfile, "a") do io
-        write(io, msg)
-    end
-    return nothing
-end
-
-function get_logfile_head()
-    msg = "LOGFILE CREATED ON "
-    msg *= Dates.format(Dates.now(), "yyyy-mm-dd, HH:MM:SS")
-    msg *= "\n"
-    msg *= get_git_info()
-    msg *= "\n"
-    return msg
-end
-
-function get_git_info()
-    git_info = try
-        _get_git_info()
-    catch
-        ""
-    end
-    return git_info
-end
-
-function _get_git_info()
-    repo = LibGit2.GitRepo(pkgdir(@__MODULE__))
-    head_name = LibGit2.headname(repo)
-    head_oid = LibGit2.head_oid(repo)
-    git_info = "GIT-INFO: "
-    if head_name == "main"
-        git_info *= "commit: $head_oid"
-    else
-        git_info *= "branch: $head_name, commit: $head_oid"
-    end
-    for tag in LibGit2.tag_list(repo)
-        if LibGit2.target(LibGit2.GitObject(repo, tag)) == head_oid
-            git_info *= "\n          tag: $tag"
-            break
-        end
-    end
-    if LibGit2.isdirty(repo)
-        git_info *= "\n          local changes detected!"
-    end
-    git_info *= "\n"
-    return git_info
-end
-
-function peridynamics_banner()
-    msg = raw"""
[…]

### 2024-05-16 src/auxiliary/mpi.jl

@@ -1,129 +1,0 @@
-const MPI_INITIALIZED = Ref(false)
-const MPI_RUN = Ref(false)
-const MPI_RUN_FORCED = Ref(false)
-const MPI_ISROOT = Ref(false)
-const TO = TimerOutput()
-
-@inline mpi_comm() = MPI.COMM_WORLD
-@inline mpi_rank() = MPI.Comm_rank(MPI.COMM_WORLD)
-@inline mpi_nranks() = MPI.Comm_size(MPI.COMM_WORLD)
-@inline mpi_run() = MPI_RUN[]
-@inline mpi_chunk_id() = mpi_rank() + 1
-@inline mpi_isroot() = MPI_ISROOT[]
-
-"""
-    force_mpi_run!()
-
-After this function is called, all following simulations will use MPI.
-"""
-@inline function force_mpi_run!()
-    MPI_RUN[] = true
-    MPI_RUN_FORCED[] = true
-    return nothing
-end
-
-"""
-    force_threads_run!()
-
-After this function is called, all following simulations will use multithreading.
-"""
-@inline function force_threads_run!()
-    MPI_RUN[] = false
-    MPI_RUN_FORCED[] = true
-    return nothing
-end
-
-@inline function set_mpi_run!(b::Bool)
-    MPI_RUN_FORCED[] && return nothing
-    MPI_RUN[] = b
-    return nothing
-end
-
-function init_mpi()
-    if !MPI_INITIALIZED[]
-        MPI.Init(finalize_atexit=true)
-        MPI_INITIALIZED[] = true
-    end
-    MPI_ISROOT[] = mpi_rank() == 0
-    set_mpi_run!(mpi_run_initial_check())
-    return nothing
-end
-
-function mpi_run_initial_check()
-    MPI_RUN_FORCED[] && return MPI_RUN[]
-    haskey(ENV, "MPI_LOCALRANKID") && return true
-    mpi_nranks() > 1 && return true
-    nthreads() > 1 && return false
-    for env_key in keys(ENV)
-        if contains(env_key, "SLURM")
-            msg = "will fall back to multithreading, due to "
-            msg *= "`nranks` = `nthreads` = 1\n"
-            msg *= "If you want to run MPI with only 1 rank, use `force_mpi_run!()`"
-            @warn msg
-            return false
-        end
-    end
-    return false
-end
-
-function log_mpi_timers(options::AbstractOptions)
-    options.exportflag || return nothing
[…]

### 2024-05-16 src/auxiliary/precompile_workload.jl

@@ -1,72 +1,0 @@
-@setup_workload begin
-    if mpi_run()
-        msg = "precompilation triggered during mpirun!\n"
-        msg *= "The precompilation is not safe to use with MPI!\n"
-        msg *= "Trigger package precompilation manually and then restart the mpirun!\n"
-        error(msg)
-    end
-    l, Δx, δ, a = 1.0, 1 / 4, 3.015 / 4, 0.5
-    root = joinpath(@__DIR__, "temp_precompilation")
-    pos, vol = uniform_box(l, l, l, Δx)
-    path_bb = joinpath(root, "BB")
-    path_osb = joinpath(root, "OSB")
-    path_nosb = joinpath(root, "NOSB")
-
-    @compile_workload begin
-        b1 = Body(BBMaterial(), pos, vol)
-        material!(b1; horizon=3.015Δx, E=2.1e5, rho=8e-6, Gc=2.7)
-        point_set!(p -> p[1] ≤ -l / 2 + a && 0 ≤ p[2] ≤ 2δ, b1, :set_a)
-        point_set!(p -> p[1] ≤ -l / 2 + a && -2δ ≤ p[2] < 0, b1, :set_b)
-        precrack!(b1, :set_a, :set_b)
-        point_set!(y -> y > l / 2 - Δx, b1, :set_top)
-        point_set!(y -> y < -l / 2 + Δx, b1, :set_bottom)
-        velocity_ic!(b1, :set_bottom, :x, 0)
-        velocity_ic!(b1, :set_bottom, :y, 0)
-        velocity_ic!(b1, :set_bottom, :z, 0)
-        velocity_ic!(b1, :set_top, 1, 0)
-        velocity_ic!(b1, :set_top, 2, 0)
-        velocity_ic!(b1, :set_top, 3, 0)
-        velocity_bc!(t -> 0, b1, :set_bottom, :x)
-        velocity_bc!(t -> -30, b1, :set_bottom, :y)
-        velocity_bc!(t -> 0, b1, :set_bottom, :z)
-        velocity_bc!(t -> 0, b1, :set_top, 1)
-        velocity_bc!(t -> 30, b1, :set_top, 2)
-        velocity_bc!(t -> 0, b1, :set_top, 3)
-        forcedensity_bc!(t -> 0, b1, :set_top, :x)
[…]

### 2024-05-16 src/auxiliary/process_each_export.jl

@@ -1,104 +1,0 @@
-const PROCESS_EACH_EXPORT_KWARGS = (:serial,)
-
-function process_each_export(f::F, vtk_path::AbstractString; kwargs...) where {F<:Function}
-    o = Dict{Symbol,Any}(kwargs)
-    check_kwargs(o, PROCESS_EACH_EXPORT_KWARGS)
-    check_process_function(f)
-    serial = get_process_each_export_options(o)
-    vtk_files = find_vtk_files(vtk_path)
-    if serial
-        process_each_export_serial(f, vtk_files)
-    elseif mpi_run()
-        process_each_export_mpi(f, vtk_files)
-    else
-        process_each_export_threads(f, vtk_files)
-    end
-    return nothing
-end
-
-function process_each_export(f::F, job::Job; kwargs...) where {F<:Function}
-    process_each_export(f, job.options.vtk; kwargs...)
-    return nothing
-end
-
-function get_process_each_export_options(o::Dict{Symbol,Any})
-    if haskey(o, :serial)
-        serial::Bool = Bool(o[:serial])
-    else
-        serial = false
-    end
-    return serial
-end
-
-function check_process_function(f::F) where {F<:Function}
-    func_method = get_method_of_function(f)
-    args = get_argument_names_of_function(func_method)
-    if length(args) != 3
-        msg = "wrong arguments for processing function!\n"
-        msg *= "The processing function needs 3 args:\n"
-        msg *= "  - ref_result::Dict{Symbol,VecOrMat}: results of the initial export\n"
-        msg *= "  - result::Dict{Symbol,VecOrMat}: results of the processed time step\n"
-        msg *= "  - file_id::Int: number / id of the processed export\n"
-        throw(ArgumentError(msg))
-    end
-    return nothing
-end
-
-function find_vtk_files(path::AbstractString)
-    isdir(path) || throw(ArgumentError("invalid path $path specified!\n"))
-    all_files = readdir(path; join=true)
-    pvtu_files = filter(x -> endswith(x, ".pvtu"), all_files)
-    isempty(pvtu_files) && throw(ArgumentError("no pvtu-files in path: $path\n"))
-    return pvtu_files
-end
-
-function process_step(f::F, ref_result::Dict{Symbol,T}, file::AbstractString,
-                      file_id::Int) where {F<:Function,T}
-    result = read_vtk(file)
-    try
-        f(ref_result, result, file_id)
-    catch err
[…]

### 2024-05-16 src/conditions/boundary_conditions.jl

@@ -1,196 +1,0 @@
-struct SingleDimBC{F<:Function} <: AbstractCondition
-    fun::F
-    field::Symbol
-    point_set::Symbol
-    dim::UInt8
-end
-
-@inline function (b::SingleDimBC{F})(t::Float64) where {F}
-    value::Float64 = b.fun(t)
-    return value
-end
-
-function override_eachother(a::SingleDimBC, b::SingleDimBC)
-    same_field = a.field === b.field
-    same_point_set = a.point_set === b.point_set
-    same_dim = a.dim == b.dim
-    return same_field && same_point_set && same_dim
-end
-
-function apply_bcs!(b::AbstractBodyChunk, time::Float64)
-    for bc in b.sdbcs
-        apply_bc!(b.storage, b.psets, bc, time)
-    end
-    for bc in b.pdsdbcs
-        apply_bc!(b.storage, b.psets, bc, b.system.position, time)
-    end
-    return nothing
-end
-
-function apply_bc!(s::AbstractStorage, psets::Dict{Symbol,Vector{Int}},
-                   bc::SingleDimBC{F}, time::Float64) where {F}
-    value = bc(time)
-    isnan(value) && return nothing
-    apply_sdbc!(get_point_data(s, bc.field), value, bc.dim, psets[bc.point_set])
-    return nothing
-end
-
-@inline function apply_sdbc!(field::Matrix{Float64}, value::Float64, dim::UInt8,
-                             point_ids::Vector{Int})
-    @simd for i in point_ids
-        @inbounds field[dim, i] = value
-    end
-    return nothing
-end
-
-struct PosDepSingleDimBC{F<:Function} <: AbstractCondition
-    fun::F
-    field::Symbol
-    point_set::Symbol
-    dim::UInt8
-end
-
-@inline function (b::PosDepSingleDimBC{F})(p::AbstractVector, t::Float64) where {F}
-    value::Float64 = b.fun(p, t)
-    return value
-end
-
-function override_eachother(a::PosDepSingleDimBC, b::PosDepSingleDimBC)
-    same_field = a.field === b.field
-    same_point_set = a.point_set === b.point_set
-    same_dim = a.dim == b.dim
-    return same_field && same_point_set && same_dim
-end
-
-function apply_bc!(s::AbstractStorage, psets::Dict{Symbol,Vector{Int}},
[…]

### 2024-05-16 src/conditions/initial_conditions.jl

@@ -1,70 +1,0 @@
-"""
-
-"""
-struct SingleDimIC <: AbstractCondition
-    value::Float64
-    field::Symbol
-    point_set::Symbol
-    dim::UInt8
-end
-
-function override_eachother(a::SingleDimIC, b::SingleDimIC)
-    same_field = a.field === b.field
-    same_point_set = a.point_set === b.point_set
-    same_dim = a.dim == b.dim
-    return same_field && same_point_set && same_dim
-end
-
-function apply_initial_conditions!(b::AbstractBodyChunk, body::AbstractBody)
-    apply_single_dim_ic!(b, body)
-    return nothing
-end
-
-@inline function apply_single_dim_ic!(b::AbstractBodyChunk, body::AbstractBody)
-    for ic in body.single_dim_ics
-        apply_ic!(b, ic)
-    end
-    return nothing
-end
-
-function apply_ic!(b::AbstractBodyChunk, ic::SingleDimIC)
-    for point_id in b.psets[ic.point_set]
-        setindex!(get_point_data(b.storage, ic.field), ic.value, ic.dim, point_id)
-    end
-    return nothing
-end
-
-"""
-    velocity_ic!(body, set, dim, value)
-
-Specifies initital conditions for the velocity of points in point set `set` on `body`
-
-# Arguments
-
-- `body::AbstractBody`: Peridynamic body
-- `set::Symbol`: Point set on `body`
-- `dim::Union{Integer,Symbol}`: Direction of velocity
-- `value::Real`: Initial velocity value
-
-# Throws
-
-- Error if no point set called `set` exists
-- Error if dimension is not correctly specified
-
-# Example
-
-```julia-repl
-julia> velocity_ic!(b, :set_b, :y, 20)
-
-julia> b.single_dim_ics
-1-element Vector{Peridynamics.SingleDimIC}:
- Peridynamics.SingleDimIC(20.0, :velocity, :set_b, 0x02)
-```
-"""
-function velocity_ic!(b::AbstractBody, name::Symbol, d::Union{Integer,Symbol}, value::Real)
-    check_if_set_is_defined(b.point_sets, name)
-    dim = get_dim(d)
-    sdic = SingleDimIC(convert(Float64, value), :velocity, name, dim)
-    _condition!(b.single_dim_ics, sdic)
-    return nothing
-end

### 2024-05-16 src/core/halo_exchange.jl

@@ -1,91 +1,0 @@
-struct HaloExchange
-    tag::Int
-    src_chunk_id::Int
-    dest_chunk_id::Int
-    src_idxs::Vector{Int}
-    dest_idxs::Vector{Int}
-end
-
-function exchange!(dest::Matrix{T}, src::Matrix{T}, dest_idxs::Vector{Int},
-                   src_idxs::Vector{Int}) where {T}
-    for i in eachindex(dest_idxs)
-        for d in axes(dest, 1)
-            @inbounds dest[d, dest_idxs[i]] = src[d, src_idxs[i]]
-        end
-    end
-    return nothing
-end
-
-function exchange_from_buf!(dest::T, buf::T, dest_idxs::Vector{Int}) where {T<:Matrix}
-    for i in eachindex(dest_idxs)
-        for d in axes(dest, 1)
-            dest[d, dest_idxs[i]] = buf[d, i]
-        end
-    end
-    return nothing
-end
-
-function exchange_to_buf!(buf::T, src::T, src_idxs::Vector{Int}) where {T<:Matrix}
-    for i in eachindex(src_idxs)
-        for d in axes(buf, 1)
-            buf[d, i] = src[d, src_idxs[i]]
-        end
-    end
-    return nothing
-end
-
-function exchange!(dest::Vector{T}, src::Vector{T}, dest_idxs::Vector{Int},
-                   src_idxs::Vector{Int}) where {T}
-    for i in eachindex(dest_idxs)
-        @inbounds dest[dest_idxs[i]] = src[src_idxs[i]]
-    end
-    return nothing
-end
-
-function exchange_from_buf!(dest::T, buf::T, dest_idxs::Vector{Int}) where {T<:Vector}
-    for i in eachindex(dest_idxs)
-        dest[dest_idxs[i]] = buf[i]
-    end
-    return nothing
-end
-
-function exchange_to_buf!(buf::T, src::T, src_idxs::Vector{Int}) where {T<:Vector}
-    for i in eachindex(src_idxs)
-        buf[i] = src[src_idxs[i]]
-    end
-    return nothing
-end
-
-function exchange_add!(dest::Matrix{T}, src::Matrix{T}, dest_idxs::Vector{Int},
-                       src_idxs::Vector{Int}) where {T<:Number}
-    for i in eachindex(dest_idxs)
-        for d in axes(dest, 1)
-            @inbounds dest[d, dest_idxs[i]] += src[d, src_idxs[i]]
[…]

### 2024-05-16 src/core/job.jl

@@ -1,138 +1,0 @@
-const JOB_KWARGS = (:path, :freq, :fields)
-
-"""
-    Job(spatial_setup, time_solver; kwargs...)
-
-Job that contains all the information required for a peridynamic simulation
-
-# Arguments
-
-- `spatial_setup::AbstractSpatialSetup`: Body or Multibody setup for the simulation
-- `time_solver::AbstractTimeSolver`: Method for calculating discrete time steps
-
-# Keywords
-
-- `path::String`: Storage path for results
-- `freq::Int`: Frequency of time steps that are exported
-- `fields::NTuple{N,Symbol}`: Exported fields
-             Possible export fields depend on the selected material model.
-             See material type documentation.
-             Default export fields: `(:displacement, :damage)`
-
-# Throws
-
-- Error if keyword is not allowed
-
-# Example
-
-```julia-repl
-julia> b = Body(BBMaterial(), pos, vol)
-
-julia> vv = VelocityVerlet(steps=2000)
-
-julia> job = Job(b, vv;
-           path=joinpath(@__DIR__, "results", "mode_I"),
-           fields=(:displacement, :velocity, :acceleration, :damage))
-Job{Body{BBMaterial, Peridynamics.BBPointParameters}, VelocityVerlet}(Body{BBMaterial,
-Peridynamics.BBPointParameters}(BBMaterial(), 12500, [-0.49 -0.47 …
-```
-
-Note that for the keyword `fields` a NTuple is expected! If you want to export only one
-field, insert `,` after the field:
-```julia-repl
-julia> job = Job(b, vv;
-           path=joinpath(@__DIR__, "results", "mode_I"),
-           fields=(:displacement,))
-```
-
----
-
-!!! warning "Internal use only"
-    Please note that the fields are intended for internal use only. They are *not* part of
-    the public API of Peridynamics.jl, and thus can be altered (or removed) at any time
-    without it being considered a breaking change.
-
-```julia
-Job{SpatialSetup,TimeSolver,Options}
-```
-
-# Type Parameters
-
-- `SpatialSetup <: AbstractSpatialSetup`: Type of the spatial setup
-- `TimeSolver <: AbstractTimeSolver`: Type of the time solver
-- `Options <: AbstractOptions`: Type of the export options
-
-# Fields
-
-- `spatial_setup::AbstractSpatialSetup`: Body or Multibody setup for the simulation
[…]

### 2024-05-16 src/core/materials.jl

@@ -1,62 +1,0 @@
-function point_param_type(mat::AbstractMaterial)
-    throw(MethodError(point_param_type, mat))
-end
-
-function get_point_params(mat::AbstractMaterial, ::Dict{Symbol,Any})
-    throw(MethodError(get_point_params, mat))
-end
-
-macro params(material, params)
-    macrocheck_input_material(material)
-    macrocheck_input_params(params)
-    local _checks = quote
-        Peridynamics.typecheck_material($(esc(material)))
-        #TODO: make this check material dependent -> overloadable for own types!
-        Peridynamics.typecheck_params($(esc(params)))
-    end
-    local _pointparam_type = quote
-        Peridynamics.point_param_type(::$(esc(material))) = $(esc(params))
-    end
-    local _get_pointparams = quote
-        function Peridynamics.get_point_params(m::$(esc(material)), p::Dict{Symbol,Any})
-            return $(esc(params))(m, p)
-        end
-    end
-    return Expr(:block, _checks, _pointparam_type, _get_pointparams)
-end
-
-function macrocheck_input_material(material)
-    material isa Symbol && return nothing
-    (material isa Expr && material.head === :.) && return nothing
-    return throw(ArgumentError("argument `$material` is not a valid material input!\n"))
-end
-
-function macrocheck_input_params(params)
-    params isa Symbol && return nothing
-    (params isa Expr && params.head === :.) && return nothing
-    msg = "argument `$params` is not a valid point parameter input!\n"
-    return throw(ArgumentError(msg))
-end
-
-function typecheck_material(::Type{Material}) where {Material}
-    if !(Material <: AbstractMaterial)
-        msg = "$Material is not a valid material type!\n"
-        throw(ArgumentError(msg))
-    end
-    return nothing
-end
-
-function typecheck_params(::Type{Param}) where {Param}
-    if !(Param <: AbstractPointParameters)
-        msg = "$Param is not a valid point parameter type!\n"
-        throw(ArgumentError(msg))
-    end
-    parameters = fieldnames(Param)
-    for req_param in required_point_parameters()
-        if !in(req_param, parameters)
-            msg = "required parameter $req_param not found in $(Param)!\n"
-            error(msg)
-        end
-    end
-    return nothing
-end

### 2024-05-16 src/core/mpi_data_handler.jl

@@ -1,371 +1,0 @@
-struct MPIHaloInfo
-    point_ids::Dict{Int,Vector{Int}}
-    halos_points::Dict{Int,Vector{Int}}
-    localizers::Dict{Int,Dict{Int,Int}}
-    hidxs_by_src::Dict{Int,Dict{Int,Vector{Int}}}
-end
-
-struct MPIDataHandler{Sys,M,P,S,Bufs} <: AbstractMPIDataHandler{Sys,M,P,S}
-    chunk::BodyChunk{Sys,M,P,S}
-    n_halo_fields::Int
-    lth_exs_send::Vector{HaloExchange}
-    lth_exs_recv::Vector{HaloExchange}
-    htl_exs_send::Vector{HaloExchange}
-    htl_exs_recv::Vector{HaloExchange}
-    lth_send_bufs::Vector{Bufs}
-    lth_recv_bufs::Vector{Bufs}
-    htl_send_bufs::Vector{Bufs}
-    htl_recv_bufs::Vector{Bufs}
-    field_to_buf::Dict{Symbol,Int}
-    lth_reqs::Vector{Vector{MPI.Request}}
-    htl_reqs::Vector{Vector{MPI.Request}}
-end
-
-function MPIDataHandler(body::AbstractBody, solver::AbstractTimeSolver,
-                        point_decomp::PointDecomposition)
-    param_spec = get_param_spec(body)
-    @timeit_debug TO "chop chunk" begin
-        chunk = chop_body_mpi(body, solver, point_decomp, param_spec)
-    end
-    @timeit_debug TO "find halo exchanges" begin
-        halo_infos = get_halo_infos(chunk, point_decomp, body.n_points)
-        lth_exs, htl_exs = find_halo_exchanges(halo_infos)
-        lth_send, lth_recv = filter_send_recv(lth_exs)
-        htl_send, htl_recv = filter_send_recv(htl_exs)
-        bufs = find_bufs(chunk.storage, lth_send, lth_recv, htl_send, htl_recv)
-        n_halo_fields = get_n_halo_fields(chunk.storage)
-        lth_reqs = init_reqs(lth_send, n_halo_fields)
-        htl_reqs = init_reqs(htl_send, n_halo_fields)
-    end
-    mdh = MPIDataHandler(chunk, n_halo_fields, lth_send, lth_recv, htl_send, htl_recv,
-                         bufs..., lth_reqs, htl_reqs)
-    return mdh
-end
-
-function MPIDataHandler(multibody::AbstractMultibodySetup,
[…]

### 2024-05-16 src/core/parameter_handler.jl

@@ -1,42 +1,0 @@
-struct SingleParamChunk <: AbstractParamSpec end
-
-struct MultiParamChunk <: AbstractParamSpec end
-
-struct ParameterHandler{P<:AbstractPointParameters} <: AbstractParameterHandler
-    parameters::Vector{P}
-    point_mapping::Vector{Int}
-end
-
-function ParameterHandler(body::AbstractBody, ch::AbstractChunkHandler)
-    parameters = body.point_params
-    point_mapping = body.params_map[ch.loc_points]
-    return ParameterHandler(parameters, point_mapping)
-end
-
-function get_paramsetup(body::AbstractBody, ::AbstractChunkHandler, ::SingleParamChunk)
-    return first(body.point_params)
-end
-
-function get_paramsetup(body::AbstractBody, ch::AbstractChunkHandler, ::MultiParamChunk)
-    return ParameterHandler(body, ch)
-end
-
-@inline function get_params(paramhandler::ParameterHandler, point_id::Int)
-    return paramhandler.parameters[paramhandler.point_mapping[point_id]]
-end
-
-@inline function get_params(params::AbstractPointParameters, ::Int)
-    return params
-end
-
-@inline function parameter_setup_type(::Body{M,P}, ::SingleParamChunk) where {M,P}
-    return P
-end
-
-@inline function parameter_setup_type(::Body{M,P}, ::MultiParamChunk) where {M,P}
-    return ParameterHandler{P}
-end
-
-@inline function get_param_spec(body::AbstractBody)
-    return length(body.point_params) == 1 ? SingleParamChunk() : MultiParamChunk()
-end

### 2024-05-16 src/core/storages.jl

@@ -1,207 +1,0 @@
-function storage_type(mat::AbstractMaterial, ts::AbstractTimeSolver)
-    throw(MethodError(storage_type, mat, ts))
-end
-
-function get_storage(::M, ts::T, system, ch) where {M,T}
-    msg = "storage for material $M and time solver $T not specified!\n"
-    return error(msg)
-end
-
-macro storage(material, timesolver, storage)
-    macrocheck_input_material(material)
-    macrocheck_input_timesolver(timesolver)
-    macrocheck_input_storage(storage)
-    local _checks = quote
-        Peridynamics.typecheck_material($(esc(material)))
-        Peridynamics.typecheck_storage($(esc(storage)), $(esc(timesolver)))
-    end
-    local _storage_type = quote
-        function Peridynamics.storage_type(::$(esc(material)), ::$(esc(timesolver)))
-            return $(esc(storage))
-        end
-    end
-    local _get_storage = quote
-        function Peridynamics.get_storage(mat::$(esc(material)), ts::$(esc(timesolver)),
-                                           system, ch)
-            return $(esc(storage))(mat, ts, system, ch)
-        end
-    end
-    return Expr(:block, _checks, _storage_type, _get_storage)
-end
-
-loc_to_halo_fields(::AbstractStorage) = ()
-halo_to_loc_fields(::AbstractStorage) = ()
-is_halo_field(::AbstractStorage, ::Val{F}) where {F} = false
-
-macro loc_to_halo_fields(storage, fields...)
-    macrocheck_input_storage(storage)
-    macrocheck_input_fields(fields...)
-    local _checks = quote
-        Peridynamics.typecheck_is_storage($(esc(storage)))
-        Peridynamics.typecheck_storage_fields($(esc(storage)), $(Expr(:tuple, fields...)))
-    end
-    local _loc_to_halo_fields = quote
-        function Peridynamics.loc_to_halo_fields(::$(esc(storage)))
-            return $(Expr(:tuple, fields...))
-        end
-    end
-    local _is_halo_fields = [
-        quote
-            function Peridynamics.is_halo_field(::$(esc(storage)), ::Val{$(esc(_field))})
-                return true
-            end
-        end
-        for _field in fields
-    ]
-    return Expr(:block, _checks, _loc_to_halo_fields, _is_halo_fields...)
-end
-
-macro halo_to_loc_fields(storage, fields...)
[…]

### 2024-05-16 src/core/submit.jl

@@ -1,83 +1,0 @@
-const SUBMIT_KWARGS = (:quiet,)
-
-"""
-    submit(job::Job; kwargs...)
-
-Submits the job to start calculations
-
-# Arguments
-
-- `job::Job`: Job that contains all defined parameters and conditions
-
-# Keywords
-
-- `quiet::Bool`: If `:quiet=true`, no outputs are printed in the terminal.
-
-# Throws
-
-- Error if keyword is not allowed
-
-# Example
-
-```julia-repl
-julia> job = Job(b, vv;
-           path=joinpath(@__DIR__, "results", "mode_I"),
-           fields=(:displacement, :damage));
-
-julia> submit(job);
-solve... 100%|████████████████████| Time: 0:00:11
-```
-"""
-function submit(job::Job; kwargs...)
-    o = Dict{Symbol,Any}(kwargs)
-    check_kwargs(o, SUBMIT_KWARGS)
-    quiet = get_submit_options(o)
-    set_quiet!(quiet)
-
-    if mpi_run()
-        ret = submit_mpi(job)
-    else
-        ret = submit_threads(job, nthreads())
-    end
-
-    return ret
-end
-
-function get_submit_options(o::Dict{Symbol,Any})
-    local quiet::Bool
-    if haskey(o, :quiet)
-        quiet = Bool(o[:quiet])
-    else
-        quiet = false
-    end
-    return quiet
-end
-
-function submit_mpi(job::Job)
-    timeit_debug_enabled() && reset_timer!(TO)
-    @timeit_debug TO "initialization" begin
-        init_logs(job.options)
-        point_decomp = PointDecomposition(job.spatial_setup, mpi_nranks())
-        mdh = MPIDataHandler(job.spatial_setup, job.time_solver, point_decomp)
-        init_time_solver!(job.time_solver, mdh)
-        initialize!(mdh, job.time_solver)
-    end
-    @timeit_debug TO "solve!" begin
-        solve!(mdh, job.time_solver, job.options)
-    end
-    if timeit_debug_enabled()
-        TimerOutputs.complement!(TO)
-        log_mpi_timers(job.options)
-    end
-    return mdh
-end
-
-function submit_threads(job::Job, n_chunks::Int)
-    init_logs(job.options)
-    point_decomp = PointDecomposition(job.spatial_setup, n_chunks)
-    tdh = ThreadsDataHandler(job.spatial_setup, job.time_solver, point_decomp)
[…]

### 2024-05-16 src/core/systems.jl

@@ -1,51 +1,0 @@
-function system_type(mat::AbstractMaterial)
-    throw(MethodError(system_type, mat))
-end
-
-# function get_system_type(mat::AbstractMaterial)
-#     Sys = system_type(mat)
-#     FullSys = full_system_type(Sys, mat)
-#     return FullSys
-# end
-
-# function full_system_type(::Type{System}, mat::AbstractMaterial) where {System}
-#     return system_type(mat)
-# end
-
-function get_system(::AbstractBody{M}, ::PointDecomposition, ::Int) where {M}
-    msg = "system for material $M not specified!\n"
-    return error(msg)
-end
-
-# macro system(material, system)
-#     macrocheck_input_material(material)
-#     macrocheck_input_system(system)
-#     local _checks = quote
-#         Peridynamics.typecheck_material($(esc(material)))
-#         Peridynamics.typecheck_system($(esc(system)))
-#     end
-#     local _system_type = quote
-#         Peridynamics.system_type(::$(esc(material))) = $(esc(system))
-#     end
-#     local _get_system = quote
-#         function Peridynamics.get_system(body::Peridynamics.AbstractBody{$(esc(material))},
-#                                          args...)
-#             return $(esc(system))(body, args...)
-#         end
-#     end
-#     return Expr(:block, _checks, _system_type, _get_system)
-# end
-
-# function macrocheck_input_system(system)
-#     system isa Symbol && return nothing
-#     (system isa Expr && system.head === :.) && return nothing
-#     return throw(ArgumentError("argument `$system` is not a valid system input!\n"))
-# end
-
-# function typecheck_system(::Type{System}) where {System}
-#     if !(System <: AbstractSystem)
-#         msg = "$System is not a valid system type!\n"
-#         throw(ArgumentError(msg))
-#     end
-#     return nothing
-# end

### 2024-05-16 src/core/threads_data_handler.jl

@@ -1,190 +1,0 @@
-struct ThreadsDataHandler{Sys,M,P,S} <: AbstractThreadsDataHandler{Sys,M,P,S}
-    n_chunks::Int
-    chunks::Vector{BodyChunk{Sys,M,P,S}}
-    lth_exs::Vector{Vector{HaloExchange}}
-    htl_exs::Vector{Vector{HaloExchange}}
-end
-
-function ThreadsDataHandler(body::AbstractBody, solver::AbstractTimeSolver,
-                            point_decomp::PointDecomposition)
-    param_spec = get_param_spec(body)
-    chunks = chop_body_threads(body, solver, point_decomp, param_spec)
-    n_chunks = length(chunks)
-    lth_exs, htl_exs = find_halo_exchanges(chunks)
-    return ThreadsDataHandler(n_chunks, chunks, lth_exs, htl_exs)
-end
-
-function ThreadsDataHandler(multibody::AbstractMultibodySetup, solver::AbstractTimeSolver,
-                            point_decomp::PointDecomposition)
-    error("MultibodySetup not yet implemented!\n")
-end
-
-function chop_body_threads(body::AbstractBody, solver::AbstractTimeSolver,
-                           point_decomp::PointDecomposition, param_spec::AbstractParamSpec)
-    ChunkType = body_chunk_type(body, solver, param_spec)
-    chunks = _chop_body_threads(ChunkType, body, solver, point_decomp, param_spec)
-    return chunks
-end
-
-function _chop_body_threads(::Type{ChunkType}, body::AbstractBody,
-                            solver::AbstractTimeSolver, point_decomp::PointDecomposition,
-                            param_spec::AbstractParamSpec) where {ChunkType}
-    chunks = Vector{ChunkType}(undef, point_decomp.n_chunks)
-    @threads :static for chunk_id in eachindex(point_decomp.decomp)
-        chunk = BodyChunk(body, solver, point_decomp, chunk_id, param_spec)
-        apply_precracks!(chunk, body)
-        apply_initial_conditions!(chunk, body)
-        initialize!(chunk)
-        chunks[chunk_id] = chunk
-    end
-    return chunks
-end
-
-function find_halo_exchanges(chunks::Vector{B}) where {B<:AbstractBodyChunk}
-    lth_exs = Vector{Vector{HaloExchange}}(undef, length(chunks))
[…]

### 2024-05-16 src/core/time_solvers.jl

@@ -1,37 +1,0 @@
-function init_time_solver!(ts::AbstractTimeSolver, dh::AbstractDataHandler)
-    throw(MethodError(init_time_solver!, ts, dh))
-end
-
-function solve!(dh::AbstractDataHandler, ts::AbstractTimeSolver, options)
-    msg = "interface function `solve!` not correctly implemented!\n"
-    msg *= "No method for arg types:\n"
-    msg *= "   dh::$(typeof(dh))\n"
-    msg *= "   ts::$(typeof(ts))\n"
-    error(msg)
-end
-
-function required_fields_timesolver(::Type{TS}) where {TS}
-    return (req_point_data_fields_timesolver(TS)..., req_data_fields_timesolver(TS)...)
-end
-
-function req_point_data_fields_timesolver(ts::Type{TS}) where {TS}
-    throw(MethodError(required_fields_timesolver, ts))
-    return nothing
-end
-
-function req_data_fields_timesolver(ts::Type{TS}) where {TS}
-    throw(MethodError(required_fields_timesolver, ts))
-    return nothing
-end
-
-function req_storage_fields_timesolver(::Type{S}, ::Type{TS}) where {S,TS}
-    parameters = fieldnames(S)
-    for req_field in required_fields_timesolver(TS)
-        if !in(req_field, parameters)
-            msg = "required field $req_field not found in $(S)!\n"
-            msg *= "The field is required for the `$(TS)` time solver!\n"
-            error(msg)
-        end
-    end
-    return nothing
-end

### 2024-05-16 src/discretization/body.jl

@@ -1,132 +1,0 @@
-"""
-    Body(material, position, volume)
-
-Creates a body for use in peridynamic calculation
-
-# Arguments
-
-- `material::AbstractMaterial`: Specifies which material model is used
-- `position::AbstractMatrix`: 3×n matrix with position of each point
-- `volume::AbstractVector`: Vector with volume of each point
-
-# Throws
-
-- Error if n_points = 0
-- `DimensionMismatch`: Error if dimension of position != 3
-
-# Example
-
-```julia-repl
-julia> l, Δx, = 1.0, 1/50;
-
-julia> pos, vol = uniform_box(l, l, 0.1l, Δx);
-
-julia> b = Body(BBMaterial(), pos, vol);
-
-julia> b
-Body{BBMaterial, Peridynamics.BBPointParameters}(BBMaterial(), 12500,
-[-0.49 -0.47 … 0.47 0.49; -0.49 -0.49 … 0.49 0.49; -0.04 -0.04 … 0.04 0.04],
-[8.000000000000001e-6, 8.000000000000001e-6,  …  8.000000000000001e-6],
-Bool[1, 1, 1, 1, 1, 1, 1, 1, 1, 1  …  1, 1, 1, 1, 1, 1, 1, 1, 1, 1],
-Dict{Symbol, Vector{Int64}}(), Peridynamics.BBPointParameters[],
-[0, 0, 0, 0, 0, 0, 0, 0, 0, 0  …  0, 0, 0, 0, 0, 0, 0, 0, 0, 0],
-Peridynamics.SingleDimBC[], Peridynamics.SingleDimIC[], Peridynamics.PointSetsPreCrack[])
-```
-
----
-
-!!! warning "Internal use only"
-    Please note that the fields are intended for internal use only. They are *not* part of
-    the public API of Peridynamics.jl, and thus can be altered (or removed) at any time
-    without it being considered a breaking change.
-
-```julia
-Body{Material,PointParameters}
-```
-
-# Type Parameters
-
-- `Material <: AbstractMaterial`: Type of the specified material model
-- `PointParameters <: AbstractPointParameters`: Type of the point parameters
-
-# Fields
-
-- `mat::Material`: Specified material model
-- `n_points::Int`: Number of material points that represent the body
-- `position::Matrix{Float64}`: 3×n_points matrix with position for each point
-- `volume::Vector{Float64}`: Vector with volume for each point
-- `fail_permit::Vector{Bool}`: Vector that describes if failure is allowed for each point
[…]

### 2024-05-16 src/discretization/body_chunk.jl

@@ -1,45 +1,0 @@
-struct BodyChunk{System<:AbstractSystem,
-                 Material<:AbstractMaterial,
-                 Params<:AbstractParameterSetup,
-                 Storage<:AbstractStorage} <: AbstractBodyChunk{System,Material}
-    system::System
-    mat::Material
-    paramsetup::Params
-    storage::Storage
-    ch::ChunkHandler
-    psets::Dict{Symbol,Vector{Int}}
-    sdbcs::Vector{SingleDimBC}
-    pdsdbcs::Vector{PosDepSingleDimBC}
-    cells::Vector{MeshCell{VTKCellType,Tuple{Int64}}}
-end
-
-function BodyChunk(body::AbstractBody, solver::AbstractTimeSolver, pd::PointDecomposition,
-                   chunk_id::Int, param_spec::AbstractParamSpec)
-    mat = body.mat
-    system, ch = get_system(body, pd, chunk_id)
-    paramsetup = get_paramsetup(body, ch, param_spec)
-    storage = get_storage(mat, solver, system, ch)
-    psets = localized_point_sets(body.point_sets, ch)
-    sdbcs = body.single_dim_bcs
-    pdsdbcs = body.posdep_single_dim_bcs
-    cells = get_cells(ch.n_loc_points)
-    return BodyChunk(system, mat, paramsetup, storage, ch, psets, sdbcs, pdsdbcs, cells)
-end
-
-@inline function get_params(b::BodyChunk, point_id::Int)
-    return get_params(b.paramsetup, point_id)
-end
-
-@inline function body_chunk_type(body::AbstractBody{Material}, solver::AbstractTimeSolver,
-                                 param_spec::AbstractParamSpec) where {Material}
-    System = system_type(body.mat)
-    Params = parameter_setup_type(body, param_spec)
-    Storage = storage_type(body, solver)
-    return BodyChunk{System,Material,Params,Storage}
-end
-
-@inline each_point_idx(b::AbstractBodyChunk) = each_point_idx(b.ch)
-
-function initialize!(::BodyChunk)
-    return nothing
-end

### 2024-05-16 src/discretization/bond_system.jl

@@ -1,174 +1,0 @@
-struct Bond
-    neighbor::Int
-    length::Float64
-    fail_permit::Bool
-end
-
-struct BondSystem{Correction<:AbstractCorrection} <: AbstractSystem
-    position::Matrix{Float64}
-    volume::Vector{Float64}
-    bonds::Vector{Bond}
-    n_neighbors::Vector{Int}
-    bond_ids::Vector{UnitRange{Int}}
-    correction::Correction
-end
-
-function BondSystem(body::AbstractBody, pd::PointDecomposition, chunk_id::Int)
-    check_bond_system_compat(body.mat)
-    bonds, n_neighbors = find_bonds(body, pd.decomp[chunk_id])
-    bond_ids = find_bond_ids(n_neighbors)
-    ch = get_chunk_handler(bonds, pd, chunk_id)
-    localize!(bonds, ch.localizer)
-    position, volume = get_pos_and_vol_chunk(body, ch.point_ids)
-    correction = get_correction(body.mat, ch.n_loc_points, length(ch.point_ids),
-                                 length(bonds))
-    bs = BondSystem(position, volume, bonds, n_neighbors, bond_ids, correction)
-    return bs, ch
-end
-
-function get_system(body::AbstractBody{Material}, pd::PointDecomposition,
-                    chunk_id::Int) where {Material<:AbstractBondSystemMaterial}
-    return BondSystem(body, pd, chunk_id)
-end
-
-@inline function system_type(mat::AbstractBondSystemMaterial)
-    return BondSystem{correction_type(mat)}
-end
-
-function check_bond_system_compat(::M) where {M<:AbstractMaterial}
-    msg = "body with material $(M) incompatible to BondSystem!\n"
-    msg *= "The material has to be a subtype of `AbstractBondSystemMaterial`!\n"
-    return throw(ArgumentError(msg))
-end
-
-function check_bond_system_compat(::AbstractBondSystemMaterial)
-    return nothing
-end
-
-function find_bonds(body::AbstractBody, loc_points::UnitRange{Int})
-    balltree = BallTree(body.position)
-    bonds = Vector{Bond}()
-    sizehint!(bonds, body.n_points * 300)
-    n_neighbors = zeros(Int, length(loc_points))
-    for (li, i) in enumerate(loc_points)
-        n_neighbors[li] = find_bonds!(bonds, balltree, body.position, body.fail_permit,
-                                      get_point_param(body, :δ, i), i)
-    end
[…]

### 2024-05-16 src/discretization/bond_system_corrections.jl

@@ -1,157 +1,0 @@
-
-"""
-    NoCorrection <: AbstractCorrection
-
-A correction handler for `AbstractBondSystemMaterial`s that does nothing. No correction
-methods will apply and if someone tries to calculate a correction factor, they will be 1.
-"""
-struct NoCorrection <: AbstractCorrection end
-
-function correction_type(::AbstractBondSystemMaterial{Correction}) where {Correction}
-    return Correction
-end
-
-function get_correction(::AbstractBondSystemMaterial{NoCorrection}, ::Int, ::Int, ::Int)
-    return NoCorrection()
-end
-
-@inline function surface_correction_factor(::NoCorrection, ::Int)
-    return 1
-end
-
-
-#===========================================================================================
-    ENERGY BASED SURFACE CORRECTION
-===========================================================================================#
-
-"""
-    EnergySurfaceCorrection <: AbstractCorrection
-
-A correction handler for `AbstractBondSystemMaterial`s that uses the strain energy density
-to calculate surface correction factors.
-"""
-struct EnergySurfaceCorrection <: AbstractCorrection
-    mfactor::Matrix{Float64} # multiplication factor mfactor[ndims, npoints]
-    scfactor::Vector{Float64} # surface correction factor scfactor[nbonds]
-end
-
-function get_correction(::AbstractBondSystemMaterial{EnergySurfaceCorrection},
-                        n_loc_points::Int, n_points::Int, n_bonds::Int)
-    mfactor = zeros(3, n_points)
-    scfactor = ones(n_bonds)
-    return EnergySurfaceCorrection(mfactor, scfactor)
-end
-
-@inline function surface_correction_factor(correction::EnergySurfaceCorrection,
-                                           bond_id::Int)
-    return correction.scfactor[bond_id]
-end
-
-function initialize!(dh::AbstractThreadsDataHandler{BondSystem{EnergySurfaceCorrection}},
-                     ::AbstractTimeSolver)
-    @threads :static for chunk in dh.chunks
-        calc_mfactor!(chunk)
-    end
-    @threads :static for chunk_id in eachindex(dh.chunks)
-        exchange_loc_to_halo!(get_mfactor, dh, chunk_id)
-        calc_scfactor!(dh.chunks[chunk_id])
-    end
-    return nothing
-end
-
[…]

### 2024-05-16 src/discretization/chunk_handler.jl

@@ -1,86 +1,0 @@
-struct ChunkHandler <: AbstractChunkHandler
-    n_loc_points::Int
-    point_ids::Vector{Int}
-    loc_points::UnitRange{Int}
-    halo_points::Vector{Int}
-    hidxs_by_src::Dict{Int,UnitRange{Int}}
-    localizer::Dict{Int,Int}
-end
-
-function sort_halo_by_src!(halo_points::Vector{Int}, point_src::Dict{Int,Int},
-                           n_loc_points::Int)
-    halo_sources = [point_src[i] for i in halo_points]
-    idx_sorted = sortperm(halo_sources)
-    halo_sources .= halo_sources[idx_sorted]
-    halo_points .= halo_points[idx_sorted]
-    hidxs_by_src = get_hidxs_by_src(halo_sources, n_loc_points)
-    return hidxs_by_src
-end
-
-function get_hidxs_by_src(halo_sources::Vector{Int}, n_loc_points::Int)
-    @assert sort(halo_sources) == halo_sources
-    hidxs_by_src = Dict{Int,UnitRange{Int}}()
-    unique_sources = unique(halo_sources)
-
-    for source in unique_sources
-        idxs = findall(x -> x == source, halo_sources)
-        idx_begin = first(idxs) + n_loc_points
-        idx_end = last(idxs) + n_loc_points
-        hidxs_by_src[source] = idx_begin:idx_end
-    end
-
-    return hidxs_by_src
-end
-
-function find_localizer(point_ids::Vector{Int})
-    localizer = Dict{Int,Int}()
-    for (li, i) in enumerate(point_ids)
-        localizer[i] = li
-    end
-    return localizer
-end
-
-function localize!(point_ids::Vector{Int}, localizer::Dict{Int,Int})
-    for i in eachindex(point_ids)
-        point_ids[i] = localizer[point_ids[i]]
-    end
-    return nothing
-end
-
-function localize(point_ids::Vector{Int}, ch::ChunkHandler)
-    is_loc_point = zeros(Bool, length(point_ids))
-    for i in eachindex(point_ids)
-        glob_index = point_ids[i]
-        if in(glob_index, ch.loc_points)
-            is_loc_point[i] = true
-        end
-    end
-    loc_point_ids = point_ids[is_loc_point]
-    localize!(loc_point_ids, ch.localizer)
-    return loc_point_ids
-end
-
[…]

### 2024-05-16 src/discretization/decomposition.jl

@@ -1,54 +1,0 @@
-struct PointDecomposition
-    n_chunks::Int
-    decomp::Vector{UnitRange{Int}}
-    point_src::Dict{Int,Int}
-
-    function PointDecomposition(decomp::Vector{UnitRange{Int}})
-        n_chunks = length(decomp)
-        point_src = Dict{Int,Int}()
-        for chunk_id in eachindex(decomp)
-            for point_id in decomp[chunk_id]
-                point_src[point_id] = chunk_id
-            end
-        end
-        return new(n_chunks, decomp, point_src)
-    end
-end
-
-function distribute_equally(n_elems::Int, n_chunks::Int)
-    if n_elems >= n_chunks
-        chunk_size = div(n_elems, n_chunks)
-        remainder = rem(n_elems, n_chunks)
-        sidx = zeros(Int64, n_chunks + 1)
-        for i in 1:(n_chunks + 1)
-            sidx[i] += (i - 1) * chunk_size + 1
-            if i <= remainder
-                sidx[i] += i - 1
-            else
-                sidx[i] += remainder
-            end
-        end
-        decomp = fill(0:0, n_chunks)
-        for i in 1:n_chunks
-            decomp[i] = sidx[i]:(sidx[i + 1] - 1)
-        end
-        return decomp
-    else
-        sidx = [1:(n_elems + 1);]
-        decomp = fill(0:-1, n_chunks)
-        for i in 1:n_elems
-            decomp[i] = sidx[i]:(sidx[i + 1] - 1)
-        end
-        return decomp
-    end
-end
-
-function PointDecomposition(b::AbstractBody, n_chunks::Int)
-    decomp = distribute_equally(b.n_points, n_chunks)
-    return PointDecomposition(decomp)
-end
-
-function PointDecomposition(::AbstractMultibodySetup, ::Int)
-    error("spatial decomposition for MultibodySetup not yet implemented!\n")
-    return nothing
-end

### 2024-05-16 src/discretization/multibody_setup.jl

@@ -1,116 +1,0 @@
-"""
-    MultibodySetup(bodies)
-
-Setup for a peridynamic simulation with multiple bodies
-
-# Arguments
-
-- `bodies::Dict{Symbol,Body{M,P}}`:
-
-# Throws
-
-- Error if less than 2 bodies are defined
-- Error if defined bodies have different material types
-
-# Example
-
----
-
-!!! warning "Internal use only"
-    Please note that the fields are intended for internal use only. They are *not* part of
-    the public API of Peridynamics.jl, and thus can be altered (or removed) at any time
-    without it being considered a breaking change.
-
-```julia
-MultibodySetup{Material,PointParameters}
-```
-
-# Type Parameters
-
-- `Material <: AbstractMaterial`: Type of the specified material model
-- `PointParameters <: AbstractPointParameters`: Type of the point parameters
-
-# Fields
-
-- `bodies::Dict{Symbol,Body{M,P}}`:
-- `contacts::Vector{Contact}`:
-
-TODO
-"""
-mutable struct MultibodySetup{M<:AbstractMaterial,
-                              P<:AbstractPointParameters} <: AbstractMultibodySetup{M}
-    bodies::Dict{Symbol,Body{M,P}}
-    contacts::Vector{Contact}
-
-    function MultibodySetup(bodies::Dict{Symbol,Body{M,P}}) where {M,P}
-        if length(bodies) < 2
-            msg = "not enough bodies given!\n"
-            msg *= "Please specify 2 or more!\n"
-            throw(ArgumentError(msg))
-        end
-        contacts = Vector{Contact}()
-        return new{M,P}(bodies, contacts)
-    end
-end
-
-function MultibodySetup(::Dict{Symbol,Body})
-    msg = "bodies have different material types!\n"
-    msg *= "Only bodies with the same material types can be used for MultibodySetup!\n"
-    throw(ArgumentError(msg))
-    return nothing
-end
-
-MultibodySetup(body_pairs...) = MultibodySetup(Dict(body_pairs...))
-
-@inline material_type(::MultibodySetup{M}) where {M} = M
-
-function check_if_bodyname_is_defined(ms::AbstractMultibodySetup, name::Symbol)
-    if !haskey(ms.bodies, name)
-        throw(ArgumentError("there is no body with name $(name)!"))
-    end
-    return nothing
-end
-
-"""
[…]

### 2024-05-16 src/discretization/point_generators.jl

@@ -1,64 +1,0 @@
-"""
-    uniform_box(lx, ly, lz, Δx; center_x=0, center_y=0, center_z=0)
-
-Creates a grid of points in a cuboid form with lengths `lx`, `ly` and `lz` and the distance
-`Δx` between the points.
-
-# Arguments
-
-- `lx::Real`: Length in x-dimension
-- `ly::Real`: Length in y-dimension
-- `lz::Real`: Length in z-dimension
-- `Δx::Real`: Distance between neighboring points
-
-# Keywords
-
-- `center_x::Real=0`: Center of the cuboid in x-dimension
-- `center_y::Real=0`: Center of the cuboid in y-dimension
-- `center_z::Real=0`: Center of the cuboid in z-dimension
-
-# Returns
-
-- `position::Matrix`: 3×n matrix with position of each point
-- `volume::Vector`: Vector with volume of each point
-
-# Example
-
-```julia-repl
-julia> position, volume = uniform_box(10, 10, 10, 2);
-
-julia> position
-3×125 Matrix{Float64}:
- -4.0  -2.0   0.0   2.0   4.0  -4.0  -2.0   0.0  …  0.0  2.0  4.0  -4.0  -2.0  0.0  2.0  4.0
- -4.0  -4.0  -4.0  -4.0  -4.0  -2.0  -2.0  -2.0     2.0  2.0  2.0   4.0   4.0  4.0  4.0  4.0
- -4.0  -4.0  -4.0  -4.0  -4.0  -4.0  -4.0  -4.0     4.0  4.0  4.0   4.0   4.0  4.0  4.0  4.0
-
-julia> volume
-125-element Vector{Int64}:
- 8
- 8
- 8
- 8
- ⋮
- 8
- 8
- 8
- 8
-```
-"""
-function uniform_box(lx::Real, ly::Real, lz::Real, Δx::Real;
-                     center_x::Real=0, center_y::Real=0, center_z::Real=0)
-    _gridx = range((-lx + Δx) / 2, (lx - Δx) / 2; step=Δx)
-    gridx = _gridx .- sum(_gridx) / length(_gridx)
-    _gridy = range((-ly + Δx) / 2, (ly - Δx) / 2; step=Δx)
-    gridy = _gridy .- sum(_gridy) / length(_gridy)
-    _gridz = range((-lz + Δx) / 2, (lz - Δx) / 2; step=Δx)
-    gridz = _gridz .- sum(_gridz) / length(_gridz)
[…]

### 2024-05-16 src/discretization/point_sets.jl

@@ -1,88 +1,0 @@
-const FIND_POINTS_ALLOWED_SYMBOLS = (:x, :y, :z, :p)
-const SYMBOL_TO_DIM = Dict(:x => 0x1, :y => 0x2, :z => 0x3)
-
-"""
-    point_set!(body, set, points)
-    point_set!(fun, body, set)
-
-Creates the point set `set` in `body` containing all points either defined in vector
-`points` or described by function `fun`.
-
-# Arguments
-
-- `body::AbstractBody`: Peridynamic body
-- `set::Symbol`: Point set on `body`
-- `points::AbstractVector`: Vector of point indices
-- `fun::Function`: Function that describes points contained in point set
-
-# Throws
-
-- Error if a point set called `set` is already defined
-- `BoundsError`: If points in `V` do not exist
-
-# Example
-
-```julia-repl
-julia> point_set!(p -> p[1] ≤ -l/2+a && 0 ≤ p[2] ≤ 2δ, b, :set_a)
-
-julia> point_set!(p -> p[1] ≤ -l/2+a && -2δ ≤ p[2] < 0, b, :set_b)
-
-julia> b.point_sets
-Dict{Symbol, Vector{Int64}} with 4 entries:
-  :set_a      => [1251, 1252, 1253, 1254, 1255, 1256, 1257, 1258, 1259, …
-  :set_b      => [951, 952, 953, 954, 955, 956, 957, 958, 959, 960  …  1…
-```
-"""
-function point_set! end
-
-function point_set!(b::AbstractBody, name::Symbol, points::V) where {V<:AbstractVector}
-    checkbounds(b.volume, points)
-    _point_set!(b.point_sets, name, points)
-    return nothing
-end
-
-function point_set!(f::F, b::AbstractBody, name::Symbol) where {F<:Function}
-    points = find_points(f, b.position)
-    point_set!(b, name, points)
-    return nothing
-end
-
-function _point_set!(point_sets::Dict{Symbol,Vector{Int}}, name::Symbol,
-                     points::V) where {V<:AbstractVector{<:Integer}}
-    if haskey(point_sets, name)
-        error("there is already a point set with name $(name)!")
-    end
-    point_sets[name] = points
-    return nothing
-end
-
-function find_points(f::F, position::Matrix{Float64}) where {F<:Function}
-    func_method = get_method_of_function(f)
-    argnames = get_argument_names_of_function(func_method)
-    if isempty(argnames)
-        msg =  "no argument in specified function $(nameof(f))!\n\n"
[…]

### 2024-05-16 src/discretization/predefined_cracks.jl

@@ -1,83 +1,0 @@
-struct PointSetsPreCrack <: AbstractPredefinedCrack
-    set_a::Symbol
-    set_b::Symbol
-    filter_bonds::Bool
-end
-
-@inline filter_bonds(crack::AbstractPredefinedCrack) = crack.filter_bonds
-
-function apply_precracks!(b::AbstractBodyChunk, body::AbstractBody)
-    for precrack in body.point_sets_precracks
-        apply_precrack!(b, body, precrack)
-    end
-    calc_damage!(b)
-    return nothing
-end
-
-function apply_precrack!(b::AbstractBodyChunk, body::AbstractBody,
-                         crack::PointSetsPreCrack)
-    filter_bonds(crack) && return nothing
-    set_a = filter(x -> in(x, b.ch.point_ids), body.point_sets[crack.set_a])
-    set_b = filter(x -> in(x, b.ch.point_ids), body.point_sets[crack.set_b])
-    localize!(set_a, b.ch.localizer)
-    localize!(set_b, b.ch.localizer)
-    if isempty(set_a) || isempty(set_b)
-        return nothing
-    end
-    break_bonds!(b.storage, b.system, b.ch, set_a, set_b)
-    return nothing
-end
-
-"""
-    precrack!(body, set_a, set_b; update_dmg=true)
-
-Creates a crack between two point sets by prohibiting interaction between points of
-different point sets.
-
-# Arguments
-
-- `body::AbstractBody`: Peridynamic body
-- `set_a::Symbol`: First point set on `body`
-- `set_b::Symbol`: Second point set on `body`
-
-# Keywords
-
-- `update_dmg::Bool`: If `update_dmg=true`, the material points involved in the predefined
-                      are initially damaged. If `update_dmg=false`, the bonds involved are
-                      deleted and the material points involved with the predefined crack
-                      are not damaged.
-                      (default=`true`)
-
-# Throws
-
-- Error if point set `set_a` or `set_b` does not exist
-- Error if point sets contain common points
-
-# Example
-
-```julia-repl
-julia> precrack!(b, :set_a, :set_b)
-
-julia> b.point_sets_precracks
-1-element Vector{Peridynamics.PointSetsPreCrack}:
- Peridynamics.PointSetsPreCrack(:set_a, :set_b)
-```
-"""
-function precrack!(b::AbstractBody, set_a::Symbol, set_b::Symbol; update_dmg::Bool=true)
[…]

### 2024-05-16 src/physics/bond_based.jl

@@ -1,128 +1,0 @@
-
-"""
-    BBMaterial <: AbstractMaterial
-
-Material type for bond-based peridynamic simulations
-
-# Allowed material parameters
-
-- `horizon::Float64`: Radius of point interactions
-- `rho::Float64`: Density
-- `E::Float64`: Young's modulus
-- `Gc::Float64`: Critical energy release rate
-- `epsilon_c::Float64`: Critical strain
-
-# Allowed export fields
-
-- `position::Matrix{Float64}`: Position of each point
-- `displacement::Matrix{Float64}`: Displacement of each point
-- `velocity::Matrix{Float64}`: Velocity of each point
-- `velocity_half::Matrix{Float64}`: Velocity parameter for Verlet time solver
-- `acceleration::Matrix{Float64}`: Acceleration of each point
-- `b_int::Matrix{Float64}`: Internal force density of each point
-- `b_ext::Matrix{Float64}`: External force density of each point
-- `damage::Vector{Float64}`: Damage of each point
-- `n_active_bonds::Vector{Int}`: Number of intact bonds for each point
-"""
-struct BBMaterial{Correction} <: AbstractBondSystemMaterial{Correction} end
-
-BBMaterial() = BBMaterial{NoCorrection}()
-
-struct BBPointParameters <: AbstractPointParameters
-    δ::Float64
-    rho::Float64
-    E::Float64
-    nu::Float64
-    G::Float64
-    K::Float64
-    λ::Float64
-    μ::Float64
-    Gc::Float64
-    εc::Float64
-    bc::Float64
-end
-
-function BBPointParameters(::BBMaterial, p::Dict{Symbol,Any})
-    δ = get_horizon(p)
-    rho = get_density(p)
-    if haskey(p, :nu)
-        msg = "keyword `nu` is not allowed for BBMaterial!\n"
-        msg *= "Bond-based peridynamics has a limitation on the possion ratio.\n"
-        msg *= "Therefore, when using BBMaterial, `nu` is hardcoded as 1/4.\n"
-        throw(ArgumentError(msg))
-    else
-        p[:nu] = 0.25
-    end
-    E, nu, G, K, λ, μ = get_elastic_params(p)
-    Gc, εc = get_frac_params(p, δ, K)
-    bc = 18 * K / (π * δ^4) # bond constant
-    return BBPointParameters(δ, rho, E, nu, G, K, λ, μ, Gc, εc, bc)
-end
-
[…]

### 2024-05-16 src/physics/continuum_kinematics_inspired.jl

@@ -1,52 +1,0 @@
-"""
-    CKIMaterial <: AbstractMaterial
-
-Material type for continuum-kinematics-inspired peridynamic simulations
-
-# Allowed material parameters
-
-- `horizon::Float64`: Radius of point interactions
-- `rho::Float64`: Density
-- `E::Float64`: Young's modulus
-- `nu::Float64`: Poisson's ratio
-- `Gc::Float64`: Critical energy release rate
-- `epsilon_c::Float64`: Critical strain
-
-# Allowed export fields
-
-TODO struct
-"""
-struct CKIMaterial{Correction} <: AbstractBondSystemMaterial{Correction} end
-
-CKIMaterial() = CKIMaterial{NoCorrection}()
-
-struct CKIPointParameters <: AbstractPointParameters
-    δ::Float64
-    rho::Float64
-    E::Float64
-    nu::Float64
-    G::Float64
-    K::Float64
-    λ::Float64
-    μ::Float64
-    Gc::Float64
-    εc::Float64
-    C1::Float64
-    C2::Float64
-    C3::Float64
-end
-
-@inline point_param_type(::CKIMaterial) = CKIPointParameters
-
-function get_point_params(::CKIMaterial, p::Dict{Symbol,Any})
-    δ = get_horizon(p)
-    rho = get_density(p)
-    E, nu, G, K, λ, μ = get_elastic_params(p)
-    Gc, εc = get_frac_params(p, δ, K)
-    C1 = 30 / π * μ / δ^4
-    C2 = 0.0
-    C3 = 32 / π^4 * (λ - μ) / δ^12
-    return CKIPointParameters(δ, rho, E, nu, G, K, λ, μ, Gc, εc, C1, C2, C3)
-end
-
-@inline allowed_material_kwargs(::CKIMaterial) = DEFAULT_POINT_KWARGS

### 2024-05-16 src/physics/correspondence.jl

@@ -1,196 +1,0 @@
-#TODO: remove @kwdef and do it manually with value warnings / errors.
-"""
-    NOSBMaterial <: AbstractMaterial
-
-Material type for non-ordinary state-based peridynamic simulations
-
-# Allowed material parameters
-
-- `horizon::Float64`: Radius of point interactions
-- `rho::Float64`: Density
-- `E::Float64`: Young's modulus
-- `nu::Float64`: Poisson's ratio
-- `Gc::Float64`: Critical energy release rate
-- `epsilon_c::Float64`: Critical strain
-
-# Allowed export fields
-
-- `position::Matrix{Float64}`: Position of each point
-- `displacement::Matrix{Float64}`: Displacement of each point
-- `velocity::Matrix{Float64}`: Velocity of each point
-- `velocity_half::Matrix{Float64}`: Velocity parameter for Verlet time solver
-- `acceleration::Matrix{Float64}`: Acceleration of each point
-- `b_int::Matrix{Float64}`: Internal force density of each point
-- `b_ext::Matrix{Float64}`: External force density of each point
-- `damage::Vector{Float64}`: Damage of each point
-- `n_active_bonds::Vector{Int}`: Number of intact bonds for each point
-"""
-Base.@kwdef struct NOSBMaterial <: AbstractBondSystemMaterial{NoCorrection}
-    maxdmg::Float64 = 0.95
-    maxjacobi::Float64 = 1.03
-    corr::Float64 = 100.0
-end
-
-struct NOSBPointParameters <: AbstractPointParameters
-    δ::Float64
-    rho::Float64
-    E::Float64
-    nu::Float64
-    G::Float64
-    K::Float64
-    λ::Float64
-    μ::Float64
-    Gc::Float64
-    εc::Float64
-    bc::Float64
-end
-
-function NOSBPointParameters(::NOSBMaterial, p::Dict{Symbol,Any})
-    δ = get_horizon(p)
-    rho = get_density(p)
-    E, nu, G, K, λ, μ = get_elastic_params(p)
-    Gc, εc = get_frac_params(p, δ, K)
-    bc = 18 * K / (π * δ^4) # bond constant
-    return NOSBPointParameters(δ, rho, E, nu, G, K, λ, μ, Gc, εc, bc)
-end
-
-@params NOSBMaterial NOSBPointParameters
-
-struct NOSBVerletStorage <: AbstractStorage
-    position::Matrix{Float64}
[…]

### 2024-05-16 src/physics/fracture.jl

@@ -1,102 +1,0 @@
-
-
-"""
-    failure_permit!(body, fail_permit)
-    failure_permit!(body, set, fail_permit)
-
-Determines whether failure is permitted `fail_permit = true` or prohibited
-`fail_permit = false` in the `body` or the point set `set` of the `body`.
-
-# Arguments
-
-- `body::AbstractBody`: Peridynamic body
-- `set::Symbol`: Point set on `body`
-- `fail_permit::Bool`: Decides if failure is allowed on considered body or point set.
-
-# Throws
-
-- Error if no point set called `set` exists
-
-# Example
-
-```julia-repl
-julia> failure_permit!(b, :set_bottom, false)
-
-julia> b.fail_permit
-12500-element Vector{Bool}:
- 0
- 0
- 0
- ⋮
- 1
- 1
-```
-"""
-function failure_permit! end
-
-function failure_permit!(b::AbstractBody, fail_permit::Bool)
-    b.fail_permit .= fail_permit
-    return nothing
-end
-
-function failure_permit!(b::AbstractBody, name::Symbol, fail_permit::Bool)
-    check_if_set_is_defined(b.point_sets, name)
-    b.fail_permit[b.point_sets[name]] .= fail_permit
-    return nothing
-end
-
-
-function get_frac_params(p::Dict{Symbol,Any}, δ::Float64, K::Float64)
-    local Gc::Float64
-    local εc::Float64
-
-    if haskey(p, :Gc) && !haskey(p, :epsilon_c)
-        Gc = float(p[:Gc])
-        εc = sqrt(5.0 * Gc / (9.0 * K * δ))
-    elseif !haskey(p, :Gc) && haskey(p, :epsilon_c)
-        εc = float(p[:epsilon_c])
-        Gc = 9.0 / 5.0 * K * δ * εc^2
-    elseif haskey(p, :Gc) && haskey(p, :epsilon_c)
-        msg = "insufficient keywords for calculation of fracture parameters!\n"
-        msg *= "Define either Gc or epsilon_c, not both!\n"
-        throw(ArgumentError(msg))
-    else
-        msg = "insufficient keywords for calculation of fracture parameters!\n"
-        msg *= "Define either Gc or epsilon_c!\n"
-        throw(ArgumentError(msg))
-    end
-
-    return Gc, εc
-end
-
-@inline function calc_damage!(b::AbstractBodyChunk)
-    for point_id in each_point_idx(b)
[…]

### 2024-05-16 src/physics/material_parameters.jl

@@ -1,128 +1,0 @@
-const ELASTIC_KWARGS = (:E, :nu)
-const FRAC_KWARGS = (:Gc, :epsilon_c)
-const DEFAULT_POINT_KWARGS = (:horizon, :rho, ELASTIC_KWARGS..., FRAC_KWARGS...)
-
-function allowed_material_kwargs(::AbstractMaterial)
-    return DEFAULT_POINT_KWARGS
-end
-
-"""
-    material!(body, set; kwargs...)
-    material!(body; kwargs...)
-
-Specifies material parameters used for `body` or point set `set`
-
-# Arguments
-
-- `body::AbstractBody`: Peridynamic body
-- `set::Symbol`: Point set on `body`
-
-# Keywords
-
-Allowed keywords depend on the selected material model. See material type documentation.
-Default material parameter keywords:
-
-- `horizon::Float64`: Radius of point interactions
-- `rho::Float64`: Density
-- `E::Float64`: Young's modulus
-- `nu::Float64`: Poisson's ratio
-- `Gc::Float64`: Critical energy release rate
-- `epsilon_c::Float64`: Critical strain
-
-# Throws
-
-- Error if parameter is not eligible for specification in selected material model
-
-# Example
-
-```julia-repl
-julia> material!(b; horizon=δ, E=2.1e5, rho=8e-6, Gc=2.7)
-
-julia> b.point_params
-1-element Vector{Peridynamics.BBPointParameters}:
- Peridynamics.BBPointParameters(0.0603, 8.0e-6, 210000.0, 0.25, 84000.0, 140000.0, 84000.0,
-84000.0, 2.7, 0.013329779199368195, 6.0671037207022026e10)
-```
-"""
-function material! end
-
-function material!(b::AbstractBody, name::Symbol; kwargs...)
-    check_if_set_is_defined(b.point_sets, name)
-
-    p = Dict{Symbol,Any}(kwargs)
-    check_material_kwargs(b.mat, p)
-
-    points = b.point_sets[name]
-    params = get_point_params(b.mat, p)
-
-    _material!(b, points, params)
-
-    return nothing
-end
-
-function material!(b::AbstractBody; kwargs...)
-    p = Dict{Symbol,Any}(kwargs)
-    check_material_kwargs(b.mat, p)
-
-    isempty(b.point_params) || empty!(b.point_params)
-
-    points = 1:b.n_points
[…]

### 2024-05-16 src/physics/ordinary_state_based.jl

@@ -1,163 +1,0 @@
-"""
-    OSBMaterial <: AbstractMaterial
-
-Material type for ordinary state-based peridynamic simulations
-
-# Allowed material parameters
-
-- `horizon::Float64`: Radius of point interactions
-- `rho::Float64`: Density
-- `E::Float64`: Young's modulus
-- `nu::Float64`: Poisson's ratio
-- `Gc::Float64`: Critical energy release rate
-- `epsilon_c::Float64`: Critical strain
-
-# Allowed export fields
-
-- `position::Matrix{Float64}`: Position of each point
-- `displacement::Matrix{Float64}`: Displacement of each point
-- `velocity::Matrix{Float64}`: Velocity of each point
-- `velocity_half::Matrix{Float64}`: Velocity parameter for Verlet time solver
-- `acceleration::Matrix{Float64}`: Acceleration of each point
-- `b_int::Matrix{Float64}`: Internal force density of each point
-- `b_ext::Matrix{Float64}`: External force density of each point
-- `damage::Vector{Float64}`: Damage of each point
-- `n_active_bonds::Vector{Int}`: Number of intact bonds for each point
-"""
-struct OSBMaterial{Correction} <: AbstractBondSystemMaterial{Correction} end
-
-OSBMaterial() = OSBMaterial{NoCorrection}()
-
-struct OSBPointParameters <: AbstractPointParameters
-    δ::Float64
-    rho::Float64
-    E::Float64
-    nu::Float64
-    G::Float64
-    K::Float64
-    λ::Float64
-    μ::Float64
-    Gc::Float64
-    εc::Float64
-    bc::Float64
-end
-
-function OSBPointParameters(::OSBMaterial, p::Dict{Symbol,Any})
-    δ = get_horizon(p)
-    rho = get_density(p)
-    E, nu, G, K, λ, μ = get_elastic_params(p)
-    Gc, εc = get_frac_params(p, δ, K)
-    bc = 18 * K / (π * δ^4)
-    return OSBPointParameters(δ, rho, E, nu, G, K, λ, μ, Gc, εc, bc)
-end
-
-@params OSBMaterial OSBPointParameters
-
-struct OSBVerletStorage <: AbstractStorage
-    position::Matrix{Float64}
-    displacement::Matrix{Float64}
-    velocity::Matrix{Float64}
-    velocity_half::Matrix{Float64}
-    acceleration::Matrix{Float64}
[…]

### 2024-05-16 src/time_solvers/velocity_verlet.jl

@@ -1,274 +1,0 @@
-"""
-    VelocityVerlet(; time=-1, steps=-1, stepsize=-1, safety_factor=0.7)
-
-Procedure for calculating discrete time steps
-
-# Keywords
-
-- `time::Real=-1`: Time covered by the simulation
-- `steps::Int=-1`: Number of calculated time steps
-- `stepsize::Real=-1`: Size of discrete time steps
-- `safety_factor::Real=0.7`: Safety factor for step size to ensure stability
-
-# Throws
-
-- Error if time and number of steps are specified
-- Error if no time or number of steps are specified
-- Error if safety factor is not between 0 and 1
-
-# Example
-
-```julia-repl
-julia> vv = VelocityVerlet(steps=2000)
-```
-
----
-
-!!! warning "Internal use only"
-    Please note that the fields are intended for internal use only. They are *not* part of
-    the public API of Peridynamics.jl, and thus can be altered (or removed) at any time
-    without it being considered a breaking change.
-
-```julia
-VelocityVerlet <: AbstractTimeSolver
-```
-
-# Type Parameter
--`AbstractTimeSolver`: Type of the time solver
-
-# Fields
-
-- `end_time::Float64`: Time covered by the simulation
-- `n_steps::Int`: Number of calculated time steps
-- `Δt::Float64`: Size of discrete time steps
-- `safety_factor::Float64`: Safety factor for step size to ensure stability
-"""
-mutable struct VelocityVerlet <: AbstractTimeSolver
-    end_time::Float64
-    n_steps::Int
-    Δt::Float64
-    safety_factor::Float64
-
-    function VelocityVerlet(; time::Real=-1, steps::Int=-1, stepsize::Real=-1,
-                            safety_factor::Real=0.7)
-        if time > 0 && steps > 0
-            msg = "specify either time or number of steps, not both!"
-            throw(ArgumentError(msg))
-        elseif time < 0 && steps < 0
-            msg = "specify either time or number of steps!"
-            throw(ArgumentError(msg))
-        end
-        if !(0 < safety_factor < 1)
-            msg = "wrong safety factor specified! condition: 0 < safety_factor < 1"
-            throw(ArgumentError(msg))
-        end
[…]

### 2024-05-16 test/AbaqusMeshConverter/test_AbaqusMeshConverter.jl

@@ -1,107 +1,0 @@
-@testitem "get_points" begin
-    import Peridynamics.AbaqusMeshConverter: get_points
-
-    nodes1 = Dict(
-        1 => [0.0, 0.0, 0.0],
-        2 => [1.0, 0.0, 0.0],
-        3 => [0.0, 1.0, 0.0],
-        4 => [0.0, 0.0, 1.0],
-    )
-    elements1 = Dict(
-        1 => [1, 2, 3, 4]
-    )
-    element_types1 = Dict(
-        1 => :Tet4
-    )
-    midpoints1, volumes1 = get_points(nodes1, elements1, element_types1)
-    @test midpoints1 == [0.25; 0.25; 0.25;;]
-    @test volumes1 == [1/6]
-
-    wrong_elem1 = Dict(
-        1 => [1, 2, 3, 4, 5]
-    )
-    @test_throws DimensionMismatch get_points(nodes1, wrong_elem1, element_types1)
-
-    nodes2 = Dict(
-        1 => [0.0, 1.0, 1.0],
-        2 => [0.0, 0.0, 1.0],
-        3 => [0.0, 0.0, 0.0],
-        4 => [0.0, 1.0, 0.0],
-        5 => [1.0, 1.0, 1.0],
-        6 => [1.0, 0.0, 1.0],
-        7 => [1.0, 0.0, 0.0],
-        8 => [1.0, 1.0, 0.0],
-    )
-    elements2 = Dict(
-        1 => [1, 2, 3, 4, 5, 6, 7, 8]
-    )
-    element_types2 = Dict(
-        1 => :Hex8
-    )
-    midpoints2, volumes2 = get_points(nodes2, elements2, element_types2)
-    @test midpoints2 == [0.5; 0.5; 0.5;;]
-    @test volumes2 == [1]
-
-    wrong_elem2 = Dict(
-        1 => [1, 2, 3, 4, 5, 6, 7]
-    )
-    @test_throws DimensionMismatch get_points(nodes1, wrong_elem1, element_types1)
-
-    wrong_elemtype = Dict(
-        1 => :Tet8
-    )
-    @test_throws DomainError get_points(nodes1, elements1, wrong_elemtype)
-end
-
-@testitem "midpoint" begin
-    import Peridynamics.AbaqusMeshConverter: midpoint
-
-    @test midpoint([1], [2], [3], [4]) == [2.5]
-    @test midpoint(([0, 0, 0] for _ in 1:4)...) == [0, 0, 0]
[…]

### 2024-05-16 test/VtkReader/test_read_vtk.jl

@@ -1,194 +1,0 @@
-
-
-@testitem "read complete results" begin
-    using Peridynamics.WriteVTK
-
-    bname = joinpath(@__DIR__, "vtk_test_1")
-    name = bname * ".vtu"
-    isfile(name) && rm(name)
-    n_points = 10
-    position = rand(3, n_points)
-    cells = [MeshCell(VTKCellTypes.VTK_VERTEX, (j,)) for j in 1:n_points]
-    damage = rand(n_points)
-    displacement = rand(3, n_points)
-    integer_test = rand(1:100, n_points)
-    time = rand() * 1000
-    vtk_grid(bname, position, cells) do vtk
-        vtk["Damage", VTKPointData()] = damage
-        vtk["Displacement", VTKPointData()] = displacement
-        vtk["integer_test", VTKPointData()] = integer_test
-        vtk["Time", VTKFieldData()] = time
-    end
-    result = read_vtk(name)
-
-    @test typeof(result) == Dict{Symbol, VecOrMat{<:Real}}
-    @test result[:position] == position
-    @test result[:Time] == [time]
-    @test result[:Damage] == damage
-    @test result[:Displacement] == displacement
-
-    rm(name)
-end
-
-#-- read incomplete results
-@testitem "read incomplete results" begin
-    using Peridynamics.WriteVTK
-
-    bname = joinpath(@__DIR__, "vtk_test_2")
-    name = bname * ".vtu"
-    isfile(name) && rm(name)
-    n_points = 10
-    position = rand(3, n_points)
-    cells = [MeshCell(VTKCellTypes.VTK_VERTEX, (j,)) for j in 1:n_points]
-    damage = rand(n_points)
-    time = rand() * 1000
-    random_point_data = rand(n_points)
-    random_field_data =  [1e-5, 1.0, 5]
-    vtk_grid(bname, position, cells) do vtk
-        vtk["time", VTKFieldData()] = time
-        vtk["damage", VTKPointData()] = damage
-        vtk["random_point_data", VTKPointData()] = random_point_data
-        vtk["random_field_data", VTKFieldData()] = random_field_data
-    end
-    result = read_vtk(name)
-
-    @test typeof(result) == Dict{Symbol, VecOrMat{Float64}}
-    @test result[:position] == position
-    @test result[:time] == [time]
-    @test result[:damage] == damage
-    @test result[:random_point_data] == random_point_data
[…]

### 2024-05-16 test/auxiliary/test_io.jl

@@ -1,54 +1,0 @@
-@testitem "ExportOptions BBVerletStorage" begin
-    o = Dict{Symbol,Any}(:path => "rootpath", :freq => 10)
-    eo = Peridynamics.get_export_options(Peridynamics.BBVerletStorage, o)
-    @test eo.exportflag == true
-    @test eo.root == "rootpath"
-    @test eo.vtk == joinpath("rootpath", "vtk")
-    @test eo.logfile == joinpath("rootpath", "logfile.log")
-    @test eo.freq == 10
-    @test eo.fields == [field for field in Peridynamics.DEFAULT_EXPORT_FIELDS]
-
-    o = Dict{Symbol,Any}(:path => "rootpath")
-    eo = Peridynamics.get_export_options(Peridynamics.BBVerletStorage, o)
-    @test eo.exportflag == true
-    @test eo.root == "rootpath"
-    @test eo.vtk == joinpath("rootpath", "vtk")
-    @test eo.logfile == joinpath("rootpath", "logfile.log")
-    @test eo.freq == 10
-    @test eo.fields == [field for field in Peridynamics.DEFAULT_EXPORT_FIELDS]
-
-    o = Dict{Symbol,Any}(:freq => 10)
-    msg = "if `freq` is specified, the keyword `path` is also needed!\n"
-    @test_throws ArgumentError(msg) begin
-        Peridynamics.get_export_options(Peridynamics.BBVerletStorage, o)
-    end
-
-    o = Dict{Symbol,Any}()
-    eo = Peridynamics.get_export_options(Peridynamics.BBVerletStorage, o)
-    @test eo.exportflag == false
-    @test eo.root == ""
-    @test eo.vtk == ""
-    @test eo.logfile == ""
-    @test eo.freq == 0
-    @test eo.fields == Symbol[]
-
-    o = Dict{Symbol,Any}(:path => "rootpath", :freq => -10)
-    msg = "`freq` should be larger than zero!\n"
-    @test_throws ArgumentError(msg) begin
-        Peridynamics.get_export_options(Peridynamics.BBVerletStorage, o)
-    end
-
-    o = Dict{Symbol,Any}(:path => "rootpath", :fields => (:displacement, :b_ext))
-    eo = Peridynamics.get_export_options(Peridynamics.BBVerletStorage, o)
-    @test eo.exportflag == true
-    @test eo.root == "rootpath"
-    @test eo.vtk == joinpath("rootpath", "vtk")
[…]

### 2024-05-16 test/auxiliary/test_process_each_export.jl

@@ -1,88 +1,0 @@
-@testitem "process_each_export" begin
-    root = joinpath(@__DIR__, "temp_root_proc_each_export")
-    isdir(root) && rm(root; recursive=true, force=true)
-    root_post_threads = joinpath(root, "post_threads")
-    mkpath(root_post_threads)
-    root_post_serial = joinpath(root, "post_serial")
-    mkpath(root_post_serial)
-    root_post_mpi = joinpath(root, "post_mpi")
-    mkpath(root_post_mpi)
-
-    l, Δx, δ, a = 1.0, 1 / 4, 3.015 / 4, 0.5
-    pos, vol = uniform_box(l, l, l, Δx)
-    b1 = Body(BBMaterial(), pos, vol)
-    material!(b1; horizon=3.015Δx, E=2.1e5, rho=8e-6, Gc=2.7)
-    point_set!(y -> y > l / 2 - Δx, b1, :set_top)
-    point_set!(y -> y < -l / 2 + Δx, b1, :set_bottom)
-    velocity_bc!(t -> 30, b1, :set_top, :y)
-    velocity_bc!(t -> -30, b1, :set_bottom, :y)
-    vv = VelocityVerlet(steps=2)
-    job = Job(b1, vv; path=root, freq=1)
-
-    @test_throws ArgumentError process_each_export((r0, r, id) -> nothing, job)
-
-    submit(job)
-
-    process_each_export(job) do result0, result, file_id
-        filename = string("max_displacement_", file_id, ".txt")
-        open(joinpath(root_post_threads, filename), "w+") do io
-            maxdisp = maximum(result[:displacement][1,:])
-            msg = string("maximum displacement x: ", maxdisp)
-            write(io, msg)
-        end
-        return nothing
-    end
-    file_1_threads = joinpath(root_post_threads, "max_displacement_1.txt")
-    @test isfile(file_1_threads)
-    @test contains(read(file_1_threads, String), "maximum displacement x: 0.0")
-    file_2_threads = joinpath(root_post_threads, "max_displacement_2.txt")
-    @test isfile(file_2_threads)
-    @test contains(read(file_2_threads, String), "maximum displacement x: 0.0")
-    file_3_threads = joinpath(root_post_threads, "max_displacement_3.txt")
-    @test isfile(file_3_threads)
-    @test contains(read(file_3_threads, String), "maximum displacement x: 2.4")
-
-    process_each_export(job; serial=true) do result0, result, file_id
-        filename = string("max_displacement_", file_id, ".txt")
[…]

### 2024-05-16 test/core/test_halo_exchange.jl

@@ -1,174 +1,0 @@
-@testitem "find_halo_exchanges BBMaterial" begin
-    position = [0.0 1.0 0.0 0.0
-                0.0 0.0 1.0 0.0
-                0.0 0.0 0.0 1.0]
-    volume = [1.1, 1.2, 1.3, 1.4]
-    mat = BBMaterial()
-    body = Body(mat, position, volume)
-    material!(body, horizon=2, rho=1, E=1, Gc=1)
-    point_set!(body, :a, 1:2)
-    point_set!(body, :b, 3:4)
-    velocity_ic!(body, :a, :x, 1.0)
-    velocity_bc!(t -> t, body, :a, :x)
-    forcedensity_bc!(t -> t, body, :a, :x)
-    precrack!(body, :a, :b)
-    ts = VelocityVerlet(steps=10)
-
-    param_spec = Peridynamics.get_param_spec(body)
-    point_decomp = Peridynamics.PointDecomposition(body, 2)
-    body_chunks = Peridynamics.chop_body_threads(body, ts, point_decomp, param_spec)
-
-    lth_exs, htl_exs = Peridynamics.find_halo_exchanges(body_chunks)
-
-    @test lth_exs[1][1].src_chunk_id == 2
-    @test lth_exs[1][1].dest_chunk_id == 1
-    @test lth_exs[1][1].src_idxs == [1, 2]
-    @test lth_exs[1][1].dest_idxs == [3, 4]
-    @test lth_exs[2][1].src_chunk_id == 1
-    @test lth_exs[2][1].dest_chunk_id == 2
-    @test lth_exs[2][1].src_idxs == [1, 2]
-    @test lth_exs[2][1].dest_idxs == [3, 4]
-
-    @test htl_exs[1][1].src_chunk_id == 2
-    @test htl_exs[1][1].dest_chunk_id == 1
-    @test htl_exs[1][1].src_idxs == [3, 4]
-    @test htl_exs[1][1].dest_idxs == [1, 2]
-    @test htl_exs[2][1].src_chunk_id == 1
-    @test htl_exs[2][1].dest_chunk_id == 2
-    @test htl_exs[2][1].src_idxs == [3, 4]
-    @test htl_exs[2][1].dest_idxs == [1, 2]
-
-    point_decomp = Peridynamics.PointDecomposition(body, 4)
-    body_chunks = Peridynamics.chop_body_threads(body, ts, point_decomp, param_spec)
-
[…]

### 2024-05-16 test/core/test_submit.jl

@@ -1,9 +1,0 @@
-@testitem "get_submit_options" begin
-    o = Dict{Symbol,Any}(:quiet => true)
-    quiet = Peridynamics.get_submit_options(o)
-    @test quiet == true
-
-    o = Dict{Symbol,Any}()
-    quiet = Peridynamics.get_submit_options(o)
-    @test quiet == false
-end

### 2024-05-16 test/core/test_threads_data_handler.jl

@@ -1,27 +1,0 @@
-@testitem "ThreadsDataHandler BBMaterial VelocityVerlet" begin
-    position = [0.0 1.0 0.0 0.0
-                0.0 0.0 1.0 0.0
-                0.0 0.0 0.0 1.0]
-    volume = [1.1, 1.2, 1.3, 1.4]
-    mat = BBMaterial()
-    body = Body(mat, position, volume)
-    material!(body, horizon=2, rho=1, E=1, Gc=1)
-    point_set!(body, :a, 1:2)
-    point_set!(body, :b, 3:4)
-    velocity_ic!(body, :a, :x, 1.0)
-    velocity_bc!(t->t, body, :a, :x)
-    forcedensity_bc!(t->t, body, :a, :x)
-    precrack!(body, :a, :b)
-    ts = VelocityVerlet(steps=10)
-    point_decomp = Peridynamics.PointDecomposition(body, 2)
-    tdh = Peridynamics.ThreadsDataHandler(body, ts, point_decomp)
-
-    @test tdh.n_chunks == 2
-    @test length(tdh.chunks) == 2
-    @test length(tdh.lth_exs[1]) == 1
-    @test length(tdh.lth_exs[2]) == 1
-    @test length(tdh.htl_exs[1]) == 1
-    @test length(tdh.htl_exs[2]) == 1
-
-    #TODO
-end

### 2024-05-16 test/discretization/test_body.jl

@@ -1,386 +1,0 @@
-@testitem "Body BBMaterial" begin
-    # setup
-    n_points = 10
-    mat, position, volume = BBMaterial(), rand(3, n_points), rand(n_points)
-    body = Body(mat, position, volume)
-
-    # test body creation
-    @test body.mat == BBMaterial()
-    @test body.n_points == n_points
-    @test body.position == position
-    @test body.volume == volume
-    @test body.fail_permit == fill(true, n_points)
-    @test body.single_dim_bcs == Vector{Peridynamics.SingleDimBC}()
-    @test body.single_dim_ics == Vector{Peridynamics.SingleDimIC}()
-    @test body.point_sets_precracks == Vector{Peridynamics.PointSetsPreCrack}()
-    @test body.point_sets == Dict{Symbol,Vector{Int}}()
-    @test body.point_params == Vector{Peridynamics.BBPointParameters}()
-    @test body.params_map == zeros(Int, n_points)
-end
-
-@testitem "Body CKIMaterial" begin
-    # setup
-    n_points = 10
-    mat, position, volume = CKIMaterial(), rand(3, n_points), rand(n_points)
-    body = Body(mat, position, volume)
-
-    # test body creation
-    @test body.mat == CKIMaterial()
-    @test body.n_points == n_points
-    @test body.position == position
-    @test body.volume == volume
-    @test body.fail_permit == fill(true, n_points)
-    @test body.single_dim_bcs == Vector{Peridynamics.SingleDimBC}()
-    @test body.single_dim_ics == Vector{Peridynamics.SingleDimIC}()
-    @test body.point_sets_precracks == Vector{Peridynamics.PointSetsPreCrack}()
-    @test body.point_sets == Dict{Symbol,Vector{Int}}()
-    @test body.point_params == Vector{Peridynamics.BBPointParameters}()
-    @test body.params_map == zeros(Int, n_points)
-end
-
-@testitem "point_set!" begin
-    # setup
-    position = [0.0 1.0 0.0 0.0
-                0.0 0.0 1.0 0.0
-                0.0 0.0 0.0 1.0]
-    volume = [1, 1, 1, 1]
-    mat = BBMaterial()
-    body = Body(mat, position, volume)
-
-    # test body
[…]

### 2024-05-16 test/discretization/test_body_chunk.jl

@@ -1,372 +1,0 @@
-@testitem "BodyChunk BBMaterial" begin
-    position = [0.0 1.0 0.0 0.0
-                0.0 0.0 1.0 0.0
-                0.0 0.0 0.0 1.0]
-    volume = [1.1, 1.2, 1.3, 1.4]
-    mat = BBMaterial()
-    body = Body(mat, position, volume)
-    material!(body, horizon=2, rho=1, E=1, Gc=1)
-    point_set!(body, :a, 1:2)
-    point_set!(body, :b, 3:4)
-    velocity_ic!(body, :a, :x, 1.0)
-    velocity_bc!(t->t, body, :a, :x)
-    forcedensity_bc!(t->t, body, :a, :x)
-    precrack!(body, :a, :b)
-    ts = VelocityVerlet(steps=10)
-    pd = Peridynamics.PointDecomposition(body, 2)
-    ps = Peridynamics.get_param_spec(body)
-    bc = Peridynamics.BodyChunk(body, ts, pd, 1, ps)
-
-    @test bc.mat == mat
-    @test bc.system isa Peridynamics.BondSystem
-    @test bc.system.position == position
-    @test bc.system.volume == volume
-    @test bc.system.bonds == [
-        Peridynamics.Bond(2, 1.0, true),
-        Peridynamics.Bond(3, 1.0, true),
-        Peridynamics.Bond(4, 1.0, true),
-        Peridynamics.Bond(1, 1.0, true),
-        Peridynamics.Bond(3, √2, true),
-        Peridynamics.Bond(4, √2, true),
-    ]
-    @test bc.system.n_neighbors == [3, 3]
-    @test bc.system.bond_ids == [1:3, 4:6]
-
-    @test bc.ch.point_ids == [1, 2, 3, 4]
-    @test bc.ch.loc_points == pd.decomp[1]
-    @test bc.ch.halo_points == [3, 4]
-    @test bc.ch.hidxs_by_src[2] == 3:4
-    for i in 1:4
-        @test bc.ch.localizer[i] == i
-    end
-
-    #TODO: test the other fields!
-end
-
-
-@testitem "chop_body_threads BBMaterial N=1" begin
-    position = [0.0 1.0 0.0 0.0
-                0.0 0.0 1.0 0.0
-                0.0 0.0 0.0 1.0]
[…]

### 2024-05-16 test/discretization/test_bond_discretization.jl

@@ -1,189 +1,0 @@
-@testitem "BondSystem" begin
-    # setup
-    position = [0.0 1.0 0.0 0.0
-                0.0 0.0 1.0 0.0
-                0.0 0.0 0.0 1.0]
-    volume = [1.1, 1.2, 1.3, 1.4]
-    mat = BBMaterial()
-    body = Body(mat, position, volume)
-    material!(body, horizon=2, rho=1, E=1, Gc=1)
-    pd = Peridynamics.PointDecomposition(body, 2)
-
-    # 1
-    bd, ch = Peridynamics.BondSystem(body, pd, 1)
-
-    @test bd.position == position
-    @test bd.volume == volume
-    @test bd.bonds == [
-        Peridynamics.Bond(2, 1.0, true),
-        Peridynamics.Bond(3, 1.0, true),
-        Peridynamics.Bond(4, 1.0, true),
-        Peridynamics.Bond(1, 1.0, true),
-        Peridynamics.Bond(3, √2, true),
-        Peridynamics.Bond(4, √2, true),
-    ]
-    @test bd.n_neighbors == [3, 3]
-    @test bd.bond_ids == [1:3, 4:6]
-
-    @test ch.point_ids == [1, 2, 3, 4]
-    @test ch.loc_points == [1, 2]
-    @test ch.halo_points == [3, 4]
-    @test ch.hidxs_by_src[2] == 3:4
-
-    for i in 1:4
-        @test ch.localizer[i] == i
-    end
-
-    # 2
-    bd, ch = Peridynamics.BondSystem(body, pd, 2)
-
-    @test bd.position == position[:, [3, 4, 1, 2]]
-    @test bd.volume == volume[[3, 4, 1, 2]]
-    @test bd.bonds == [
-        Peridynamics.Bond(3, 1.0, true),
-        Peridynamics.Bond(4, √2, true),
-        Peridynamics.Bond(2, √2, true),
-        Peridynamics.Bond(3, 1.0, true),
-        Peridynamics.Bond(4, √2, true),
-        Peridynamics.Bond(1, √2, true),
-    ]
-    @test bd.n_neighbors == [3, 3]
-    @test bd.bond_ids == [1:3, 4:6]
-
-    @test ch.point_ids == [3, 4, 1, 2]
-    @test ch.loc_points == [3, 4]
-    @test ch.halo_points == [1, 2]
-    @test ch.hidxs_by_src[1] == 3:4
-    @test ch.localizer[3] == 1
-    @test ch.localizer[4] == 2
[…]

### 2024-05-16 test/discretization/test_chunk_handler.jl

@@ -1,163 +1,0 @@
-@testitem "find_localizer" begin
-    point_ids_1 = [10, 20, 30, 40]
-    localizer_1 = Peridynamics.find_localizer(point_ids_1)
-    @test localizer_1[10] == 1
-    @test localizer_1[20] == 2
-    @test localizer_1[30] == 3
-    @test localizer_1[40] == 4
-
-    point_ids_2 = unique(rand(1:200, 200))
-    localizer_2 = Peridynamics.find_localizer(point_ids_2)
-    for (li, gi) in enumerate(point_ids_2)
-        @test localizer_2[gi] == li
-    end
-end
-
-@testitem "localize!" begin
-    point_ids_1 = [10, 20, 30, 40]
-    localizer_1 = Peridynamics.find_localizer(point_ids_1)
-    point_set_1 = [40, 30, 20, 10]
-    Peridynamics.localize!(point_set_1, localizer_1)
-    @test point_set_1 == [4, 3, 2, 1]
-
-    Peridynamics.localize!(point_ids_1, localizer_1)
-    @test point_ids_1 == [1, 2, 3, 4]
-
-    point_ids_2 = unique(rand(1:200, 200))
-    localizer_2 = Peridynamics.find_localizer(point_ids_2)
-    Peridynamics.localize!(point_ids_2, localizer_2)
-    for i in eachindex(point_ids_2)
-        @test point_ids_2[i] == i
-    end
-end
-
-@testitem "localize" begin
-    point_ids = collect(101:200)
-    loc_points = 101:200
-    n_loc_points = length(loc_points)
-    halo_points = Vector{Int}()
-    hidxs_by_src = Dict{Int,UnitRange{Int}}()
-    localizer = Peridynamics.find_localizer(point_ids)
-    ch = Peridynamics.ChunkHandler(n_loc_points, point_ids, loc_points, halo_points,
-                                   hidxs_by_src, localizer)
-
-    point_set = [101, 110, 120, 210, 220]
-    loc_point_set = Peridynamics.localize(point_set, ch)
-    @test loc_point_set == [1, 10, 20]
-end
-
-@testitem "localized_point_sets" begin
-    point_ids = collect(101:200)
-    loc_points = 101:200
-    n_loc_points = length(loc_points)
-    halo_points = Vector{Int}()
[…]

### 2024-05-16 test/discretization/test_decomposition.jl

@@ -1,11 +1,0 @@
-@testitem "distribute_equally" begin
-    @test Peridynamics.distribute_equally(4, 2) == [1:2, 3:4]
-    @test Peridynamics.distribute_equally(3, 2) == [1:2, 3:3]
-    @test Peridynamics.distribute_equally(2, 3) == [1:1, 2:2, 0:-1]
-end
-
-@testitem "find_localizer" begin
-    point_ids = [101, 102, 103]
-    localizer = Peridynamics.find_localizer(point_ids)
-    @test localizer == Dict(101 => 1, 102 => 2, 103 => 3)
-end

### 2024-05-16 test/discretization/test_find_points.jl

@@ -1,35 +1,0 @@
-@testitem "find_points" begin
-    #setup
-    position = [
-        0.0 1.0 0.0 0.0 1.0
-        0.0 0.0 1.0 0.0 1.0
-        0.0 0.0 0.0 1.0 1.0
-    ]
-    # find the points with different function names
-    p = Peridynamics.find_points(p -> p[3] > 0.1 && p[2] > 0.1, position)
-    @test p == [5]
-    p = Peridynamics.find_points(p -> p[1] > 0.1 || p[2] > 0.1, position)
-    @test p == [2, 3, 5]
-    p = Peridynamics.find_points(p -> p[1] < -0.1 || p[2] < -0.1, position)
-    @test p == Vector{Int}()
-    px = Peridynamics.find_points(x -> x > 0.1, position)
-    @test px == [2, 5]
-    px = Peridynamics.find_points(x -> x < -0.1, position)
-    @test px == Vector{Int}()
-    py = Peridynamics.find_points(y -> y > 0.1, position)
-    @test py == [3, 5]
-    py = Peridynamics.find_points(y -> y < -0.1, position)
-    @test py == Vector{Int}()
-    pz = Peridynamics.find_points(z -> z > 0.1, position)
-    @test pz == [4, 5]
-    pz = Peridynamics.find_points(z -> z < -0.1, position)
-    @test pz == Vector{Int}()
-
-    @test_throws ArgumentError Peridynamics.find_points(k -> k > 0.1, position)
-    @test_throws ArgumentError Peridynamics.find_points((k,x) -> x > 0.1, position)
-    @test_throws ArgumentError Peridynamics.find_points(() -> 1, position)
-
-    findfunc(x::Int) = x < 0
-    findfunc(x::Float64) = x > 0
-    @test_throws ArgumentError Peridynamics.find_points(findfunc, position)
-end

### 2024-05-16 test/discretization/test_multibody_setup.jl

@@ -1,39 +1,0 @@
-@testitem "MultibodySetup" begin
-    b1 = Body(BBMaterial(), rand(3,10), rand(10))
-    b2 = Body(BBMaterial(), rand(3,10), rand(10))
-    b3 = Body(CKIMaterial(), rand(3,10), rand(10))
-
-    ms = MultibodySetup(:body1 => b1, :body2 => b2)
-    @test ms isa MultibodySetup{Peridynamics.BBMaterial{Peridynamics.NoCorrection},Peridynamics.BBPointParameters}
-    @test Peridynamics.material_type(ms) == Peridynamics.BBMaterial{Peridynamics.NoCorrection}
-    @test length(ms.bodies) == 2
-    @test isempty(ms.contacts)
-
-    ms = MultibodySetup(Dict(:body1 => b1, :body2 => b2))
-    @test ms isa MultibodySetup{Peridynamics.BBMaterial{Peridynamics.NoCorrection},Peridynamics.BBPointParameters}
-    @test Peridynamics.material_type(ms) == Peridynamics.BBMaterial{Peridynamics.NoCorrection}
-    @test length(ms.bodies) == 2
-    @test isempty(ms.contacts)
-
-    @test_throws ArgumentError MultibodySetup(:body1 => b1, :body3 => b3)
-end
-
-@testitem "contact!" begin
-    b1 = Body(BBMaterial(), rand(3,10), rand(10))
-    b2 = Body(BBMaterial(), rand(3,10), rand(10))
-    ms = MultibodySetup(:body1 => b1, :body2 => b2)
-
-    contact!(ms, :body1, :body2; radius=1)
-    @test ms.contacts[1] == Peridynamics.Contact(:body1, :body2, 1.0, 1e12)
-    empty!(ms.contacts)
-
-    contact!(ms, :body1, :body2; radius=2, sc=1.5e12)
-    @test ms.contacts[1] == Peridynamics.Contact(:body1, :body2, 2.0, 1.5e12)
-    empty!(ms.contacts)
-
-    @test_throws UndefKeywordError(:radius) contact!(ms, :body1, :body2)
-
-    @test_throws ArgumentError contact!(ms, :body1, :body2; radius=0)
-
-    @test_throws ArgumentError contact!(ms, :body1, :body2; radius=1, sc=0)
-end

### 2024-05-16 test/discretization/test_predefined_cracks.jl

@@ -1,33 +1,0 @@
-@testitem "precrack!" begin
-    # setup
-    position = [0.0 1.0 0.0 0.0
-                0.0 0.0 1.0 0.0
-                0.0 0.0 0.0 1.0]
-    volume = [1, 1, 1, 1]
-    mat = BBMaterial()
-    body = Body(mat, position, volume)
-
-    # test body creation
-    @test body.n_points == 4
-    @test body.position == position
-    @test body.volume == volume
-    @test body.fail_permit == fill(true, 4)
-
-    # add point sets
-    point_set!(body, :a, [1, 2])
-    point_set!(body, :b, [2])
-    point_set!(body, :c, [3])
-    point_set!(body, :d, [4])
-
-    # precrack! with dmg update = no bond filtering
-    precrack!(body, :a, :c)
-    @test body.point_sets_precracks == [Peridynamics.PointSetsPreCrack(:a, :c, false)]
-
-    # precrack! without dmg update = bond filtering
-    precrack!(body, :a, :d; update_dmg=false)
-    @test body.point_sets_precracks == [Peridynamics.PointSetsPreCrack(:a, :c, false),
-                                        Peridynamics.PointSetsPreCrack(:a, :d, true),]
-
-    # precrack! with set :a and :b which intersect
-    @test_throws ArgumentError precrack!(body, :a, :b)
-end

### 2024-05-16 test/integration/material_interface.jl

@@ -1,290 +1,0 @@
-@testitem "Material declaration" begin
-    struct TestMaterial1 <: Peridynamics.AbstractMaterial end
-    struct WrongTestMaterial end
-
-    @test isnothing(Peridynamics.typecheck_material(TestMaterial1))
-    @test_throws ArgumentError Peridynamics.typecheck_material(WrongTestMaterial)
-end
-
-@testitem "Point parameters declaration" begin
-    struct TestMaterial2 <: Peridynamics.AbstractMaterial end
-    struct TestPointParameters <: Peridynamics.AbstractPointParameters
-        δ::Float64
-        rho::Float64
-        E::Float64
-        nu::Float64
-        G::Float64
-        K::Float64
-        λ::Float64
-        μ::Float64
-        Gc::Float64
-        εc::Float64
-    end
-    @test isnothing(Peridynamics.typecheck_params(TestPointParameters))
-
-    struct PointParametersNoSubtype
-        δ::Float64
-        rho::Float64
-        E::Float64
-        nu::Float64
-        G::Float64
-        K::Float64
-        λ::Float64
-        μ::Float64
-        Gc::Float64
-        εc::Float64
-    end
-    @test_throws ArgumentError Peridynamics.typecheck_params(PointParametersNoSubtype)
-
-    struct PointParametersMissingHorizon <: Peridynamics.AbstractPointParameters
-        rho::Float64
-        E::Float64
-        nu::Float64
-        G::Float64
-        K::Float64
-        λ::Float64
-        μ::Float64
-        Gc::Float64
-        εc::Float64
-    end
-    @test_throws ErrorException Peridynamics.typecheck_params(PointParametersMissingHorizon)
-
-    Peridynamics.@params TestMaterial2 TestPointParameters
-    @test hasmethod(Peridynamics.point_param_type, Tuple{TestMaterial2})
-    @test Peridynamics.point_param_type(TestMaterial2()) == TestPointParameters
-    @test hasmethod(Peridynamics.get_point_params, Tuple{TestMaterial2,Dict{Symbol,Any}})
-end
-
-# TODO
-# @testitem "System declaration" begin
[…]

### 2024-05-16 test/integration/mpi_threads_comparison.jl

@@ -1,267 +1,0 @@
-@testitem "MPI-Threads comparison BBMaterial{NoCorrection}" begin
-    root = joinpath(@__DIR__, "temp_mpi_threads_comparison")
-    path_threads = joinpath(root, "results_threads")
-    path_threads_vtk = joinpath(path_threads, "vtk")
-    path_mpi = joinpath(root, "results_mpi")
-    path_mpi_vtk = joinpath(path_mpi, "vtk")
-
-    function sim_bb(N::Int, path::String)
-        l, Δx, δ, a = 1.0, 1/N, 3.015/N, 0.5
-        pos, vol = uniform_box(l, l, 0.1l, Δx)
-        ids = sortperm(pos[2,:])
-        b = Body(BBMaterial(), pos[:, ids], vol[ids])
-        material!(b; horizon=3.015Δx, E=2.1e5, rho=8e-6, Gc=2.7)
-        point_set!(p -> p[1] ≤ -l/2+a && 0 ≤ p[2] ≤ 2δ, b, :set_a)
-        point_set!(p -> p[1] ≤ -l/2+a && -2δ ≤ p[2] < 0, b, :set_b)
-        precrack!(b, :set_a, :set_b)
-        point_set!(p -> p[2] > l/2-Δx, b, :set_top)
-        point_set!(p -> p[2] < -l/2+Δx, b, :set_bottom)
-        velocity_bc!(t -> -30, b, :set_bottom, :y)
-        velocity_bc!(t -> 30, b, :set_top, :y)
-        vv = VelocityVerlet(steps=100)
-        job = Job(b, vv; path=path, freq=50)
-        submit(job)
-        return nothing
-    end
-    sim_bb(30, path_threads)
-
-    mpi_cmd = """
-    using Peridynamics
-    function sim_bb(N::Int, path::String)
-        l, Δx, δ, a = 1.0, 1/N, 3.015/N, 0.5
-        pos, vol = uniform_box(l, l, 0.1l, Δx)
-        ids = sortperm(pos[2,:])
-        b = Body(BBMaterial(), pos[:, ids], vol[ids])
-        material!(b; horizon=3.015Δx, E=2.1e5, rho=8e-6, Gc=2.7)
-        point_set!(p -> p[1] ≤ -l/2+a && 0 ≤ p[2] ≤ 2δ, b, :set_a)
-        point_set!(p -> p[1] ≤ -l/2+a && -2δ ≤ p[2] < 0, b, :set_b)
-        precrack!(b, :set_a, :set_b)
[…]

### 2024-05-16 test/integration/predefined_cracks.jl

@@ -1,226 +1,0 @@
-@testitem "precrack bond chunk" begin
-    position = [0.0 1.0 0.0 0.0
-                0.0 0.0 1.0 0.0
-                0.0 0.0 0.0 1.0]
-    volume = [1.1, 1.2, 1.3, 1.4]
-    mat = BBMaterial()
-    body = Body(mat, position, volume)
-    material!(body, horizon=2, rho=1, E=1, Gc=1)
-    point_set!(body, :a, 1:2)
-    point_set!(body, :b, 3:4)
-    precrack!(body, :a, :b)
-    ts = VelocityVerlet(steps=10)
-    point_decomp = Peridynamics.PointDecomposition(body, 2)
-    param_spec = Peridynamics.get_param_spec(body)
-
-    body_chunks = Peridynamics.chop_body_threads(body, ts, point_decomp, param_spec)
-
-    b1 = body_chunks[1]
-    @test b1 isa Peridynamics.BodyChunk
-    @test b1.mat == BBMaterial()
-    @test b1.system isa Peridynamics.BondSystem
-    @test b1.system.position == position
-    @test b1.system.volume == volume
-    @test b1.system.bonds == [
-        Peridynamics.Bond(2, 1.0, true),
-        Peridynamics.Bond(3, 1.0, true),
-        Peridynamics.Bond(4, 1.0, true),
-        Peridynamics.Bond(1, 1.0, true),
-        Peridynamics.Bond(3, √2, true),
-        Peridynamics.Bond(4, √2, true),
-    ]
-    @test b1.system.n_neighbors == [3, 3]
-    @test b1.system.bond_ids == [1:3, 4:6]
-
-    @test b1.storage.position == position
-    @test b1.storage.displacement == zeros(3, 2)
-    @test b1.storage.velocity == zeros(3, 2)
-    @test b1.storage.velocity_half == zeros(3, 2)
-    @test b1.storage.acceleration == zeros(3, 2)
-    @test b1.storage.b_int == zeros(3, 2)
-    @test b1.storage.b_ext == zeros(3, 2)
-    @test b1.storage.damage ≈ [2/3, 2/3]
-    @test b1.storage.bond_active == [1, 0, 0, 1, 0, 0]
-    @test b1.storage.n_active_bonds == [1, 1]
-
-    @test b1.ch.point_ids == [1, 2, 3, 4]
-    @test b1.ch.loc_points == 1:2
[…]

### 2024-05-16 test/integration/symmetry_bond_based.jl

@@ -1,58 +1,0 @@
-@testitem "symmetry BBMaterial" begin
-    # simulation
-    Δx = 0.2
-    width = 1
-    grid⁺ = Δx/2:Δx:width/2
-    grid⁻ = -reverse(grid⁺)
-    grid = [grid⁻; grid⁺]
-    pos = hcat(([x;y;z] for x in grid for y in grid for z in grid)...)
-    n_points = size(pos, 2)
-    vol = fill(Δx^3, n_points)
-    body = Body(BBMaterial(), pos, vol)
-    failure_permit!(body, false)
-    material!(body, horizon=3.015Δx, rho=7850, E=210e9, Gc=1)
-    point_set!(z -> z > width/2 - 0.6Δx, body, :set_a)
-    point_set!(z -> z < -width/2 + 0.6Δx, body, :set_b)
-    velocity_bc!(t -> 100, body, :set_a, :z)
-    velocity_bc!(t -> -100, body, :set_b, :z)
-    vv = VelocityVerlet(steps=100)
-    temp_root = joinpath(@__DIR__, "temp_root_symmetry_test")
-    rm(temp_root; recursive=true, force=true)
-    job = Job(body, vv; path=temp_root, freq=10)
-    dh = Peridynamics.submit_threads(job, 1)
-
-    # check if the correct files were exported
-    @test length(filter(x->endswith(x,".pvtu"), readdir(joinpath(temp_root,"vtk")))) == 11
-
-    # find the points that should have symmetrical positions
-    xp = findall(pos[1,:] .> 0)
-    xm = findall(pos[1,:] .< 0)
-    yp = findall(pos[2,:] .> 0)
-    ym = findall(pos[2,:] .< 0)
-    zp = findall(pos[3,:] .> 0)
-    zm = findall(pos[3,:] .< 0)
-
-    # check the symmetry
-    end_position = first(dh.chunks).storage.position
-    @test !(end_position ≈ pos)
-    @test sort(end_position[1,xp]) ≈ sort(-end_position[1,xm])
-    @test sort(end_position[2,xp]) ≈ sort(end_position[2,xm])
-    @test sort(end_position[3,xp]) ≈ sort(end_position[3,xm])
-    @test sort(end_position[1,yp]) ≈ sort(end_position[1,ym])
-    @test sort(end_position[2,yp]) ≈ sort(-end_position[2,ym])
[…]

### 2024-05-16 test/integration/symmetry_correspondence.jl

@@ -1,58 +1,0 @@
-@testitem "symmetry NOSBMaterial" begin
-    # simulation
-    Δx = 0.2
-    width = 1
-    grid⁺ = Δx/2:Δx:width/2
-    grid⁻ = -reverse(grid⁺)
-    grid = [grid⁻; grid⁺]
-    pos = hcat(([x;y;z] for x in grid for y in grid for z in grid)...)
-    n_points = size(pos, 2)
-    vol = fill(Δx^3, n_points)
-    body = Body(NOSBMaterial(), pos, vol)
-    failure_permit!(body, false)
-    material!(body, horizon=3.015Δx, rho=7850, E=210e9, nu=0.25, Gc=1)
-    point_set!(z -> z > width/2 - 0.6Δx, body, :set_a)
-    point_set!(z -> z < -width/2 + 0.6Δx, body, :set_b)
-    velocity_bc!(t -> 100, body, :set_a, :z)
-    velocity_bc!(t -> -100, body, :set_b, :z)
-    vv = VelocityVerlet(steps=100)
-    temp_root = joinpath(@__DIR__, "temp_root_symmetry_test")
-    rm(temp_root; recursive=true, force=true)
-    job = Job(body, vv; path=temp_root, freq=10)
-    dh = Peridynamics.submit_threads(job, 1)
-
-    # check if the correct files were exported
-    @test length(filter(x->endswith(x,".pvtu"), readdir(joinpath(temp_root,"vtk")))) == 11
-
-    # find the points that should have symmetrical positions
-    xp = findall(pos[1,:] .> 0)
-    xm = findall(pos[1,:] .< 0)
-    yp = findall(pos[2,:] .> 0)
-    ym = findall(pos[2,:] .< 0)
-    zp = findall(pos[3,:] .> 0)
-    zm = findall(pos[3,:] .< 0)
-
-    # check the symmetry
-    end_position = first(dh.chunks).storage.position
-    @test !(end_position ≈ pos)
-    @test sort(end_position[1,xp]) ≈ sort(-end_position[1,xm])
-    @test sort(end_position[2,xp]) ≈ sort(end_position[2,xm])
-    @test sort(end_position[3,xp]) ≈ sort(end_position[3,xm])
-    @test sort(end_position[1,yp]) ≈ sort(end_position[1,ym])
-    @test sort(end_position[2,yp]) ≈ sort(-end_position[2,ym])
-    @test sort(end_position[3,yp]) ≈ sort(end_position[3,ym])
[…]

### 2024-05-16 test/integration/symmetry_ordinary_state_based.jl

@@ -1,58 +1,0 @@
-@testitem "symmetry OSBMaterial" begin
-    # simulation
-    Δx = 0.2
-    width = 1
-    grid⁺ = Δx/2:Δx:width/2
-    grid⁻ = -reverse(grid⁺)
-    grid = [grid⁻; grid⁺]
-    pos = hcat(([x;y;z] for x in grid for y in grid for z in grid)...)
-    n_points = size(pos, 2)
-    vol = fill(Δx^3, n_points)
-    body = Body(OSBMaterial(), pos, vol)
-    failure_permit!(body, false)
-    material!(body, horizon=3.015Δx, rho=7850, E=210e9, nu=0.25, Gc=1)
-    point_set!(z -> z > width/2 - 0.6Δx, body, :set_a)
-    point_set!(z -> z < -width/2 + 0.6Δx, body, :set_b)
-    velocity_bc!(t -> 100, body, :set_a, :z)
-    velocity_bc!(t -> -100, body, :set_b, :z)
-    vv = VelocityVerlet(steps=100)
-    temp_root = joinpath(@__DIR__, "temp_root_symmetry_test")
-    rm(temp_root; recursive=true, force=true)
-    job = Job(body, vv; path=temp_root, freq=10)
-    dh = Peridynamics.submit_threads(job, 1)
-
-    # check if the correct files were exported
-    @test length(filter(x->endswith(x,".pvtu"), readdir(joinpath(temp_root,"vtk")))) == 11
-
-    # find the points that should have symmetrical positions
-    xp = findall(pos[1,:] .> 0)
-    xm = findall(pos[1,:] .< 0)
-    yp = findall(pos[2,:] .> 0)
-    ym = findall(pos[2,:] .< 0)
-    zp = findall(pos[3,:] .> 0)
-    zm = findall(pos[3,:] .< 0)
-
-    # check the symmetry
-    end_position = first(dh.chunks).storage.position
-    @test !(end_position ≈ pos)
-    @test sort(end_position[1,xp]) ≈ sort(-end_position[1,xm])
-    @test sort(end_position[2,xp]) ≈ sort(end_position[2,xm])
-    @test sort(end_position[3,xp]) ≈ sort(end_position[3,xm])
-    @test sort(end_position[1,yp]) ≈ sort(end_position[1,ym])
-    @test sort(end_position[2,yp]) ≈ sort(-end_position[2,ym])
-    @test sort(end_position[3,yp]) ≈ sort(end_position[3,ym])
[…]

### 2024-05-16 test/integration/test_material.jl

@@ -1,54 +1,0 @@
-struct TestMaterial <: Peridynamics.AbstractBondSystemMaterial{Peridynamics.NoCorrection} end
-struct TestPointParameters <: Peridynamics.AbstractPointParameters
-    δ::Float64
-    rho::Float64
-    E::Float64
-    nu::Float64
-    G::Float64
-    K::Float64
-    λ::Float64
-    μ::Float64
-    Gc::Float64
-    εc::Float64
-end
-function TestPointParameters(::TestMaterial, p::Dict{Symbol,Any})
-    δ = Peridynamics.get_horizon(p)
-    rho = Peridynamics.get_density(p)
-    E, nu, G, K, λ, μ = Peridynamics.get_elastic_params(p)
-    Gc, εc = Peridynamics.get_frac_params(p, δ, K)
-    return TestPointParameters(δ, rho, E, nu, G, K, λ, μ, Gc, εc)
-end
-Peridynamics.@params TestMaterial TestPointParameters
-# Peridynamics.@system TestMaterial Peridynamics.BondSystem
-struct TestVerletStorage <: Peridynamics.AbstractStorage
-    position::Matrix{Float64}
-    displacement::Matrix{Float64}
-    velocity::Matrix{Float64}
-    velocity_half::Matrix{Float64}
-    acceleration::Matrix{Float64}
-    b_int::Matrix{Float64}
-    b_ext::Matrix{Float64}
-    damage::Vector{Float64}
-    bond_active::Vector{Bool}
-    n_active_bonds::Vector{Int}
-end
-function TestVerletStorage(::TestMaterial, ::Peridynamics.VelocityVerlet,
-                           system::Peridynamics.BondSystem, ch::Peridynamics.ChunkHandler)
-    n_loc_points = length(ch.loc_points)
-    position = copy(system.position)
-    displacement = zeros(3, n_loc_points)
-    velocity = zeros(3, n_loc_points)
-    velocity_half = zeros(3, n_loc_points)
-    acceleration = zeros(3, n_loc_points)
-    b_int = zeros(3, length(ch.point_ids))
-    b_ext = zeros(3, n_loc_points)
-    damage = zeros(n_loc_points)
-    bond_active = ones(Bool, length(system.bonds))
-    n_active_bonds = copy(system.n_neighbors)
-    return TestVerletStorage(position, displacement, velocity, velocity_half,
-                             acceleration, b_int, b_ext, damage, bond_active,
[…]

### 2024-05-16 test/physics/test_bond_based.jl

@@ -1,21 +1,0 @@
-@testitem "get_storage" begin
-    position, volume = uniform_box(1,1,1,0.25)
-    body = Body(BBMaterial(), position, volume)
-    material!(body, horizon=2, rho=1, E=1, Gc=1)
-    ts = VelocityVerlet(steps=10)
-    pd = Peridynamics.PointDecomposition(body, 1)
-    db, ch = Peridynamics.get_system(body, pd, 1)
-    s = Peridynamics.get_storage(body.mat, ts, db, ch)
-
-    @test s isa Peridynamics.BBVerletStorage
-    @test s.position == position
-    @test s.displacement == zeros(3, 64)
-    @test s.velocity == zeros(3, 64)
-    @test s.velocity_half == zeros(3, 64)
-    @test s.acceleration == zeros(3, 64)
-    @test s.b_int == zeros(3, 64)
-    @test s.b_ext == zeros(3, 64)
-    @test s.damage == zeros(64)
-    @test s.bond_active == ones(Bool, 4032)
-    @test s.n_active_bonds == fill(63, 64)
-end

### 2024-05-16 test/physics/test_material_parameters.jl

@@ -1,70 +1,0 @@
-@testitem "get_horizon" begin
-    p = Dict{Symbol,Any}(:horizon => 1)
-    rho = Peridynamics.get_horizon(p)
-    @test rho ≈ 1.0
-
-    p = Dict{Symbol,Any}(:nothorizon => 1)
-    @test_throws UndefKeywordError(:horizon) Peridynamics.get_horizon(p)
-
-    p = Dict{Symbol,Any}(:horizon => 0)
-    msg = "`horizon` should be larger than zero!\n"
-    @test_throws ArgumentError(msg) Peridynamics.get_horizon(p)
-end
-
-@testitem "get_density" begin
-    p = Dict{Symbol,Any}(:rho => 1)
-    rho = Peridynamics.get_density(p)
-    @test rho ≈ 1.0
-
-    p = Dict{Symbol,Any}(:notrho => 1)
-    @test_throws UndefKeywordError(:rho) Peridynamics.get_density(p)
-
-    p = Dict{Symbol,Any}(:rho => 0)
-    msg = "`rho` should be larger than zero!\n"
-    @test_throws ArgumentError(msg) Peridynamics.get_density(p)
-end
-
-@testitem "get_elastic_params" begin
-    p = Dict{Symbol,Any}(:E => 1, :nu => 0.25)
-    E, nu, G, K, λ, μ = Peridynamics.get_elastic_params(p)
-    @test E ≈ 1.0
-    @test nu ≈ 0.25
-    @test G ≈ 0.4
-    @test K ≈ 2/3
-    @test λ ≈ 0.4
-    @test μ ≈ 0.4
-
-    p = Dict{Symbol,Any}(:E => 210e9, :nu => 0.25)
-    E, nu, G, K, λ, μ = Peridynamics.get_elastic_params(p)
-    @test E ≈ 2.1e11
-    @test nu ≈ 0.25
-    @test G ≈ 8.4e10
-    @test K ≈ 1.4e11
-    @test λ ≈ 8.4e10
-    @test μ ≈ 8.4e10
-
-    p = Dict{Symbol,Any}(:E => 27e9, :nu => 0.2)
-    E, nu, G, K, λ, μ = Peridynamics.get_elastic_params(p)
-    @test E ≈ 2.7e10
-    @test nu ≈ 0.2
-    @test G ≈ 1.125e10
-    @test K ≈ 1.5e10
-    @test λ ≈ 7.5e9
-    @test μ ≈ 1.125e10
-
[…]

### 2024-05-16 test/runtests.jl

@@ -1,3 +1,0 @@
-using TestItemRunner
-
-@run_package_tests verbose=true

### 2024-05-16 test/time_solvers/test_velocity_verlet.jl

@@ -1,98 +1,0 @@
-@testitem "VelocityVerlet steps" begin
-    vv = VelocityVerlet(steps=1000)
-    @test vv.end_time == -1.0
-    @test vv.n_steps == 1000
-    @test vv.Δt == -1.0
-    @test vv.safety_factor == 0.7
-end
-
-@testitem "VelocityVerlet time" begin
-    vv = VelocityVerlet(time=1)
-    @test vv.end_time == 1.0
-    @test vv.n_steps == -1
-    @test vv.Δt == -1.0
-    @test vv.safety_factor == 0.7
-end
-
-@testitem "VelocityVerlet time & stepsize" begin
-    vv = (@test_logs (:warn,) VelocityVerlet(time=1, stepsize=0.1))
-    @test vv.end_time == 1.0
-    @test vv.n_steps == -1
-    @test vv.Δt == 0.1
-    @test vv.safety_factor == 0.7
-end
-
-@testitem "VelocityVerlet steps & stepsize" begin
-    vv = (@test_logs (:warn,) VelocityVerlet(steps=10, stepsize=0.1))
-    @test vv.end_time == -1.0
-    @test vv.n_steps == 10
-    @test vv.Δt == 0.1
-    @test vv.safety_factor == 0.7
-end
-
-@testitem "VelocityVerlet wrong input" begin
-    @test_throws ArgumentError VelocityVerlet(time=1, steps=10)
-    @test_throws ArgumentError VelocityVerlet()
-    @test_throws ArgumentError VelocityVerlet(time=1.0, safety_factor=0)
-    @test_throws ArgumentError VelocityVerlet(time=1.0, safety_factor=1)
-end
-
-@testitem "init_time_solver! ThreadsDataHandler" begin
-    pos = [0 1; 0 0; 0 0]
-    Δx, δ = 1, 1.5
-    E, nu, rho = 1, 0.25, 1
-    vol = fill(Δx^3, 2)
-    body = Body(BBMaterial(), pos, vol)
-    material!(body, horizon=δ, rho=rho, E=E, Gc=1)
-
-    vv = VelocityVerlet(steps=10)
-
-    point_decomp = Peridynamics.PointDecomposition(body, 1)
-    tdh = Peridynamics.ThreadsDataHandler(body, vv, point_decomp)
-    Peridynamics.init_time_solver!(vv, tdh)
-
[…]

### 2024-05-16 paper/header.tex
Initial state

@@
 
-\title{My JuliaCon proceeding}
+\title{Simulation of fracture and damage with Peridynamics.jl}
 
-\author[1]{1st author}
-\author[1, 2]{2nd author}
-\author[2]{3rd author}
-\affil[1]{University}
-\affil[2]{National Lab}
+\author[1]{Kai Partmann}
+\author[1]{Manuel Dienst}
+\author[1]{Kerstin Weinberg}
+\affil[1]{Chair of Solid Mechanics, University of Siegen, Siegen, Germany}
 
-\keywords{Julia, Optimization, Game theory, Compiler}
+\keywords{Julia, Peridynamics, Fracture Mechanics, Simulations, Simulation Framework}
 
 \hypersetup{
-pdftitle = {My JuliaCon proceeding},
+pdftitle = {Simulation of fracture and damage with Peridynamics.jl},
 pdfsubject = {JuliaCon 2022 Proceedings},
-pdfauthor = {1st author, 2nd author, 3rd author},
-pdfkeywords = {Julia, Optimization, Game theory, Compiler},
+pdfauthor = {Kai Partmann, Manuel Dienst, Kerstin Weinberg},
+pdfkeywords = {Julia, Peridynamics, Fracture Mechanics, Simulations, Simulation Framework},
 }

### 2024-05-16 paper/paper.tex
Initial state

@@
 
-\begin{abstract}
+\section{Summary}
 
-This is a guide for authors who are preparing papers for JuliaCon using the \LaTeX{} document
-preparation system and the \verb|juliacon|  class file.
+\cite{bezanson2017julia}
 
-\end{abstract}
+\section{Statement of need}
 
-\section{Introduction}
+\section{Acknowledgments}
+The authors gratefully acknowledge the support of the Deutsche Forschungsgemeinschaft (DFG) in the project \mbox{WE~2525/15-1}.
 
-The \LaTeX{} document preparation system is a special version of the
-\TeX; typesetting program where-in a collection of \TeX; commands
-are added to \LaTeX{} to simplify typesetting. Importantly, it allows
-the author to concentrate on the logical structure of the document
-rather than its visual layout.\vskip 6pt
-Moreover, \LaTeX{} provides a consistent and comprehensive document
-preparation interface. There are simple-to-use commands for
-generating a table of contents, lists of figures and/or tables, and indexes.
-\LaTeX{} can automatically number list entries, equations, figures,
-tables, and footnotes, as well as articles, sections, and subsections.
-Using this numbering system, bibliographic citations, page
-references, and cross references to any other numbered entity (e.g.
-article, section, equation, figure, list entry, etc.) become quite simple
-and straightforward. The use of \LaTeX{} document classes allows
-a simple change of class to transform the appearance of your document.\vskip 6pt
-\LaTeX{} is a powerful tool for managing long and complex documents.
-In particular, partial processing enables long documents to
-be produced article by article without losing sequential information.
-The use of document classes allows a simple change of style
-(or style option) to transform the appearance of your document.
-
-\section{The JuliaCon Article Class}
-\label{sec:documentclass}
-%
-The juliacon class file preserves the standard LATEX{} interface such
-that any document that can be produced using the standard LATEX{}
-article class can also be produced with the class file.\vskip 6pt
-It is likely that the make up will change after file submission. For
-this reason, we ask you to ignore details such as slightly long lines,
-page stretching, or figures falling out of synchronization, as these
-details can be dealt with at a later stage.\vskip 6pt
-Use should be made of symbolic references (\verb|\ref| ) in order to
-protect against late changes of order, etc.
-
-\section{USING THE JuliaCon Article CLASS FILE}
-
-If the file \verb|juliacon.cls|  is not already in the appropriate system directory
-for \LaTeX{} files, either arrange for it to be put there or copy
-it to your working directory. The \verb|juliacon|  document class is implemented
-as a complete class, not a document style option. In order to
-use the \verb|juliacon  document class, replace \verb|article|  by \verb|juliacon|  in the
-\verb|\documentclass|  command at the beginning of your document:
-\vskip 6pt
-\begin{centering}
-    \verb|\documentclass{article}|  \end{centering}
-\vskip 6pt
-replace by
-\vskip 6pt
- \verb|\documentclass{juliacon}|  \vskip 6pt
-In general, the following standard document \verb|style|  options should
-{ \itshape not} be used with the {\footnotesize \itshape article} class file:
-\begin{enumerate}
-\item[(1)] \verb|10pt|,  \verb|11pt|,  \verb|12pt|   ? unavailable;
-\item[(2)] \verb|twoside|  (no associated style file) ? \verb|twoside|  is the default;
-\item[(3)] \verb|fleqn|, \verb|leqno|, \verb|titlepage| ? should not be used;
-\end{enumerate}
-
-\section{Additional Document Style Options}
-\label{sec:additional_doc}
-%
-The following additional style option is available with the \verb|juliacon|  class file:
-\vskip 6pt
-Please place any additional command definitions at the very start of
-the \LaTeX{} file, before the \verb|\begin{document}|. For example, user-defined
-\verb|\def|  and \verb|\newcommand|   commands that define macros for
-technical expressions should be placed here. Other author-defined
-macros should be kept to a minimum.
-\vskip 6pt
-Commands that differ from the standard \LaTeX{} interface, or that
-are provided in addition to the standard interface, are explained in
-this guide. This guide is not a substitute for the \LaTeX{} manual itself.
-Authors planning to submit their papers in \LaTeX{} are advised to use
-\verb|juliacon.cls|  as early as possible in the creation of their files.
-
-%
-%
-%
-%
-\begin{table*}[t]
-\tabcolsep22pt
-\tbl{If necessary, the tables can be extended both columns.}{
-\begin{tabular}{|l|l|c|c|}\hline
-Label & \multicolumn{1}{c|}{Description}
-& Number of Users &
-Number of Queries\\\hline
-Test 1 & Training Data &
-\smash{\raise-7pt\hbox{70}} & 104\\
-\cline{1-2}\cline{4-4}
-Test 2 & Testing Data I & & 105\\\hline
-Test 3 & Testing Data II & 30 & 119\\\hline
-& Total & 100 & 328\\\hline
-\end{tabular}}
-\label{tab:symbols}
-\begin{tabnote}
-This is an example of table footnote.
-\end{tabnote}
-\end{table*}
-% \begin{figure*}[t]
-% \centerline{\includegraphics[width=11cm]{juliagraphs.png}}
-% \caption{If necessary, the images can be extended both columns.}
-%   \label{fig:sample_image}
-% \end{figure*}
-
-\section{Additional features}
-\label{sec:additional_faci}
-In addition to all the standard \LaTeX{} design elements, the \verb|juliacon|  class file includes the following features:
-In general, once you have used the additional \verb|juliacon.cls| facilities
-in your document, do not process it with a standard \LaTeX{} class
-file.
-
-\subsection{Titles, Author's Name, and Affiliation}
-\label{subsub:title_auth}
-The title of the article, author's name, and affiliation are used at the
-beginning of the article (for the main title). These can be produced
-using the following code:
-
-\begin{verbatim}
-\title{ This is an example of article title} }
-\author{
-   \large 1st Author \\[-3pt]
-   \normalsize 1st author's affiliation  \\[-3pt]
-    \normalsize 1st line of address \\[-3pt]
-    \normalsize 2nd line of address \\[-3pt]
-    \normalsize	1st author's email address \\[-3pt]
-  \and
-   \large 2nd Author \\[-3pt]
-   \normalsize 2nd author's affiliation  \\[-3pt]
-    \normalsize 1st line of address \\[-3pt]
-    \normalsize 2nd line of address \\[-3pt]
-    \normalsize	2nd author's email address \\[-3pt]
-\and
-   \large 3rd Author \\[-3pt]
-   \normalsize 3rd author's affiliation  \\[-3pt]
-    \normalsize 1st line of address \\[-3pt]
-    \normalsize 2nd line of address \\[-3pt]
-    \normalsize	3rd author's email address \\[-3pt]
-}
-\maketitle
-\end{verbatim}
-
-\subsection{Writing Julia code}
-
-A special environment is already defined for Julia code,
-built on top of \textit{listings} and \textit{jlcode}.
-
-\begin{verbatim}
-\begin{lstlisting}[
-    language = Julia, 
-    numbers=left, 
-    label={lst:exmplg}, 
-    caption={Example Code Block.}
-]
-using Plots
-
-x = -3.0:0.01:3.0
-y = rand(length(x))
-plot(x, y)
-\end{lstlisting}
-\end{verbatim}
-\begin{lstlisting}[
-    language = Julia, 
-    numbers=left, 
-    label={lst:exmplg}, 
-    caption={Example Code Block.}
-]
-using Plots
-
-x = -3.0:0.01:3.0
-y = rand(length(x))
-plot(x, y)
-\end{lstlisting}
-
-\subsection{Abstracts, Key words, term etc...}
-\label{subsub:abs_key_etc}
-
-At the beginning of your article, the title should be generated
-in the usual way using the \verb|\maketitle|  command. For genaral tem and keywords use
-\verb|\terms|,
-\verb|\keywords|  commands respectively. The abstract should be enclosed
-within an abstract environment, All these environment
-can be produced using the following code:
-\begin{verbatim}
-\terms{Experimentation, Human Factors}
-
-\keywords{Face animation, image-based modelling...}
-
-\begin{abstract}
-In this paper, we propose a new method for the
-systematic determination of the model's base of
-time varying delay system. This method based on
-the construction of the classification data related
-to the considered system. The number, the orders,
-the time delay and the parameters of the local
-models are generated automatically without any
-knowledge about the full operating range of the
-process. The parametric identification of the local
-models is realized by a new recursive algorithm for
-on line identification of systems with unknown time
-delay. The proposed algorithm allows simultaneous
-estimation of time delay and parameters of
-discrete-time systems. The effectiveness of
-the new method has been illustrated through
-simulation.
-\end{abstract}
-
-\end{verbatim}
-
-\section{Some guidelines}
-\label{sec:some_guide}
-The following notes may help you achieve the best effects with the
-\verb|juliacon|  class file.
-
-\subsection{Sections}
-\label{subsub:sections}
-\LaTeXe{}  provides four levels of section headings and they are all
-defined in the \verb|juliacon|  class file:
-\begin{itemize}
-\item \verb|\section|
-\item \verb|\subsection|
-\item \verb|\subsubsection|
-\item \verb|\paragraph|
-\end{itemize}
-Section headings are automatically converted to allcaps style.
-\subsection{Lists}
-\label{sec:lists}
-%
-The \verb|juliacon|   class file provides unnumbered lists using the
-\verb|unnumlist|  environment for example,
-
-\begin{unnumlist}
-\item First unnumbered item which has no label and is indented from the
-left margin.
-\item Second unnumbered item.
-\item Third unnumbered item.
-\end{unnumlist}
-The unnumbered list which has no label and is indented from the
-left margin. was produced by:
-\begin{verbatim}
-\begin{unnumlist}
-\item First unnumbered item...
-\item Second unnumbered item...
-\item Third unnumbered item...
-\end{unnumlist}
-\end{verbatim}
-
-The \verb|juliacon|  class file also provides hyphen list using the
-\verb|itemize|  environment for example,
-\begin{itemize}
-\item First unnumbered bulleted item which has no label and is indented
-from the left margin.
-\item Second unnumbered bulleted item.
-\item Third unnumbered bulleted item which has no label and is indented
-from the left margin.
-\end{itemize}
-was produced by:
-\begin{verbatim}
-\begin{itemize}
-\item First item...
-\item Second item...
-\item Third item...
-\end{itemize}
-\end{verbatim}
-
-Numbered list is also provided in acmtog class file using the
-enumerate environment for example,
-\begin{enumerate}
-\item The attenuated and diluted stellar radiation.
-\item Scattered radiation, and
-\item Reradiation from other grains.
-\end{enumerate}
-
-was produced by:
-\begin{verbatim}
-\begin{enumerate}
-\item The attenuated...
-\item Scattered radiation, and...
-\item Reradiation from other grains...
-\end{enumerate}
-\end{verbatim}
-\subsection{Illustrations (or figures)}
-\label{subsub:sec_Illus}
-The \verb|juliacon|  class file will cope with most of the positioning of
-your illustrations and you should not normally use the optional positional
-qualifiers on the \verb|figure|  environment that would override
-these decisions.
-\vskip 6pt
-
-%
-\begin{figure}[t]
-\centerline{\includegraphics[width=4cm]{juliagraphs.png}}
-\caption{This is example of the image in a column.}
-	\label{fig:sample_figure}
-\end{figure}
-
-The figure \ref{fig:sample_figure} is taken from the JuliaGraphs
-organization \footnote{https://github.com/JuliaGraphs}.
-
-Figure captions should be \emph{below} the figure itself, therefore the
-\verb|\caption|  command should appear after the figure or space left for
-an illustration. For example, Figure 1 is produced using the following
-commands:
-
-\begin{verbatim}
-\begin{figure}
-\centerline{\includegraphics[width=20pc]{Graphics.eps}}
-\caption{An example of the testing process for a
-binary tree. The globa null hypothesis is tested
-first at level $\alpha$ (a), and the level of
-individual variables is reached last (d). Note
-that individual hypotheses can be tested at
-level $\alpha/4$ and not $\alpha/8$ as one might
-expect at first.}
-\label{sample-figure_2}
-\end{figure}
-\end{verbatim}
-Figures can be resized using first and second argument of
-\verb|\includegraphics|   command. First argument is used for modifying
-figure height and the second argument is used for modifying
-figure width respectively.
-\vskip 6pt
-Cross-referencing of figures, tables, and numbered, displayed
-equations using the \verb|\label|  and \verb|\ref|   commands is encouraged.
-For example, in referencing Figure 1 above, we used
-\verb|Figure~\ref{sample-figure}|
-
- \subsection{Tables}
-\label{subsub:sec_Tab}
-The \verb|juliacon|   class file will cope with most of the positioning of
-your tables and you should not normally use the optional positional qualifiers on the table environment which would override these
-decisions. Table captions should be at the top.
-\begin{verbatim}
-\begin{table}
-\tbl{Tuning Set and Testing Set}{
-\begin{tabular}{|l|l|c|c|}\hline
-Label & \multicolumn{1}{c|}{Description}
-& Number of Users &
-Number of Queries\\\hline
-Train70 & Training Data &
-\smash{\raise-7pt\hbox{70}} & 104\\
-\cline{1-2}\cline{4-4}
-Test70 & Testing Data I & & 105\\\hline
-Test30 & Testing Data II & 30 & 119\\\hline
-& Total & 100 & 328\\\hline
-\end{tabular}}
-\end{table}
-\end{verbatim}
-
-\begin{table}
-\tbl{Tuning Set and Testing Set}{
-\begin{tabular}{|l|l|c|c|}\hline
-Label & \multicolumn{1}{c|}{Description}
-& Number of Users &
-Number of Queries\\\hline
-Test 1 & Training Data &
-\smash{\raise-7pt\hbox{70}} & 104\\
-\cline{1-2}\cline{4-4}
-Test 2 & Testing Data I & & 105\\\hline
-Test 3 & Testing Data II & 30 & 119\\\hline
-& Total & 100 & 328\\\hline
-\end{tabular}}
-\end{table}
-\subsection{Landscaping Pages}
-\label{subsub:landscaping_pages}
-If a table is too wide to fit the standard measure, it may be turned,
-with its caption, to 90 degrees. Landscape tables cannot be produced
-directly using the \verb|juliacon|   class file because \TeX{} itself cannot
-turn the page, and not all device drivers provide such a facility.
-The following procedure can be used to produce such pages.
-\vskip 6pt
-Use the package \verb|rotating|   in your document and change the coding
-from
-\begin{verbatim}
-\begin{table}...\end{table}
-to
-\begin{sidewaystable}...\end{sidewaystable}
-and for figures
-\begin{figure}...\end{figure}
-to
-\begin{sidewaysfigure}...\end{sidewaysfigure}
-\end{verbatim}
-
-environments in your document to turn your table on the appropriate
-page of your document. For instance, the following code prints
-a page with the running head, a message half way down and the
-table number towards the bottom.
-\begin{verbatim}
-\begin{sidewaystable}
-\tbl{Landscape table caption to go here.}{...}
-\label{landtab}
-\end{sidewaystable}
-\end{verbatim}
-
-\subsection{Double Column Figure and Tables}
-\label{subsub:double_fig_tab}
-For generating the output of figures and tables in double column
-we can use the following coding:
-
-\begin{enumerate}
-\item For Figures:
-\begin{verbatim}
-\begin{figure*}...\end{figure*}
-\end{verbatim}
-\item For landscape figures:
-\begin{verbatim}
-\begin{sidewaysfigure*}...\end{sidewaysfigure*}
-\end{verbatim}
-\item For Tables:
-\begin{verbatim}
-\begin{table*}...\end{table*}
-\end{verbatim}
-\item For landscape tables:
-\begin{verbatim}
-\begin{sidewaystable*}...\end{sidewaystable*}
-\end{verbatim}
-\end{enumerate}
-
-\subsection{Typesetting Mathematics}
-\label{subsub:type_math}
-The \verb|juliacon| class file will set displayed mathematics with center to
-the column width, provided that you use the \LaTeXe{} standard of
-open and closed square brackets as delimiters.
-The equation
-\[
-\sum_{i=1}^p \lambda_i = (S)
-\]
-
-was typeset using the acmtog class file with the commands
-
-\begin{verbatim}
-\[
-\sum_{i=1}^p \lambda_i = (S)
-\]
-\end{verbatim}
-
-For display equations, cross-referencing is encouraged. For example,
-\begin{verbatim}
-\begin{equation}
-(n-1)^{-1} \sum^n_{i=1} (X_i - \overline{X})^2.
-\label{eq:samplevar}
-\end{equation}
-Equation~(\ref{eq:samplevar}) gives the formula for
-sample variance.
-\end{verbatim}
-The following output is generated with the above coding:
-\begin{equation}
-(n-1)^{-1} \sum^n_{i=1} (X_i - \overline{X})^2.
-\label{eq:samplevar}
-\end{equation}
-Equation~(\ref{eq:samplevar}) gives the formula for
-sample variance.
-
-\subsection{Enunciations}
-\label{subsub:enunciation}
-The \verb|juliacon|   class file generates the enunciations with the help of
-the following commands:
-\begin{verbatim}
-\begin{theorem}...\end{theorem}
-\begin{strategy}...\end{strategy}
-\begin{property}...\end{property}
-\begin{proposition}...\end{proposition}
-\begin{lemma}...\end{lemma}
-\begin{example}...\end{example}
-\begin{proof}...\end{proof}
-\begin{definition}...\end{definition}
-\begin{algorithm}...\end{algorithm}
-\begin{remark}...\end{remark}
-\end{verbatim}
-The above-mentioned coding can also include optional arguments
-such as
-\begin{verbatim}
-\begin{theorem}[...]. Example for theorem:
-\begin{theorem}[Generalized Poincare Conjecture]
-Four score and seven ... created equal.
-\end{theorem}
-\end{verbatim}
-
-\begin{theorem}[Generalized Poincare Conjecture]
-Four score and seven years ago our fathers brought forth,
-upon this continent, a new nation, conceived in Liberty,
- and dedicated to the proposition that all men are
-created equal.
-\end{theorem}
-
-\subsection{Extract}
-\label{subsub:extract}
-Extract environment should be coded within
-\begin{verbatim}
-\begin{extract}..\end{extract}
-\end{verbatim}
-
-\subsection{Balancing column at last page}
-\label{subsub:Balance}
-For balancing the both column length at last page use :
-\begin{verbatim}
-\vadjust{\vfill\pagebreak}
-\end{verbatim}
+The authors gratefully acknowledge the support and the supercomputing resources of the Paderborn Center for Parallel Computing (https://pc2.uni-paderborn.de) and the University of Siegen (https://cluster.uni-siegen.de) used to conduct the research reported in this paper.
 
 %\vadjust{\vfill\pagebreak}
-
-at appropriate place in your \TeX{} file or in bibliography file.
-
-\section{Handling references}
-\label{subsub:references}
-References are most easily (and correctly) generated using the
-BIBTEX, which is easily invoked via
-\begin{verbatim}
-\bibliographystyle{juliacon}
-\bibliography{ref}
-\end{verbatim}
-When submitting the document source (.tex) file to external
-parties, the ref.bib file should be sent with it.
-\cite{bezanson2017julia}
 

### 2024-05-16 paper/paper.tex
Add comments with infos from JOSS docs
first draft of begin of summary

@@
 \setcounter{page}{1}
+
+%%---- definition of custom commands
+\newcommand{\abs}[1]{\left|#1\right|}
+\newcommand{\vb}{\boldsymbol}
+%%----
 
@@
 \section{Summary}
+
+\texttt{Peridynamics.jl} is an open source implementation of the nonlocal continuum mechanics formulation by Silling (ref?).
+In peridynamics, a body is described by material points and, based on interactions between them, internal force densities are calculated. 
+The equation of motion reads
+\begin{equation}
+    \varrho \, \vb{\ddot{u}}(\vb{X},t) = \vb{b}^{\mathrm{int}}(\vb{X},t) + \vb{b}^{\mathrm{ext}}(\vb{X},t) \qquad \forall \vb{X} \in \mathcal{B}_0, \; t \geq 0 \; ,
+\end{equation} 
+with the mass density $\varrho$, the point acceleration vector $\vb{\ddot{u}}$, and the point force density vectors $\vb{b}^{\mathrm{int}}$ and $\vb{b}^{\mathrm{ext}}$. 
+In the original bond-based formulation (BB), the internal force density is calculated by
+\begin{equation}
+    \vb{b}^{\mathrm{int}}(\vb{X},t) = \int_\mathcal{H} \vb{f} \; \mathrm{d}V' \; ,
+\end{equation}
+with the \emph{pairwise force function} $\vb{f}$, which is evaluated for each material point $\vb{X}^i$ and depends on the deformation of the bonds to each point in its neighborhood $\mathcal{H}$.
+These point families contain each point within a distance $\delta$, also called horizon.
+
+To overcome the restrictions of the BB formulation with only one determinable material parameter, the state-based formulation was established.
+Here not only the bonds to neighboring material points, but also the states of neighboring points influence the internal force density $\vb{b}^{\mathrm{int}}$ of each material point.
+The equation reads
+\begin{equation}
+    \vb{b}^{\mathrm{int}} (\vb{X},t) = \int_\mathcal{H} \vb{t} - \vb{t}' \; \mathrm{d}V' \; ,
+\end{equation}
+with the force vector states $\vb{t}=\vb{t}(\vb{\Delta X}, t)$ and $\vb{t}'=\vb{t}(-\vb{\Delta X}, t)$.
+
+The \texttt{Peridynamics.jl} package enables users to perform peridynamic simulations
 

### 2024-05-16 paper/paper.tex
Added some images and references

@@
 \section{Summary}
+% from the JOSS docs:
+% The paper should include a summary describing the high-level functionality and purpose of the software for a diverse, non-specialist audience.
 
-\texttt{Peridynamics.jl} is an open source implementation of the nonlocal continuum mechanics formulation by Silling (ref?).
+%--- What is Peridynamics? ---%
+\texttt{Peridynamics.jl} is an open source Julia \cite{bezanson2017julia} implementation of the nonlocal continuum mechanics formulation by Silling (ref?).
 In peridynamics, a body is described by material points and, based on interactions between them, internal force densities are calculated. 
@@
 
-The \texttt{Peridynamics.jl} package enables users to perform peridynamic simulations
+%--- What is the high-level functionality of Peridynamics.jl? ---%
+The \texttt{Peridynamics.jl} package enables users to perform peridynamic simulations.
 
-\cite{bezanson2017julia}
+\begin{figure}
+\centerline{\includegraphics[width=0.8\linewidth]{logo.png}}
+\caption{High-velocity contact simulation of three spheres crashing into a rectangular panel; logo of Peridynamics.jl}
+\label{fig:logo}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=0.8\linewidth]{tensile_test.png}}
+\caption{Fracture simulation of tensile tension test with a crack propagating in the middle of the specimen}
+\label{fig:tensiletest}
+\end{figure}
 
 \section{Statement of need}
+% from the JOSS docs:
+% The paper should include a Statement of need section that clearly illustrates the research purpose of the software and places it in the context of related work.
+
+%--- Place the package in the context of related work
+The package was already used in numerous publications, e.g. \cite{Friebertshaeuser2022PAMM,Friebertshaeuser2022AIMS,Partmann2023IJF,Partmann2024AAM,Partmann2024PAMM,Tornquist2022PAMM}.
+
+%--- What is the research purpose of Peridynamics.jl?
 
@@
 
-The authors gratefully acknowledge the support and the supercomputing resources of the Paderborn Center for Parallel Computing (https://pc2.uni-paderborn.de) and the University of Siegen (https://cluster.uni-siegen.de) used to conduct the research reported in this paper.
+The authors gratefully acknowledge the support and the supercomputing resources of the Paderborn Center for Parallel Computing (https://pc2.uni-paderborn.de).
 
-%\vadjust{\vfill\pagebreak}
+% \vadjust{\vfill\pagebreak}
 

### 2024-05-17 paper/paper.tex
Added Summary section

--- 2024-05-16 paper/paper.tex
@@
 \section{Summary}
+% from the JOSS docs:
+% The paper should include a summary describing the high-level functionality and purpose of the software for a diverse, non-specialist audience.
 
-\cite{bezanson2017julia}
+%=== What is Peridynamics? ===%
+\begin{figure}
+\centerline{\includegraphics[width=0.8\linewidth]{logo.png}}
+\caption{High-velocity contact simulation of three spheres crashing into a rectangular panel; logo of Peridynamics.jl}
+\label{fig:logo}
+\end{figure}
+
+%- General peridynamics context
+Peridynamics is a nonlocal continuum mechanics formulation, which was invented by Silling \cite{Silling2000}.
+It has gained increased popularity as an approach for modeling fracture.
+The material behavior is described by integro-differential equations that are also fulfilled for discontinuities, making it very capable of modeling crack propagation and fragmentation with large displacements.
+Much peridynamics research has been done in recent years, summarized in various review papers and books \cite{Diehl2019,Javili2019Review,Madenci2014}.
+
+%- Peridynamics short introduction
+Typically, in peridynamics the continuum is discretized by material points.
+Points interact only with other points inside of their specified \emph{neighborhood} or \emph{point family}~$\mathcal{H}$, which is defined as the set of points inside a sphere with the radius $\delta$, also named the \emph{horizon}.
+The interaction of the point $\vb{X}$ with its neighbor $\vb{X}'$ is called \emph{bond} and defined as
+\begin{equation}
+\vb{\Delta X} = \vb{X}' - \vb{X} \; .
+\end{equation}
+The equation of motion reads
+\begin{equation}
+\varrho \, \vb{\ddot{u}}(\vb{X},t) = \vb{b}^{\mathrm{int}}(\vb{X},t) + \vb{b}^{\mathrm{ext}}(\vb{X},t) \; ,
+\end{equation} 
+with the mass density $\varrho$, the point acceleration vector $\vb{\ddot{u}}$, and the point force density vectors $\vb{b}^{\mathrm{int}}$ and $\vb{b}^{\mathrm{ext}}$.
+Various formulations of peridynamics exist for the calculation of the internal force density $\vb{b}^{\mathrm{int}}$, and all of them are based on the nonlocal interactions between material points.
+
+%- Some information on peridynamic material models
+In the first original bond-based formulation (BB) of peridynamics, the internal force density is calculated by
+\begin{equation}
+\vb{b}^{\mathrm{int}}(\vb{X},t) = \int_\mathcal{H} \vb{f}(\vb{\Delta X}, t) \; \mathrm{d}V' \; ,
+\end{equation}
+with the \emph{pairwise force function} $\vb{f}$.
+The BB model has intrinsic limitations due to a restriction on the Poisson's ratio \cite{Silling2007,Trageser2020}.
+To overcome these restrictions, state-based peridynamics was established.
+In state-based Peridynamics, the deformation states of neighboring points also influence the internal force density \cite{Silling2007}.
+The general internal force density for state-based peridynamics is defined as
+\begin{equation}
+\vb{b}^{\mathrm{int}} (\vb{X},t) = \int_\mathcal{H} \vb{t} - \vb{t}' \; \mathrm{d}V' \; ,
+\end{equation}
+with the force vector states $\vb{t}=\vb{t}(\vb{\Delta X}, t)$ and $\vb{t}'=\vb{t}(-\vb{\Delta X}, t)$.
+State-based peridynamics can be divided in two subcategories.
+In ordinary state-based peridynamics, the force vector state $\vb{t}$ is always parallel to the deformed bond.
+Non-ordinary state-based formulations do not have this restriction.
+Within the local continuum consistent correspondence formulation of non-ordinary state-based peridynamics, an elastic model from the classical material theory can be used to calculate the internal force density.
+Other formulations of peridynamics exist, such as continuum-kinematics-inspired peridynamics \cite{Javili2019}.
+
+\begin{figure}
+\centerline{\includegraphics[width=0.9\linewidth]{tensile_test.png}}
+\caption{Fracture simulation of tensile tension test with a crack propagating in the middle of the specimen}
+\label{fig:tensiletest}
+\end{figure}
+
+%=== What is the high-level functionality of Peridynamics.jl? ===%
+\texttt{Peridynamics.jl} is an open source Julia \cite{Bezanson2017julia} implementation of peridynamics.
+It can be used to conduct simulations with applications such as crack propagation due to external loading conditions (see Fig.~\ref{fig:tensiletest}), or multi-body contact simulations (see Fig.~\ref{fig:logo}).
+Users can specify arbitrary geometries as a point cloud to use as a spatial discretization for a simulation.
+It is also possible to import meshes generated with ABAQUS and convert them into point clouds.
+Multiple peridynamic material models are implemented and can be used in dynamic simulations using Velocity Verlet integration or in quasi-static simulations with an adaptive dynamic relaxation algorithm \cite{Kilic2010}.
+
+%=== What is the purpose of Peridynamics.jl? ===%
+The primary purpose of the package is to provide a framework for peridynamic simulations for a broad user base.
+Peridynamics simulations can be conducted with custom geometry and setup with just a few lines of code.
+Due to Julia's multiple dispatch functionality, custom material models can be defined to extend the package.
+Therefore, researchers can use the package to develop new peridynamic material models, simplifying their workflow by utilizing the Julia ecosystem.
 
 \section{Statement of need}
+% from the JOSS docs:
+% The paper should include a Statement of need section that clearly illustrates the research purpose of the software and places it in the context of related work.
+
+%=== Place the package in the context of related work ===%
+The package was already used in numerous publications \cite{Friebertshaeuser2022PAMM,Friebertshaeuser2022AIMS,Partmann2023IJF,Partmann2024AAM,Partmann2024PAMM,Tornquist2022PAMM}.
+
+%=== What is the research purpose of Peridynamics.jl? ===%
+
+\section{Perspectives}
 

### 2024-05-17 paper/paper.tex
Minor changes
Update paper.tex

@@
 %- General peridynamics context
-Peridynamics is a nonlocal continuum mechanics formulation, which was invented by Silling \cite{Silling2000}.
+Peridynamics is a nonlocal continuum mechanics formulation, which was introduced by Silling \cite{Silling2000}.
 It has gained increased popularity as an approach for modeling fracture.
@@
 The primary purpose of the package is to provide a framework for peridynamic simulations for a broad user base.
-Peridynamics simulations can be conducted with custom geometry and setup with just a few lines of code.
+A user-friendly interface makes it possible to define geometries and boundary conditions with just a few lines of code.
 Due to Julia's multiple dispatch functionality, custom material models can be defined to extend the package.
@@
 
+%=== What is the research purpose of Peridynamics.jl? ===%
+
 %=== Place the package in the context of related work ===%
 The package was already used in numerous publications \cite{Friebertshaeuser2022PAMM,Friebertshaeuser2022AIMS,Partmann2023IJF,Partmann2024AAM,Partmann2024PAMM,Tornquist2022PAMM}.
-
-%=== What is the research purpose of Peridynamics.jl? ===%
 

### 2024-05-17 paper/paper.tex
Added Sec.2 and Sec.3

@@
 %- General peridynamics context
-Peridynamics is a nonlocal continuum mechanics formulation, which was introduced by Silling \cite{Silling2000}.
+Peridynamics is a nonlocal continuum mechanics formulation, which was invented by Silling \cite{Silling2000}.
 It has gained increased popularity as an approach for modeling fracture.
-The material behavior is described by integro-differential equations that are also fulfilled for discontinuities, making it very capable of modeling crack propagation and fragmentation with large displacements.
+The deformation of the solid is described by integro-differential equations that are also fulfilled for discontinuities, making it very capable of modeling crack propagation and fragmentation with large displacements.
 Much peridynamics research has been done in recent years, summarized in various review papers and books \cite{Diehl2019,Javili2019Review,Madenci2014}.
@@
 with the mass density $\varrho$, the point acceleration vector $\vb{\ddot{u}}$, and the point force density vectors $\vb{b}^{\mathrm{int}}$ and $\vb{b}^{\mathrm{ext}}$.
-Various formulations of peridynamics exist for the calculation of the internal force density $\vb{b}^{\mathrm{int}}$, and all of them are based on the nonlocal interactions between material points.
+Various material formulations of peridynamics exist for the calculation of the internal force density $\vb{b}^{\mathrm{int}}$, and all of them are based on the nonlocal interactions between material points.
 
 %- Some information on peridynamic material models
-In the first original bond-based formulation (BB) of peridynamics, the internal force density is calculated by
-\begin{equation}
-\vb{b}^{\mathrm{int}}(\vb{X},t) = \int_\mathcal{H} \vb{f}(\vb{\Delta X}, t) \; \mathrm{d}V' \; ,
-\end{equation}
-with the \emph{pairwise force function} $\vb{f}$.
-The BB model has intrinsic limitations due to a restriction on the Poisson's ratio \cite{Silling2007,Trageser2020}.
-To overcome these restrictions, state-based peridynamics was established.
-In state-based Peridynamics, the deformation states of neighboring points also influence the internal force density \cite{Silling2007}.
 The general internal force density for state-based peridynamics is defined as
@@
 \end{equation}
-with the force vector states $\vb{t}=\vb{t}(\vb{\Delta X}, t)$ and $\vb{t}'=\vb{t}(-\vb{\Delta X}, t)$.
-State-based peridynamics can be divided in two subcategories.
-In ordinary state-based peridynamics, the force vector state $\vb{t}$ is always parallel to the deformed bond.
-Non-ordinary state-based formulations do not have this restriction.
-Within the local continuum consistent correspondence formulation of non-ordinary state-based peridynamics, an elastic model from the classical material theory can be used to calculate the internal force density.
-Other formulations of peridynamics exist, such as continuum-kinematics-inspired peridynamics \cite{Javili2019}.
+with the \emph{force vector states} $\vb{t}=\vb{t}(\vb{\Delta X}, t)$ and $\vb{t}'=\vb{t}(-\vb{\Delta X}, t)$.
+In the first original bond-based formulation of peridynamics, the force vector states $\vb{t}$ and  $\vb{t}'$ have the same value and opposite direction.
+This implies intrinsic limitation to only one material parameter and in consequence to restrictions on the Poisson's ratio \cite{Silling2007,Trageser2020}.
+To overcome these restrictions, a state-based peridynamics was established.
+In the ordinary state-based peridynamics, the deformation states of neighboring points also influence the internal force density \cite{Silling2007}.
+This leads to force vector states which are still collinear but not of same value anymore.
+
+Further developments are summarized as non-ordinary state-based peridynamics.
+A recent development in this regard is continuum-kinematics-inspired peridynamics \cite{Javili2019}.
+Another peridynamic formulation is the local continuum consistent correspondence formulation of non-ordinary state-based peridynamics, where an elastic model from the classical local material theory can be used to calculate the internal force density.
 
 \begin{figure}
-\centerline{\includegraphics[width=0.9\linewidth]{tensile_test.png}}
+\centerline{\includegraphics[width=0.8\linewidth]{tensile_test.png}}
 \caption{Fracture simulation of tensile tension test with a crack propagating in the middle of the specimen}
@@
 
-%=== What is the research purpose of Peridynamics.jl? ===%
+%=== Place the package in the context of related work ===%
+Various peridynamics software projects exist, including \texttt{PeriPy} \cite{PeriPy2021}, \texttt{NLMech} \cite{Jha2021}, \texttt{Peridigm} \cite{Peridigm2024}, and \texttt{PeriHub} \cite{Willberg2023}.
+\texttt{Peridigm} stands out as a mature package capable of large-scale peridynamics simulations that also 
+includes several material models and features.
+However, the installation process and integrating custom models is notably complex.
 
-%=== Place the package in the context of related work ===%
-The package was already used in numerous publications \cite{Friebertshaeuser2022PAMM,Friebertshaeuser2022AIMS,Partmann2023IJF,Partmann2024AAM,Partmann2024PAMM,Tornquist2022PAMM}.
+The initial intention in developing the package was to simplify the process of implementing new material models within the Julia ecosystem.
+In contrast to \texttt{Peridigm}, installing and extending \texttt{Peridynamics.jl} is straightforward, as it benefits from the Julia ecosystem.
+\texttt{Peridynamics.jl} was already used in numerous publications \cite{Friebertshaeuser2022PAMM,Friebertshaeuser2022AIMS,Partmann2023IJF,Partmann2024AAM,Partmann2024PAMM,Tornquist2022PAMM}, which shows the practical usability of the package.
 
 \section{Perspectives}
+In version \texttt{0.2.0}, a multithreading approach is employed.
+An extension to a hybrid approach utilizing MPI and multithreading is currently underway and is planned for version \texttt{0.3.0}.
+The internals have been thoroughly reworked to incorporate a parallel data structure, resulting in significantly faster simulations that surpass the performance of \texttt{Peridigm}.
+The planned changes include new material models and a simplified API with streamlined internal structures.
 
 \section{Acknowledgments}
-The authors gratefully acknowledge the support of the Deutsche Forschungsgemeinschaft (DFG) in the project \mbox{WE~2525/15-1}.
+The authors gratefully acknowledge the support of the Deutsche Forschungsgemeinschaft (DFG) in the project \mbox{WE~2525/15-1} and \mbox{WE~2525/15-2}.
 

### 2024-09-03 paper/paper.tex
Increase legend of Fig. 2
Updated the perspectives section

@@
 \begin{figure}
-\centerline{\includegraphics[width=0.8\linewidth]{tensile_test.png}}
+\centerline{\includegraphics[width=0.9\linewidth]{tensile_test.png}}
 \caption{Fracture simulation of tensile tension test with a crack propagating in the middle of the specimen}
@@
 \section{Perspectives}
-In version \texttt{0.2.0}, a multithreading approach is employed.
-An extension to a hybrid approach utilizing MPI and multithreading is currently underway and is planned for version \texttt{0.3.0}.
-The internals have been thoroughly reworked to incorporate a parallel data structure, resulting in significantly faster simulations that surpass the performance of \texttt{Peridigm}.
-The planned changes include new material models and a simplified API with streamlined internal structures.
+In version \texttt{v0.2.0}, a multithreading approach is employed.
+An extension to a hybrid approach with MPI or multithreading is made in version \texttt{v0.3.0}.
+The internals have been thoroughly reworked to incorporate a data structure that can be used for parallel simulations with either MPI or multithreading.
+These changes also include new material models and a simplified API with streamlined internal structures.
+For future versions it is planned to add improved material models and to utilize \texttt{DifferentialEquations.jl} for the time integration.
 

### 2024-09-03 paper/paper.tex
Update the statement of need section to clarify the audience of the package

@@
 
-The initial intention in developing the package was to simplify the process of implementing new material models within the Julia ecosystem.
-In contrast to \texttt{Peridigm}, installing and extending \texttt{Peridynamics.jl} is straightforward, as it benefits from the Julia ecosystem.
+Installing and extending \texttt{Peridynamics.jl} is straightforward, as it benefits from the Julia ecosystem.
+Due to its extendability via multiple-dispatch, the package is attractive to researchers developing new peridynamic models.
 \texttt{Peridynamics.jl} was already used in numerous publications \cite{Friebertshaeuser2022PAMM,Friebertshaeuser2022AIMS,Partmann2023IJF,Partmann2024AAM,Partmann2024PAMM,Tornquist2022PAMM}, which shows the practical usability of the package.
+
+Furthermore, practitioners interested in high-performance computing can also use the default methods of the package for exciting simulations.
+The package is used for teaching and was already used by several students for their final thesis.
 

### 2024-09-03 paper/paper.tex
Minor shortifications

@@
 In the first original bond-based formulation of peridynamics, the force vector states $\vb{t}$ and  $\vb{t}'$ have the same value and opposite direction.
-This implies intrinsic limitation to only one material parameter and in consequence to restrictions on the Poisson's ratio \cite{Silling2007,Trageser2020}.
+This implies intrinsic limitation to only one material parameter and in consequence to restrictions on the Poisson's ratio \cite{Silling2007}.
 To overcome these restrictions, a state-based peridynamics was established.
@@
 The internals have been thoroughly reworked to incorporate a data structure that can be used for parallel simulations with either MPI or multithreading.
-These changes also include new material models and a simplified API with streamlined internal structures.
+These changes also include new material models and a simplified API.
 For future versions it is planned to add improved material models and to utilize \texttt{DifferentialEquations.jl} for the time integration.

### 2024-09-05 src/discretization/point_generators.jl
Correct formatting of function uniform_cylinder
Co-authored-by: Kai Partmann <68582683+kaipartmann@users.noreply.github.com>

@@ -167,22 +167,23 @@ julia> volume
  8
 ```
 """
-function uniform_cylinder(diameter::Real, height::Real, ΔX0::Real; center_position=(0, 0, 0))
-radius = diameter / 2
-center_x, center_y, center_z = center_position
-_gridxy = range(- radius + ΔX0 / 2, radius - ΔX0 / 2; step=ΔX0)
-gridxy = _gridxy .- sum(_gridxy) / length(_gridxy)
-_gridz = range((-height + ΔX0) / 2, (height - ΔX0) / 2; step=ΔX0)
-gridz = _gridz .- sum(_gridz) / length(_gridz)
-__position = vec(collect(Iterators.product(gridxy, gridxy, gridz)))
-_position = reinterpret(reshape, eltype(eltype(__position)), __position)
-cylinder_points = find_points(p -> √(p[1]^2 + p[2]^2) ≤ radius, _position)
-position = _position[:, cylinder_points]
-volume = fill(ΔX0^3, size(position, 2))
-isapprox(center_x, 0; atol=eps()) || (position[1, :] .+= center_x)
-isapprox(center_y, 0; atol=eps()) || (position[2, :] .+= center_y)
-isapprox(center_z, 0; atol=eps()) || (position[3, :] .+= center_z)
-return position, volume
+function uniform_cylinder(diameter::Real, height::Real, ΔX0::Real;
+                          center_position=(0, 0, 0))
+    radius = diameter / 2
+    center_x, center_y, center_z = center_position
+    _gridxy = range(-radius + ΔX0 / 2, radius - ΔX0 / 2; step=ΔX0)
+    gridxy = _gridxy .- sum(_gridxy) / length(_gridxy)
+    _gridz = range((-height + ΔX0) / 2, (height - ΔX0) / 2; step=ΔX0)
+    gridz = _gridz .- sum(_gridz) / length(_gridz)
+    __position = vec(collect(Iterators.product(gridxy, gridxy, gridz)))
+    _position = reinterpret(reshape, eltype(eltype(__position)), __position)
+    cylinder_points = find_points(p -> √(p[1]^2 + p[2]^2) ≤ radius, _position)
+    position = _position[:, cylinder_points]
+    volume = fill(ΔX0^3, size(position, 2))
+    isapprox(center_x, 0; atol=eps()) || (position[1, :] .+= center_x)
+    isapprox(center_y, 0; atol=eps()) || (position[2, :] .+= center_y)
[…]

### 2024-09-05 src/discretization/point_generators.jl
Added reference to `TrixiParticles.jl` to docstring of round_sphere
Co-authored-by: Kai Partmann <68582683+kaipartmann@users.noreply.github.com>

@@ -193,7 +193,8 @@ end
     round_sphere(diameter, ΔX0; kwargs...)
 
 Creates a grid of points distributed in a smooth sphere without edges on the surface
-with a specific `diameter` and the point spacing `ΔX0`.
+with a specific `diameter` and the point spacing `ΔX0`. Internally, some parts of 
+`TrixiParticles.jl` were copied and adapted for this function.
 
 # Arguments
 - `diameter::Real`: Diameter of the sphere.

### 2024-09-05 src/Peridynamics.jl
exported new point generator functions and adapted tests

@@ -17,7 +17,7 @@ export NoCorrection, EnergySurfaceCorrection
 # Discretization
 export Body, point_set!, point_sets, failure_permit!, material!, velocity_bc!, velocity_ic!,
        forcedensity_bc!, precrack!, MultibodySetup, contact!, uniform_box, uniform_sphere,
-       n_points
+       uniform_cylinder, round_sphere, round_cylinder, n_points
 
 # Running simulations
 export VelocityVerlet, DynamicRelaxation, Job, submit

### 2024-10-08 paper/paper.tex
Minor typo fixes

@@
 In the first original bond-based formulation of peridynamics, the force vector states $\vb{t}$ and  $\vb{t}'$ have the same value and opposite direction.
-This implies intrinsic limitation to only one material parameter and in consequence to restrictions on the Poisson's ratio \cite{Silling2007}.
+In bond-based peridynamics, this implies an intrinsic limitation to only one material parameter and, consequently, restrictions on the Poisson's ratio  \cite{Silling2007}.
 To overcome these restrictions, a state-based peridynamics was established.

### 2024-10-09 src/Peridynamics.jl
Renaming

@@ -74,7 +74,7 @@ include("auxiliary/mpi.jl")
 
 include("physics/boundary_conditions.jl")
 include("physics/initial_conditions.jl")
-include("physics/material_parameters.jl")
+include("physics/elasticity.jl")
 include("physics/fracture.jl")
 include("physics/short_range_force_contact.jl")
 
@@ -94,7 +94,7 @@ include("core/job.jl")
 include("core/submit.jl")
 include("core/parameter_handler.jl")
 include("core/systems.jl")
-include("core/materials.jl")
+include("core/parameters.jl")
 include("core/storages.jl")
 include("core/time_solvers.jl")
 include("core/halo_exchange.jl")

### 2024-10-09 src/Peridynamics.jl
Update filename

@@ -94,7 +94,7 @@ include("core/job.jl")
 include("core/submit.jl")
 include("core/parameter_handler.jl")
 include("core/systems.jl")
-include("core/parameters.jl")
+include("core/material_parameters.jl")
 include("core/storages.jl")
 include("core/time_solvers.jl")
 include("core/halo_exchange.jl")

### 2024-10-09 src/Peridynamics.jl
Renaming

@@ -74,7 +74,7 @@ include("auxiliary/mpi.jl")
 
 include("physics/boundary_conditions.jl")
 include("physics/initial_conditions.jl")
-include("physics/elasticity.jl")
+include("physics/material_parameters.jl")
 include("physics/fracture.jl")
 include("physics/short_range_force_contact.jl")
 
@@ -94,7 +94,7 @@ include("core/job.jl")
 include("core/submit.jl")
 include("core/parameter_handler.jl")
 include("core/systems.jl")
-include("core/material_parameters.jl")
+include("core/point_parameters.jl")
 include("core/storages.jl")
 include("core/time_solvers.jl")
 include("core/halo_exchange.jl")

### 2024-10-09 src/core/point_parameters.jl
Draft that precompiles

@@ -10,13 +10,126 @@ function get_point_params(mat::AbstractMaterial, ::Dict{Symbol,Any})
     throw(MethodError(get_point_params, mat))
 end
 
-macro params(material, params)
+function extract_parameters(mat::AbstractMaterial,
+                            custom_params::Vector{Tuple{Symbol,DataType}},
+                            p::Dict{Symbol,Any})
+    required_params = extract_required_parameters(mat, p)
+    params = (; required_params...)
+    for (name, type) in custom_params
+        value = parse_parameter(mat, name, type, p)
+        if isnothing(value)
+            value = calc_parameter(mat, Val(name), required_params)
+        end
+        check_parameter(mat, Val(name), value)
+        params = (; params..., name = value)
+    end
+    return params
+end
+
+function extract_required_parameters(::AbstractMaterial, p::Dict{Symbol,Any})
+    params = (; get_horizon(p)..., get_density(p)..., get_elastic_params(p)...)
+    params = (; params..., get_frac_params(p, params)...)
+    return params
+end
+
+function parse_parameter(::M, keyword::Symbol, ::Type{T}, p::Dict{Symbol,Any}) where {M,T}
+    haskey(p, keyword) || return nothing
+    value::T = convert(T, p[keyword])
+    return value
+end
+
+function calc_parameter(::AbstractMaterial, ::Val{P}, elparams) where {P}
+    msg = "point parameter `$P` is not specified and has no calculation method!\n"
+    return throw(ArgumentError(msg))
+end
+
+function check_parameter(::AbstractMaterial, ::Val{P}, value) where {P}
+    return nothing
+end
+
+function required_point_parameters(::Type{Material}) where {Material}
+    required_params = (:(δ::Float64), # horizon
+                       :(rho::Float64), # density
+                       :(E::Float64), # Young's modulus
+                       :(nu::Float64), # Poisson's ratio
+                       :(G::Float64), # shear modulus
+                       :(K::Float64), # bulk modulus
+                       :(λ::Float64), # Lamé's first parameter
+                       :(μ::Float64), # Lamé's second parameter
+                       :(Gc::Float64), # fracture energy
+                       :(εc::Float64))
+    return required_params
+end
+
+function required_point_parameter_names(::Type{Material}) where {Material}
+    required_params = required_point_parameters(Material)
+    param_names = Tuple(extract_parameter_name(field) for field in required_params)
+    return param_names
+end
+
[…]

### 2024-10-09 src/physics/bond_based.jl

@@ -62,24 +62,17 @@ struct BBMaterial{Correction} <: AbstractBondSystemMaterial{Correction} end
 
 BBMaterial() = BBMaterial{NoCorrection}()
 
-struct BBPointParameters <: AbstractPointParameters
-    δ::Float64
-    rho::Float64
-    E::Float64
-    nu::Float64
-    G::Float64
-    K::Float64
-    λ::Float64
-    μ::Float64
-    Gc::Float64
-    εc::Float64
+@params BBMaterial struct BBPointParameters <: AbstractPointParameters
+    @required_params
     bc::Float64
 end
 
-function BBPointParameters(::BBMaterial, p::Dict{Symbol,Any})
-    δ = get_horizon(p)
-    rho = get_density(p)
-    if haskey(p, :nu)
+function calc_parameter(::BBMaterial, ::Val{:bc}, params::NamedTuple)
+    return 18 * params.K / (π * params.δ^4)
+end
+
+function extract_required_parameters(::BBMaterial, p::Dict{Symbol,Any})
+    if haskey(p, :nu) #&& !isapprox(float(p[:nu]), 0.25)
         msg = "keyword `nu` is not allowed for BBMaterial!\n"
         msg *= "Bond-based peridynamics has a limitation on the possion ratio.\n"
         msg *= "Therefore, when using BBMaterial, `nu` is hardcoded as 1/4.\n"
@@ -87,13 +80,43 @@ function BBPointParameters(::BBMaterial, p::Dict{Symbol,Any})
     else
         p[:nu] = 0.25
     end
-    E, nu, G, K, λ, μ = get_elastic_params(p)
-    Gc, εc = get_frac_params(p, δ, K)
-    bc = 18 * K / (π * δ^4) # bond constant
-    return BBPointParameters(δ, rho, E, nu, G, K, λ, μ, Gc, εc, bc)
+    params = (; get_horizon(p)..., get_density(p)..., get_elastic_params(p)...)
+    params = (; params..., get_frac_params(p, params)...)
+    return params
 end
 
-@params BBMaterial BBPointParameters
+# struct BBPointParameters <: AbstractPointParameters
+#     δ::Float64
+#     rho::Float64
+#     E::Float64
+#     nu::Float64
+#     G::Float64
+#     K::Float64
+#     λ::Float64
+#     μ::Float64
+#     Gc::Float64
+#     εc::Float64
+#     bc::Float64
+# end
+
[…]

### 2024-10-09 src/physics/continuum_kinematics_inspired.jl

@@ -56,68 +56,87 @@ When specifying the `fields` keyword of [`Job`](@ref) for a [`Body`](@ref) with
 """
 struct CKIMaterial <: AbstractInteractionSystemMaterial end
 
-struct CKIPointParameters <: AbstractPointParameters
-    δ::Float64
-    rho::Float64
-    E::Float64
-    nu::Float64
-    G::Float64
-    K::Float64
-    λ::Float64
-    μ::Float64
-    Gc::Float64
-    εc::Float64
+@params CKIMaterial struct CKIPointParameters <: AbstractPointParameters
+    @required_params
     C1::Float64
     C2::Float64
     C3::Float64
 end
 
-function CKIPointParameters(::CKIMaterial, p::Dict{Symbol,Any})
-    δ = get_horizon(p)
-    rho = get_density(p)
-    E, nu, G, K, λ, μ = get_elastic_params(p)
-    Gc, εc = get_frac_params(p, δ, K)
-    C1, C2, C3 = cki_parameters(p, δ, λ, μ)
-    return CKIPointParameters(δ, rho, E, nu, G, K, λ, μ, Gc, εc, C1, C2, C3)
+function calc_parameter(::CKIMaterial, ::Val{:C1}, params::NamedTuple)
+    return 30 / π * params.μ / params.δ^4
 end
 
-function cki_parameters(p::Dict{Symbol,Any}, δ, λ, μ)
-    if haskey(p, :C1)
-        C1::Float64 = float(p[:C1])
-    else
-        C1 = 0.0
-    end
-
-    if haskey(p, :C2)
-        C2::Float64 = float(p[:C2])
-    else
-        C2 = 0.0
-    end
-
-    if haskey(p, :C3)
-        C3::Float64 = float(p[:C3])
-    else
-        C3 = 0.0
-    end
-
-    if C1 ≈ 0 && C2 ≈ 0 && C3 ≈ 0
-        C1 = 30 / π * μ / δ^4
-        C2 = 0.0
-        C3 = 32 / π^4 * (λ - μ) / δ^12
-    else
-        msg = "parameters for CKIMaterial specified manually!\n"
-        msg *= "Be careful when adjusting these parameters to avoid unexpected outcomes!"
-        @mpiroot @warn msg
-    end
-
-    return C1, C2, C3
+function calc_parameter(::CKIMaterial, ::Val{:C2}, params::NamedTuple)
+    return 0.0
 end
+
[…]

### 2024-10-09 src/physics/correspondence.jl

@@ -80,30 +80,39 @@ function Base.show(io::IO, @nospecialize(mat::NOSBMaterial))
     return nothing
 end
 
-struct NOSBPointParameters <: AbstractPointParameters
-    δ::Float64
-    rho::Float64
-    E::Float64
-    nu::Float64
-    G::Float64
-    K::Float64
-    λ::Float64
-    μ::Float64
-    Gc::Float64
-    εc::Float64
+@params NOSBMaterial struct NOSBPointParameters <: AbstractPointParameters
+    @required_params
     bc::Float64
 end
 
-function NOSBPointParameters(::NOSBMaterial, p::Dict{Symbol,Any})
-    δ = get_horizon(p)
-    rho = get_density(p)
-    E, nu, G, K, λ, μ = get_elastic_params(p)
-    Gc, εc = get_frac_params(p, δ, K)
-    bc = 18 * K / (π * δ^4) # bond constant
-    return NOSBPointParameters(δ, rho, E, nu, G, K, λ, μ, Gc, εc, bc)
+function calc_parameter(::NOSBMaterial, ::Val{:bc}, params::NamedTuple)
+    return 18 * params.K / (π * params.δ^4)
 end
 
-@params NOSBMaterial NOSBPointParameters
+# struct NOSBPointParameters <: AbstractPointParameters
+#     δ::Float64
+#     rho::Float64
+#     E::Float64
+#     nu::Float64
+#     G::Float64
+#     K::Float64
+#     λ::Float64
+#     μ::Float64
+#     Gc::Float64
+#     εc::Float64
+#     bc::Float64
+# end
+
+# function NOSBPointParameters(::NOSBMaterial, p::Dict{Symbol,Any})
+#     δ = get_horizon(p)
+#     rho = get_density(p)
+#     E, nu, G, K, λ, μ = get_elastic_params(p)
+#     Gc, εc = get_frac_params(p, δ, K)
+#     bc = 18 * K / (π * δ^4) # bond constant
+#     return NOSBPointParameters(δ, rho, E, nu, G, K, λ, μ, Gc, εc, bc)
+# end
+
+# @params NOSBMaterial NOSBPointParameters
 
 struct NOSBVerletStorage <: AbstractStorage
     position::Matrix{Float64}

### 2024-10-09 src/physics/fracture.jl

@@ -42,11 +42,10 @@ function failure_permit!(body::AbstractBody, set_name::Symbol, fail_permit::Bool
     return nothing
 end
 
-
-function get_frac_params(p::Dict{Symbol,Any}, δ::Float64, K::Float64)
+function get_frac_params(p::Dict{Symbol,Any}, params::NamedTuple)
+    (; δ, K) = params
     local Gc::Float64
     local εc::Float64
-
     if haskey(p, :Gc) && !haskey(p, :epsilon_c)
         Gc = float(p[:Gc])
         εc = sqrt(5.0 * Gc / (9.0 * K * δ))
@@ -62,8 +61,7 @@ function get_frac_params(p::Dict{Symbol,Any}, δ::Float64, K::Float64)
         msg *= "Define either Gc or epsilon_c!\n"
         throw(ArgumentError(msg))
     end
-
-    return Gc, εc
+    return (; Gc, εc)
 end
 
 

### 2024-10-09 src/physics/material_parameters.jl

@@ -2,7 +2,8 @@ const ELASTIC_KWARGS = (:E, :nu)
 const FRAC_KWARGS = (:Gc, :epsilon_c)
 const DEFAULT_POINT_KWARGS = (:horizon, :rho, ELASTIC_KWARGS..., FRAC_KWARGS...)
 
-function allowed_material_kwargs(::AbstractMaterial)
+function allowed_material_kwargs(mat::AbstractMaterial)
+    # return fieldnames(point_param_type(mat))
     return DEFAULT_POINT_KWARGS
 end
 
@@ -96,7 +97,7 @@ function get_horizon(p::Dict{Symbol,Any})
     end
     δ::Float64 = float(p[:horizon])
     δ ≤ 0 && throw(ArgumentError("`horizon` should be larger than zero!\n"))
-    return δ
+    return (; δ,)
 end
 
 function get_density(p::Dict{Symbol,Any})
@@ -105,7 +106,7 @@ function get_density(p::Dict{Symbol,Any})
     end
     rho::Float64 = float(p[:rho])
     rho ≤ 0 && throw(ArgumentError("`rho` should be larger than zero!\n"))
-    return rho
+    return (; rho,)
 end
 
 function get_elastic_params(p::Dict{Symbol,Any})
@@ -123,10 +124,10 @@ function get_elastic_params(p::Dict{Symbol,Any})
     K = E / (3 * (1 - 2 * nu))
     λ = E * nu / ((1 + nu) * (1 - 2nu))
     μ = G
-    return E, nu, G, K, λ, μ
+    return (; E, nu, G, K, λ, μ)
 end
 
-required_point_parameters() = (:δ, :rho, :E, :nu, :G, :K, :λ, :μ, :Gc, :εc)
+# required_point_parameters() = (:δ, :rho, :E, :nu, :G, :K, :λ, :μ, :Gc, :εc)
 
 #TODO: parameter checks material dependent...
 # req_param_material(::AbstractMaterial) = (:δ, :rho, :E, :nu, :G, :K, :λ, :μ)
@@ -139,21 +140,4 @@ function log_material_parameters(param::AbstractPointParameters; indentation::In
     msg *= msg_qty("shear modulus", param.G; indentation=indentation)
     msg *= msg_qty("bulk modulus", param.K; indentation=indentation)
     return msg
-end
-
-function Base.show(io::IO, @nospecialize(params::AbstractPointParameters))
-    print(io, "Parameters ", material_type(params), ": ")
[…]

### 2024-10-09 src/physics/ordinary_state_based.jl

@@ -58,30 +58,39 @@ struct OSBMaterial{Correction} <: AbstractBondSystemMaterial{Correction} end
 
 OSBMaterial() = OSBMaterial{NoCorrection}()
 
-struct OSBPointParameters <: AbstractPointParameters
-    δ::Float64
-    rho::Float64
-    E::Float64
-    nu::Float64
-    G::Float64
-    K::Float64
-    λ::Float64
-    μ::Float64
-    Gc::Float64
-    εc::Float64
+@params OSBMaterial struct OSBPointParameters <: AbstractPointParameters
+    @required_params
     bc::Float64
 end
 
-function OSBPointParameters(::OSBMaterial, p::Dict{Symbol,Any})
-    δ = get_horizon(p)
-    rho = get_density(p)
-    E, nu, G, K, λ, μ = get_elastic_params(p)
-    Gc, εc = get_frac_params(p, δ, K)
-    bc = 18 * K / (π * δ^4)
-    return OSBPointParameters(δ, rho, E, nu, G, K, λ, μ, Gc, εc, bc)
+function calc_parameter(::OSBMaterial, ::Val{:bc}, params::NamedTuple)
+    return 18 * params.K / (π * params.δ^4)
 end
 
-@params OSBMaterial OSBPointParameters
+# struct OSBPointParameters <: AbstractPointParameters
+#     δ::Float64
+#     rho::Float64
+#     E::Float64
+#     nu::Float64
+#     G::Float64
+#     K::Float64
+#     λ::Float64
+#     μ::Float64
+#     Gc::Float64
+#     εc::Float64
+#     bc::Float64
+# end
+
+# function OSBPointParameters(::OSBMaterial, p::Dict{Symbol,Any})
+#     δ = get_horizon(p)
+#     rho = get_density(p)
+#     E, nu, G, K, λ, μ = get_elastic_params(p)
+#     Gc, εc = get_frac_params(p, δ, K)
+#     bc = 18 * K / (π * δ^4)
+#     return OSBPointParameters(δ, rho, E, nu, G, K, λ, μ, Gc, εc, bc)
+# end
+
+# @params OSBMaterial OSBPointParameters
 
 struct OSBVerletStorage <: AbstractStorage
     position::Matrix{Float64}

### 2024-10-09 test/integration/material_interface.jl

@@ -8,7 +8,7 @@ end
 
 @testitem "Point parameters declaration" begin
     struct TestMaterial2 <: Peridynamics.AbstractMaterial end
-    struct TestPointParameters2 <: Peridynamics.AbstractPointParameters
+    Peridynamics.@params TestMaterial2 struct TestPointParameters2 <: Peridynamics.AbstractPointParameters
         δ::Float64
         rho::Float64
         E::Float64
@@ -49,7 +49,6 @@ end
     end
     @test_throws ErrorException Peridynamics.typecheck_params(PointParametersMissingHorizon)
 
-    Peridynamics.@params TestMaterial2 TestPointParameters2
     @test hasmethod(Peridynamics.point_param_type, Tuple{TestMaterial2})
     @test Peridynamics.point_param_type(TestMaterial2()) == TestPointParameters2
     @test hasmethod(Peridynamics.get_point_params, Tuple{TestMaterial2,Dict{Symbol,Any}})

### 2024-10-09 test/integration/test_material.jl

@@ -1,24 +1,15 @@
 struct TestMaterial <: Peridynamics.AbstractBondSystemMaterial{Peridynamics.NoCorrection} end
-struct TestPointParameters <: Peridynamics.AbstractPointParameters
-    δ::Float64
-    rho::Float64
-    E::Float64
-    nu::Float64
-    G::Float64
-    K::Float64
-    λ::Float64
-    μ::Float64
-    Gc::Float64
-    εc::Float64
+Peridynamics.@params TestMaterial struct TestPointParameters <: Peridynamics.AbstractPointParameters
+    Peridynamics.@required_params
 end
-function TestPointParameters(::TestMaterial, p::Dict{Symbol,Any})
-    δ = Peridynamics.get_horizon(p)
-    rho = Peridynamics.get_density(p)
-    E, nu, G, K, λ, μ = Peridynamics.get_elastic_params(p)
-    Gc, εc = Peridynamics.get_frac_params(p, δ, K)
-    return TestPointParameters(δ, rho, E, nu, G, K, λ, μ, Gc, εc)
-end
-Peridynamics.@params TestMaterial TestPointParameters
+# function TestPointParameters(::TestMaterial, p::Dict{Symbol,Any})
+#     δ = Peridynamics.get_horizon(p)
+#     rho = Peridynamics.get_density(p)
+#     E, nu, G, K, λ, μ = Peridynamics.get_elastic_params(p)
+#     Gc, εc = Peridynamics.get_frac_params(p, δ, K)
+#     return TestPointParameters(δ, rho, E, nu, G, K, λ, μ, Gc, εc)
+# end
+# Peridynamics.@params TestMaterial TestPointParameters
 # Peridynamics.@system TestMaterial Peridynamics.BondSystem
 struct TestVerletStorage <: Peridynamics.AbstractStorage
     position::Matrix{Float64}

### 2024-10-09 test/physics/test_material_parameters.jl

@@ -1,7 +1,7 @@
 @testitem "get_horizon" begin
     p = Dict{Symbol,Any}(:horizon => 1)
-    rho = Peridynamics.get_horizon(p)
-    @test rho ≈ 1.0
+    (; δ) = Peridynamics.get_horizon(p)
+    @test δ ≈ 1.0
 
     p = Dict{Symbol,Any}(:nothorizon => 1)
     @test_throws UndefKeywordError(:horizon) Peridynamics.get_horizon(p)
@@ -13,7 +13,7 @@ end
 
 @testitem "get_density" begin
     p = Dict{Symbol,Any}(:rho => 1)
-    rho = Peridynamics.get_density(p)
+    (; rho) = Peridynamics.get_density(p)
     @test rho ≈ 1.0
 
     p = Dict{Symbol,Any}(:notrho => 1)

### 2024-10-09 src/core/point_parameters.jl
Working Draft

@@ -21,9 +21,13 @@ function extract_parameters(mat::AbstractMaterial,
             value = calc_parameter(mat, Val(name), required_params)
         end
         check_parameter(mat, Val(name), value)
-        params = (; params..., name = value)
+        params = (; params..., name => value)
     end
     return params
+end
+
+function set_kw(::Type, ::Val{keyword}) where {keyword}
+    return keyword
 end
 
 function extract_required_parameters(::AbstractMaterial, p::Dict{Symbol,Any})
@@ -32,7 +36,9 @@ function extract_required_parameters(::AbstractMaterial, p::Dict{Symbol,Any})
     return params
 end
 
-function parse_parameter(::M, keyword::Symbol, ::Type{T}, p::Dict{Symbol,Any}) where {M,T}
+function parse_parameter(::M, name::Symbol, ::Type{T}, p::Dict{Symbol,Any}) where {M,T}
+    keyword = set_kw(M, Val(name))
+    isnothing(keyword) && return nothing
     haskey(p, keyword) || return nothing
     value::T = convert(T, p[keyword])
     return value
@@ -47,7 +53,7 @@ function check_parameter(::AbstractMaterial, ::Val{P}, value) where {P}
     return nothing
 end
 
-function required_point_parameters(::Type{Material}) where {Material}
+function required_point_parameters(::Val{M}) where {M}
     required_params = (:(δ::Float64), # horizon
                        :(rho::Float64), # density
                        :(E::Float64), # Young's modulus
@@ -61,14 +67,14 @@ function required_point_parameters(::Type{Material}) where {Material}
     return required_params
 end
 
-function required_point_parameter_names(::Type{Material}) where {Material}
-    required_params = required_point_parameters(Material)
+function required_point_parameter_names(mat::Val{M}) where {M}
+    required_params = required_point_parameters(mat)
     param_names = Tuple(extract_parameter_name(field) for field in required_params)
     return param_names
 end
 
-function required_point_parameter_types(::Type{Material}) where {Material}
-    required_params = required_point_parameters(Material)
+function required_point_parameter_types(mat::Val{M}) where {M}
+    required_params = required_point_parameters(mat)
     param_types = Tuple(extract_parameter_type(field) for field in required_params)
     return param_types
 end
@@ -87,13 +93,13 @@ function extract_parameter_type(expr::Expr)::DataType
     return eval(expr.args[2])
 end
 
-function expand_point_parameters(material, struct_expr)
+function expand_point_parameters(struct_expr, matval)
[…]

### 2024-10-09 src/physics/bond_based.jl

@@ -71,6 +71,8 @@ function calc_parameter(::BBMaterial, ::Val{:bc}, params::NamedTuple)
     return 18 * params.K / (π * params.δ^4)
 end
 
+@inline set_kw(::Type{<:BBMaterial}, ::Val{:bc}) = nothing
+
 function extract_required_parameters(::BBMaterial, p::Dict{Symbol,Any})
     if haskey(p, :nu) #&& !isapprox(float(p[:nu]), 0.25)
         msg = "keyword `nu` is not allowed for BBMaterial!\n"

### 2024-10-09 src/physics/continuum_kinematics_inspired.jl

@@ -132,9 +132,9 @@ end
 #     return C1, C2, C3
 # end
 
-function allowed_material_kwargs(::CKIMaterial)
-    return (DEFAULT_POINT_KWARGS..., :C1, :C2, :C3)
-end
+# function allowed_material_kwargs(::CKIMaterial)
+#     return (DEFAULT_POINT_KWARGS..., :C1, :C2, :C3)
+# end
 
 # @params CKIMaterial CKIPointParameters
 

### 2024-10-09 src/physics/material_parameters.jl

@@ -2,9 +2,11 @@ const ELASTIC_KWARGS = (:E, :nu)
 const FRAC_KWARGS = (:Gc, :epsilon_c)
 const DEFAULT_POINT_KWARGS = (:horizon, :rho, ELASTIC_KWARGS..., FRAC_KWARGS...)
 
-function allowed_material_kwargs(mat::AbstractMaterial)
-    # return fieldnames(point_param_type(mat))
-    return DEFAULT_POINT_KWARGS
+function allowed_material_kwargs(mat::M) where {M<:AbstractMaterial}
+    fields = fieldnames(point_param_type(mat))
+    kwargs = [set_kw(M, Val(p)) for p in fields]
+    allowed_kwargs = Tuple(filter(x -> !isnothing(x), kwargs))
+    return allowed_kwargs
 end
 
 """
@@ -91,20 +93,22 @@ function check_material_kwargs(mat::AbstractMaterial, p::Dict{Symbol,Any})
     return nothing
 end
 
+@inline set_kw(::Type{M}, ::Val{:δ}) where {M} = :horizon
+@inline set_kw(::Type{M}, ::Val{:G}) where {M} = nothing
+@inline set_kw(::Type{M}, ::Val{:K}) where {M} = nothing
+@inline set_kw(::Type{M}, ::Val{:λ}) where {M} = nothing
+@inline set_kw(::Type{M}, ::Val{:μ}) where {M} = nothing
+
 function get_horizon(p::Dict{Symbol,Any})
-    if !haskey(p, :horizon)
-        throw(UndefKeywordError(:horizon))
-    end
-    δ::Float64 = float(p[:horizon])
+    δ = parse_parameter(AbstractMaterial, :δ, Float64, p)
+    isnothing(δ) && throw(UndefKeywordError(set_kw(AbstractMaterial, Val(:δ))))
     δ ≤ 0 && throw(ArgumentError("`horizon` should be larger than zero!\n"))
     return (; δ,)
 end
 
 function get_density(p::Dict{Symbol,Any})
-    if !haskey(p, :rho)
-        throw(UndefKeywordError(:rho))
-    end
-    rho::Float64 = float(p[:rho])
+    rho = parse_parameter(AbstractMaterial, :rho, Float64, p)
+    isnothing(rho) && throw(UndefKeywordError(:rho))
     rho ≤ 0 && throw(ArgumentError("`rho` should be larger than zero!\n"))
     return (; rho,)
 end

### 2024-10-09 test/discretization/test_interaction_system.jl

@@ -4,7 +4,7 @@
                 0.0 0.0 1.0]
     volume = fill(1.0, 3)
     body = Body(CKIMaterial(), position, volume)
-    material!(body; horizon=1.5, rho=8e-6, E=210e3, nu=0.3, Gc=1.0, C1=1, C2=1)
+    material!(body; horizon=1.5, rho=8e-6, E=210e3, nu=0.3, Gc=1.0, C1=1, C2=1, C3=0)
     pd = Peridynamics.PointDecomposition(body, 1)
 
     is, ch = Peridynamics.InteractionSystem(body, pd, 1)

### 2024-10-09 test/integration/material_interface.jl

@@ -20,7 +20,7 @@ end
         Gc::Float64
         εc::Float64
     end
-    @test isnothing(Peridynamics.typecheck_params(TestPointParameters2))
+    @test isnothing(Peridynamics.typecheck_params(TestMaterial2,TestPointParameters2))
 
     struct PointParametersNoSubtype
         δ::Float64
@@ -34,7 +34,7 @@ end
         Gc::Float64
         εc::Float64
     end
-    @test_throws ArgumentError Peridynamics.typecheck_params(PointParametersNoSubtype)
+    @test_throws ArgumentError Peridynamics.typecheck_params(TestMaterial2,PointParametersNoSubtype)
 
     struct PointParametersMissingHorizon <: Peridynamics.AbstractPointParameters
         rho::Float64
@@ -47,7 +47,7 @@ end
         Gc::Float64
         εc::Float64
     end
-    @test_throws ErrorException Peridynamics.typecheck_params(PointParametersMissingHorizon)
+    @test_throws ArgumentError Peridynamics.typecheck_params(TestMaterial2, PointParametersMissingHorizon)
 
     @test hasmethod(Peridynamics.point_param_type, Tuple{TestMaterial2})
     @test Peridynamics.point_param_type(TestMaterial2()) == TestPointParameters2

### 2024-10-09 test/integration/test_material.jl

@@ -1,6 +1,6 @@
 struct TestMaterial <: Peridynamics.AbstractBondSystemMaterial{Peridynamics.NoCorrection} end
 Peridynamics.@params TestMaterial struct TestPointParameters <: Peridynamics.AbstractPointParameters
-    Peridynamics.@required_params
+    @required_params
 end
 # function TestPointParameters(::TestMaterial, p::Dict{Symbol,Any})
 #     δ = Peridynamics.get_horizon(p)
